---
title: "Check missingness in 10/66"
output: 
  html_document:
      code_folding: hide
date: "2022-11-18"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE)
```

### Open libraries

```{r}
library(cowplot)
library(epiR)       # for epi.conf() to calculate CIs for prevalence
library(gridExtra)
library(haven)      # for opening Stata dta files and converting relevant variables into factors as_factor()
library(here)       # for easy file referencing by using the top-level directory of a file project
library(knitr)
library(labelled)   # for var_label() to get variable labels
library(openxlsx)   # for write.xlsx()
library(readxl)     # for read_excel()
library(tableone)
library(tidyverse)
```

What is the top-level of current project?

```{r}
here::here()
```

## Open data

Source codes

```{r}
source(here::here("Script", "Functions", "Data process", "func_open_and_process_data.R"))
```

### Open 10/66 baseline dataset

```{r}
# here::here("Data", "raw data", "baseline survey", "prevalence_survey_data_1_3.dta")
# using here() means that file paths can be created from any physical place as long as fold structure is equivalent
path = here::here("Data", "raw data", "baseline survey", "prevalence_survey_data_1_3.dta")
data_base = open_and_process_data(path, "dta") # this function opens a Stata dataset (dta) and converts Stata's labelled variables into factors
```

### Open 10/66 incidence dataset

```{r}
path = here::here("Data", "raw data", "fu folder from Matthew", "incidence cohort (all survey outcomes)", "other countries", "full follow up_1_2.dta")
data_inc = open_and_process_data(path, "dta")
```

## Process data

Select variables of interest:

```{r}
varnames_base = data_base %>% 
  select(houseid2, PARTICID, countryid, centreid, age, gender, rural, Nassets, PMARRY, CARENEED, anycare, illnocat, cdem1066, PEDUC, PTOLDDM, PDMTRT, PSMOKE, PSTART, PSMKNOW, PSTOP, PCIGDOSE, PALCNOW, PALCPAST, PHEAVY, PALCTRT, PACTIVE, PMEATFRQ, PFISHFRQ, PVEGS,  NEO14G, NEO6AU, NEO6AL, NEO6BU, NEO6BL, NEO4E, NEO4F, NOE1, NEO14E, PCVA, medserv, PHOSAD) %>% 
  names()

varnames_inc = paste0("f_", varnames_base[5:length(varnames_base)])
varnames_inc = c("HOUSEID" , "PARTICID", "countryid", "centreid" , varnames_inc)
```

```{r}
data_base = data_base %>% select_if(names(.) %in% varnames_base)
data_inc = data_inc %>%  select_if(names(.) %in% varnames_inc)
```

## Check missingness

### Baseline phase

```{r}
glimpse(data_base)
```

Plot histogram of continuous variables

```{r}
plot_data_histogram = function (data, col){
  
  tot = nrow(data)
  miss = sum(is.na(data[[col]]))
  pct_miss = round(miss/tot*100,1)
  
  lab = paste0("Total=", tot,"\n",
               "Missing=", miss, " (", pct_miss, "%)")
    
  ggplot(data, aes_string(x = col)) +
    geom_histogram() +
    geom_text(data=data.frame(), aes(label = lab, x=Inf, y=Inf, hjust=1, vjust=1), size=3)+
    xlab(col) +
    ylab("Count") +
    theme_classic()
}

myplots1 = lapply(colnames(data_base[, 3:9]), plot_data_histogram, data=data_base)


plot_hist1 = gridExtra::grid.arrange( myplots1[[1]], myplots1[[2]], myplots1[[3]], myplots1[[4]], ncol=2)
plot_hist2 = gridExtra::grid.arrange( myplots1[[5]], myplots1[[6]], myplots1[[7]], ncol=2)

plot_hist1
plot_hist2
```

Plot bar charts of factor variables

```{r, out.width="50%"}
plot_data_barchart = function (data, col){
  
  geom.text.size = 4
  theme.size = (14/5)*geom.text.size
  
  p = ggplot(data, aes_string(x = col)) +
    geom_bar() +
    geom_text(stat = "count", aes(label=..count..), vjust=-0.5, size=geom.text.size) +
    scale_y_continuous(expand = expansion(mult= c(0, 0.1), add=c(1,0))) + # to add room for labels at the top
    scale_x_discrete(labels = function(x) stringr::str_wrap(x, width=10)) + # make sure x axis labels wrap appropriately
    xlab(col) +
    ylab("Count") +
    theme_classic()+
    theme(axis.text.x = element_text(size=theme.size, angle=45, hjust=1),
          axis.text = element_text(size=theme.size))
  
  print(p)
  
  return(p)
}

myplots = lapply(colnames(data_base[, 11:ncol(data_base)]), plot_data_barchart, data=data_base)
```

### Incidence phase

```{r}
glimpse(data_inc)
```

Plot histogram of continuous variables

```{r}
myplots = lapply(colnames(data_inc[, 3:5]), plot_data_histogram, data=data_inc)

plot_hist1 = gridExtra::grid.arrange(myplots1[[1]], myplots1[[2]], myplots1[[3]], myplots1[[4]], ncol=2)

plot_hist1
```

Plot bar charts of factor variables

```{r, out.width="50%"}
myplots = lapply(colnames(data_inc[, 6:ncol(data_inc)]), plot_data_barchart, data=data_inc)
```
