---
title: "View PD and neuropsychiatric variables in 1066 baseline data"
output: 
  html_document:
    code_folding: hide
date: "2022-10-05"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE)
```

### Open libraries

```{r}
library(descr)      # for crosstab(), descriptive statistics package
library(haven)      # for opening Stata dta files and converting relevant variables into factors as_factor()
library(here)       # for easy file referencing by using the top-level directory of a file project
library(knitr)
library(labelled)   # for var_label() to get variable labels
library(readxl)     # for read_excel()
library(tableone)
library(tidyverse)
```

What is the top-level of current project?

```{r}
here::here()
```

## Open data

### Open 10/66 baseline dataset

```{r}
# here::here("Data", "raw data", "baseline survey", "prevalence_survey_data_1_3.dta")
# using here() means that file paths can be created from any physical place as long as fold structure is equivalent
data = haven::read_dta(here::here("Data", "raw data", "baseline survey", "prevalence_survey_data_1_3.dta"))
```

### View susbet of the data

```{r}
# get a list of relevant variable

# parkinsonism/parks: self-reported Parkinson's disease by informant (no, probable, certain) - missing in most ppl
# NEO14G: bradykinesia
# NEO6AU: ridigity - nul
# NEO6AL: ridigity - rll
# NEO6BU: ridigity - lul
# NEO6BL: rigitidy - lll
# NEO4E: tremor - nul
# NEO4F: tremor - lul
# NOE1: vertical upgaze
# NEO14E: ataxia
# PCVA: told had stroke?
# countryid: country identifier
# cdem1066: Education adjusted 1066 Lancet dementia diagnosis
# PEDUC: level of education
# zbtot: total zarit carer burden score
# careeduc: informant educational level - is this the correct variable?
# careneed: need for care
# npisev: npi total severity score [0,36]
# npidis: npi total distress score [0,52]
# dsmdisab: dsm disability (whodas score) [0,8]

varnames = data %>% 
  select(houseid2, PARTICID, countryid, centreid, age, gender, rural, Nassets, anycare, illnocat, PCVA, cdem1066, PEDUC, zbtot, CAREEDUC, CARENEED, dsmdisab, PARK, parkinsonism, starts_with("NPI"), starts_with("CARER"), starts_with("NEO1"), starts_with("NEO6"), starts_with("NEO4"), starts_with("NOE1")) %>% 
  names()
```

```{r}
data %>% select_if(names(.) %in% varnames) %>% glimpse()
```

## Process data

### Convert labelled variables into factors

```{r}
# use haven::as_factor, which uses the labels imported from the Stata data to convert into factor levels
test = data %>% 
  select_if(is.labelled) %>%                            # select labelled variables
  mutate(across(everything(), ~haven::as_factor(.x)))   # convert these into factors
```

### Merge the factor variables back to original data

```{r}
data_factors = data %>% 
  select_if(~!is.labelled(.)) %>%    # deselect labelled variables
  bind_cols(test)                    # bind factor variables

mydata = data_factors %>% 
  select_if(names(.) %in% varnames)

glimpse(mydata)
```

### Compute variables

#### Parkinsonism

`PARK` variable (self-reported PD):

```{r}
summary(mydata$PARK)
```

`NEO14G` variable:

```{r}
summary(mydata$NEO14G)
```

Define the `pnism` variable:

```{r}
mydata = mydata %>% 
  mutate(pnism1 = if_else(((NEO14G=="somewhat slow movements" | NEO14G=="very slow movements") & (NEO6AU=="slightly increased tone" | NEO6AU=="much increased tone" |NEO6AL=="slightly increased tone" |NEO6AL=="much increased tone" | NEO6BU=="slightly increased tone" |NEO6BU=="much increased tone" | NEO6BL=="slightly increased tone" | NEO6BL=="much increased tone")), 1, 0)) %>%  
  # Stata treats missing data differently (removes observations in the calculation when there is missing data), so the next line of codes does that in R
  mutate(pnism1 = if_else(is.na(NEO14G) & (is.na(NEO6AU) | NEO6AU=="normal tone") & (is.na(NEO6AL) | NEO6AL=="normal tone") & (is.na(NEO6BU) | NEO6BU=="normal tone") & (is.na(NEO6BL) | NEO6BL=="normal tone"), NA_real_, pnism1))

summary(as.factor(mydata$pnism1))
```

```{r}
mydata = mydata %>% 
  mutate(pnism2 = if_else(((NEO14G=="somewhat slow movements" | NEO14G=="very slow movements") & ((!NEO4E=="no tremor") | (!NEO4F=="no tremor"))), 1, 0))

summary(as.factor(mydata$pnism2))
```

```{r}
mydata = mydata %>% 
  mutate(pnism = if_else(pnism1==1 | pnism2==1, 1, pnism1)) %>% 
  select(-pnism1, -pnism2)

summary(as.factor(mydata$pnism))
```

#### Parkinson's disease

Define the `JorgePD` variable:

```{r}
mydata = mydata %>% 
  mutate(JorgePD = if_else(pnism==1 & (NOE1=="normal upgaze" & NEO14E=="normal gait" & PCVA=="no"), 1, 0)) %>% 
  mutate(JorgePD = if_else(is.na(pnism) & (is.na(NOE1) | is.na(NEO14E) | is.na(PCVA)), NA_real_, JorgePD))

summary(as.factor(mydata$JorgePD))
```

What is the overlap between the self-reported pnism and questionnaire-based pnism dx

```{r}
# relabel PARK variable
mydata = mydata %>% 
  mutate(selfpnism = if_else(parkinsonism == "Parkinsonian", 1, 0, missing = NA_real_),
         selfpd = if_else(PARK == "probable" | PARK == "certain", 1, 0, missing = NA_real_),
         selfpd1 = if_else(PARK == "certain", 1, 0, missing = NA_real_))

# Pull variables as vectors
pnism = mydata$pnism
selfpnism = mydata$selfpnism

#table(mydata$pnism, mydata$selfpnism, useNA = "always")
descr::CrossTable(pnism, selfpnism, prop.t = TRUE)
descr::CrossTable(mydata$JorgePD, mydata$selfpd, prop.t = TRUE)
descr::CrossTable(mydata$JorgePD, mydata$selfpd1, prop.t = TRUE)
table(mydata$JorgePD, mydata$selfpd1, useNA = "always")
```

#### Combine dementia and Parkinsonism variables

`cdem1066` variable:

```{r}
summary(mydata$cdem1066)
```

`pnism` and `cdem1066` combined:

```{r, eval=FALSE}
# this results in incorrect variable because results in deletion of observation with any missing data in psnim and cdem1066, i.e. uses complete case
# in Stata, the relevant code includes data from pnism/cdem1066 observerations even if they are missing data in cdem1066/pnism
mydata = mydata %>% 
  mutate(combined = factor(case_when(pnism==0 & cdem1066=="non-case" ~ "0 non-case",
                                     pnism==0 & cdem1066=="case" ~ "0 case",
                                     pnism==1 & cdem1066=="non-case" ~ "1 non-case",
                                     pnism==1 & cdem1066=="case" ~ "1 case",
                                     TRUE ~ NA_character_),
                           levels = c("0 non-case", "0 case", "1 non-case", "1 case"),
                           labels = c("Control", "DAT", "Parkinsonism", "PPD")))

summary(mydata$combined) # some differences in the numbers
```

```{r}
mydata = mydata %>% 
  mutate(combined = paste(pnism, cdem1066),
         combined = factor(if_else(grepl("NA", combined), NA_character_, combined),
                           levels = c("0 non-case", "1 non-case", "0 case", "1 case"),
                           labels = c("Control", "Parkinsonism", "Dementia", "Parkinsonism and dementia")))

summary(mydata$combined) # still some differences in the number of dementia (1111 vs 1098) and controls (13634 vs 13571); numbers of parkinsonism and parkinsonism with dementia is same
```

Note: some differences in the numbers in dementia (1111 vs 1098) and controls (13634 vs 13571) requires investigation

#### List of neuropsychiatric symptoms

```{r}
npi = data %>% 
  select(starts_with("NPI")) %>% 
  labelled::var_label() %>% 
  as_tibble() %>% 
  gather(key = variable, value = description) %>% 
  mutate(description = str_sub(description, 8, -1), # removes the first 7 characters
         description = str_remove(description, "\\-"), # remove all strings after '-'
         description = str_trim(description)) # remove any leading or trailing white spaces

kable(npi)
```

#### Drop observations from China or India

```{r}
mydata = mydata %>% 
  filter(!countryid %in% c("China", "India"))

# drop unused factor levels
mydata$countryid = droplevels(mydata$countryid)

summary(mydata$countryid)

table(mydata$countryid, mydata$rural)
```
