---
title: "Association between Parkinsonism/PD and frailty"
output: html_document
date: "2023-07-27"
---

## Open libraries

```{r}
library(cowplot)
library(broom)      # for tidy()
library(data.table) # for rbindlist()
library(descr)      # for crosstab(), descriptive statistics package
library(ggVennDiagram)
library(gridGraphics) # for grid.grab()
#library(gtsummary)  # for tbl_regression()
library(here)       # for easy file referencing by using the top-level directory of a file project
library(kableExtra)
library(knitr)
library(meta)       # meta-analysis
library(survival)
library(tableone)
library(tidyverse)
```

What is the top-level of current project?

```{r}
here::here()
```

# Open and process dataset

## Open baseline phase data

Source codes

```{r}
source(here::here("Script", "Functions", "Data process", "func_open_and_process_data.R"))
source(here::here("Script", "Functions", "Data process", "func_compute_pd_variables.R"))
```

Set path for function input

```{r}
path = here::here("Data", "raw data", "baseline survey", "prevalence_survey_data_1_3.dta")
```

Open dataset

```{r}
data = open_and_process_data(path, "dta") # this function opens a Stata dataset (dta) and converts Stata's labelled variables into factors
```

Process Parkinsonism and PD variables

```{r}
data = compute_pd_variables(data)
```

Subset relevant variables

```{r}
varnames = data %>% 
  select(houseid2, PARTICID, countryid, centreid, age, gender, rural, Nassets, PMARRY, CARENEED, illnocat, cdem1066, PEDUC, PTOLDDM, PSMOKE, PALCNOW, PALCPAST, PACTIVE, PMEATFRQ, PFISHFRQ, PVEGS, NEO14G, NEO6AU, NEO6AL, NEO6BU, NEO6BL, NEO4E, NEO4F, NOE1, NEO14E, PCVA, medserv, PPC, PHOSP, POTH, PPD, PDENT, PTH, PHOSAD, pnism, JorgePD, parkinsonism, PARK) %>% 
  names()

data = data %>% select_if(names(.) %in% varnames)
```

Rename PD variable

```{r}
data = data %>% 
  mutate(PD = JorgePD) %>% 
  select(-JorgePD)

summary(as.factor(data$PD))
```

## Open pre-processed frailty variables

Open rds file

```{r}
data_base_frail = readRDS(here::here("Data", "processed data", "data_baseline_frailty.rds")) 
data_inc_frail = readRDS(here::here("Data", "processed data", "data_incidence_frailty.rds")) 
```

## Subset data for Latin America

```{r}
# Create function to drop observations from certain countries and relabel countries

process_country_var = function(data){
  
  data = data %>% 
    filter(centreid %in% c("Cuba", "DR", "Peru (urban)", "Peru (rural)", "Venezuela", "Mexico (urban)", "Mexico (rural)", "Puerto Rico"))
  
  # drop unused factor levels
  data$centreid = droplevels(data$centreid)
  data$countryid = droplevels(data$countryid)
  
  data$countryid = factor(data$countryid, levels = c("Cuba", "DR", "Peru", "Venezuela", "Mexico", "Puerto Rico"),
                        labels = c("Cuba", "Dominican Republic", "Peru", "Venezuela", "Mexico", "Puerto Rico"))
  
  return(data)
  
}

data = process_country_var(data)
data_base_frail = process_country_var(data_base_frail)
data_inc_frail = process_country_var(data_inc_frail)
```

## Create datasets for analysis

### Cross-sectional analysis: everyone (i.e. has missing data)

```{r}
# Baseline data
data_base = data %>% 
  select(houseid2, PARTICID, pnism, PD) %>% 
  left_join(select(data_base_frail, houseid2, PARTICID, starts_with("b_fp."), starts_with("b_mf."), starts_with("b_fi.")), by = c("houseid2", "PARTICID")) %>% 
  mutate(id=row_number())

# Merge back covariates
data_base = data %>%  
  select(houseid2, PARTICID, countryid, age, gender, PMARRY, PEDUC, Nassets, illnocat, CARENEED) %>% 
  right_join(data_base, by = c("houseid2", "PARTICID"))
```

### Cross-sectional analysis: complete cases on frailty and PD variables

```{r}
# Baseline data
data_base_complete = data %>% 
  select(houseid2, PARTICID, pnism, PD) %>% 
  left_join(select(data_base_frail, houseid2, PARTICID, starts_with("b_fp."), starts_with("b_mf."), starts_with("b_fi.")), by = c("houseid2", "PARTICID")) %>% 
  filter(complete.cases(.)) %>% 
  mutate(id=row_number())

# Merge back covariates
data_base_complete = data %>%  
  select(houseid2, PARTICID, countryid, age, gender, PMARRY, PEDUC, Nassets, illnocat, CARENEED) %>% 
  right_join(data_base_complete, by = c("houseid2", "PARTICID"))
```

### Prospective analysis: followed-up and complete cases on frailty and PD variables

```{r}
# Open follow-up status data
# Create data path for follow-up status at incidence phase
path = here::here("Data", "raw data", "fu folder from Matthew", "incidence cohort (all survey outcomes)", "other countries", "status_outcome (survey cohort)_1_0.sav")
status_outcome = open_and_process_data(path, "sav")

# Relabel country and id variables to match the other dataframe
status_outcome = status_outcome %>% 
  mutate(centreid_num = case_when(centreid == "Cuba" ~ 10,
                                  centreid == "DR" ~ 20,
                                  centreid == "Peru (urban)" ~ 30,
                                  centreid == "Peru (rural)" ~ 40,
                                  centreid == "Venezuela" ~ 50,
                                  centreid == "Mexico (urban)" ~ 60,
                                  centreid == "Mexico (rural)" ~ 70,
                                  centreid == "China (urban)" ~ 100,
                                  centreid == "China (rural)" ~ 110,
                                  centreid == "Puerto Rico" ~ 200)) %>% 
  mutate(HOUSEID = stringr::str_pad(HOUSEID, 4, pad="0")) %>% 
  mutate(houseid2 = as.numeric(paste0(centreid_num, HOUSEID))) %>% 
  select(-HOUSEID, -centreid_num, -centreid)

# Merge in follow-up status & gender to incidence phase data
temp = data %>% 
  left_join(status_outcome, by = c("houseid2", "PARTICID"))
  
summary(temp$Statusfu)

# Select participants who either died or interviewed by follow-up (i.e. exclude refused, uncontactable, not traced, not recorded or NA)
# Merge in frailty data
temp = temp %>% 
  filter(Statusfu=="Died" | Statusfu=="Interviewed") %>% 
  left_join(select(data_inc_frail, houseid2, PARTICID, starts_with("i_fi."), starts_with("i_fp."), starts_with("i_mf.")), by=c("houseid2", "PARTICID")) %>% 
  left_join(select(data_base_frail, houseid2, PARTICID, starts_with("b_fi."), starts_with("b_fp."), starts_with("b_mf.")), by=c("houseid2", "PARTICID"))

# Create separate datasets by frailty definition
temp_fp = temp %>% select(-contains("fi"), -contains("mf"))
temp_mf = temp %>% select(-contains("fp"), -contains("fi"))
temp_fi = temp %>% select(-contains("fp"), -contains("mf"))

# Subset participants with complete data
temp_fp = temp_fp %>% filter(if_all(c(pnism, PD, b_fp.frail), complete.cases))
temp_mf = temp_mf %>% filter(if_all(c(pnism, PD, b_mf.frail), complete.cases))
temp_fi = temp_fi %>% filter(if_all(c(pnism, PD, b_fi.frail), complete.cases))

# Filter participants without frailty at baseline
data_fp = temp_fp %>% filter(b_fp.frail==0)
data_mf = temp_mf %>% filter(b_mf.frail==0)
data_fi = temp_fi %>% filter(b_fi.frail==0)

# Subset participants with frailty data at follow-up or died
data_fp = data_fp %>% filter(!is.na(i_fp.frail) | Statusfu=="Died")
data_mf = data_mf %>% filter(!is.na(i_mf.frail) | Statusfu=="Died")
data_fi = data_fi %>% filter(!is.na(i_fi.frail) | Statusfu=="Died")
```

Venn diagram of frail participants at baseline

```{r}
x = list(`FI` = data_base_complete %>% filter(b_fi.frail==1) %>% pull(id), 
         `FP` = data_base_complete %>% filter(b_fp.frail==1) %>% pull(id), 
         `MF` = data_base_complete %>% filter(b_mf.frail==1) %>% pull(id))

ggVennDiagram::ggVennDiagram(x, 
                             set_color = c("black", "black", "black"),
                             color = c("black", "black", "black"), 
                             edge_size = 1, 
                             edge_lty = "solid") +
  scale_fill_gradient(low = "#F4FAFE", high = "#4981BF") +
  theme(legend.position = "none")
```

# Descriptive analysis

## Table 1 Baseline characteristics of the total 10/66 participants from Latin American countries

```{r, include=FALSE}
vars = c("age", "gender", "PMARRY", "PEDUC", "Nassets", "illnocat", "CARENEED", "pnism", "PD", "b_fp.frail", "b_mf.frail", "b_fi.frail")
factorVars = c("gender", "PMARRY", "PEDUC", "Nassets",  "illnocat", "CARENEED", "pnism", "PD", "b_fp.frail", "b_mf.frail", "b_fi.frail")

# include missing as a separate factor level
tab1 = tableone::CreateTableOne(data = data_base,
                                vars = vars,
                                factorVars = factorVars,
                                strata = c("countryid"),
                                includeNA = TRUE,
                                addOverall = TRUE)

table1 = print(tab1)
```

```{r, echo=FALSE}
print(tab1) %>% 
  kbl() %>% 
  kable_paper("hover", full_width=FALSE)
```

Save table

```{r}
path = here::here("Output", "PD and frailty paper", "Table1.csv")
write.csv(table1, path)
```

## Baseline characteristics by whether participants were followed-up and interviewed at incidence phase versus lost to follow-up

```{r}
temp = data %>% 
  left_join(status_outcome, by = c("houseid2", "PARTICID")) %>% 
  mutate(fu = factor(if_else(Statusfu=="Died" | Statusfu=="Interviewed", 1, 0, missing=0)))

vars = c("age", "gender", "PMARRY", "PEDUC", "Nassets", "illnocat", "CARENEED", "pnism", "PD")
factorVars = c("gender", "PMARRY", "PEDUC", "Nassets",  "illnocat", "CARENEED", "pnism", "PD")

# include missing as a separate factor level
tab_fu = tableone::CreateTableOne(data = temp,
                                vars = vars,
                                factorVars = factorVars,
                                strata = c("fu"),
                                includeNA = TRUE,
                                addOverall = TRUE)

table_fu = print(tab_fu)
```

Save table

```{r}
write.csv(table_fu, here::here("Output", "PD and frailty paper", "Table1_follow-up.csv"))
```

## Baseline characteristics by frailty status at follow-up

```{r, include=FALSE}
vars = c("age", "gender", "PMARRY", "PEDUC", "Nassets", "illnocat", "CARENEED", "pnism", "PD")
factorVars = c("gender", "PMARRY", "PEDUC", "Nassets",  "illnocat", "CARENEED", "pnism", "PD")

# include missing as a separate factor level
tab_fp = tableone::CreateTableOne(data = data_fp,
                                vars = vars,
                                factorVars = factorVars,
                                strata = c("i_fp.frail"),
                               #includeNA = TRUE,
                                addOverall = TRUE)

table_fp = print(tab_fp)

tab_mf = tableone::CreateTableOne(data = data_mf,
                                vars = vars,
                                factorVars = factorVars,
                                strata = c("i_mf.frail"),
                               #includeNA = TRUE,
                                addOverall = TRUE)

table_mf = print(tab_mf)

tab_fi = tableone::CreateTableOne(data = data_fi,
                                vars = vars,
                                factorVars = factorVars,
                                strata = c("i_fi.frail"),
                               #includeNA = TRUE,
                                addOverall = TRUE)

table_fi = print(tab_fi)
```

Save tables

```{r}
write.csv(table_fp, here::here("Output", "PD and frailty paper", "Table1_fp.csv"))
write.csv(table_mf, here::here("Output", "PD and frailty paper", "Table1_mf.csv"))
write.csv(table_fi, here::here("Output", "PD and frailty paper", "Table1_fi.csv"))
```

# Cross-sectional association between Parkinsonism/PD and frailty at baseline (complete case analysis)

## Logistic regression: site-specific estimates

Create function to run logistic regression models

```{r}
func_logreg = function(data, outcome, exposure, adj, country){
  
  # Create an empty output df
  output = data.frame(
    outcome = NA,
    exposure = NA,
    study.site = NA,
    ors = NA,
    estimate = NA,
    std.error = NA
  )
  
  # List countries to iterate logistic regression through
  #countries = c("Cuba", "DR", "Peru (urban)", "Peru (rural)", "Venezuela", "Mexico (urban)", "Mexico (rural)", "Puerto Rico")
  countries = c("Cuba", "Dominican Republic", "Peru", "Venezuela", "Mexico", "Puerto Rico")
  
  # Formula for the logistic regression
  formula = as.formula(paste0(outcome, " ~ ", exposure, adj))
  
  for (i in countries){
    # logistic regression
    model = glm(formula, family = binomial(link="logit"), data=data, subset=countryid==i) # make sure subset column is correct - either centreid or countryid
  
    temp = tidy(model, conf.int = TRUE, conf.level = 0.95, exponentiate = TRUE) %>% # process regression output
      mutate(ors = paste0(format.pval(round(estimate,2),nsmall=2), " (", format.pval(round(conf.low,2),nsmall=2),"-", format.pval(round(conf.high,2),nsmall=2),")")) %>% 
      mutate(estimate = log(estimate)) %>% 
      select(exposure=term, ors, estimate, std.error)
    
    temp$outcome = outcome # label outcome
    temp$study.site = i #label study site
    
    temp = temp[temp$exposure==exposure, ] # select ORs for exposure of interest
    
    output = bind_rows(output, temp)
  
  }
  
  return(output)
  
}
```

Run models

```{r, message=FALSE, warning=FALSE}
adjustments = " + age + gender + PEDUC"

################# Parkinsonism #####################

# FP
ors_pnism_fp_crude = func_logreg(data=data_base_complete, outcome="b_fp.frail", exposure="pnism", adj="")
ors_pnism_fp_adj = func_logreg(data=data_base_complete, outcome="b_fp.frail", exposure="pnism", adj= adjustments)

# Multidimensional frailty
ors_pnism_mf_crude = func_logreg(data=data_base_complete, outcome="b_mf.frail", exposure="pnism", adj="")
ors_pnism_mf_adj = func_logreg(data=data_base_complete, outcome="b_mf.frail", exposure="pnism", adj= adjustments)

# FI
ors_pnism_fi_crude = func_logreg(data=data_base_complete, outcome="b_fi.frail", exposure="pnism", adj="")
ors_pnism_fi_adj = func_logreg(data=data_base_complete, outcome="b_fi.frail", exposure="pnism", adj= adjustments)

################# PD #####################

# FP
ors_pd_fp_crude = func_logreg(data=data_base_complete, outcome="b_fp.frail", exposure="PD", adj="")
ors_pd_fp_adj = func_logreg(data=data_base_complete, outcome="b_fp.frail", exposure="PD", adj=adjustments)

# Multidimensional frailty
ors_pd_mf_crude = func_logreg(data=data_base_complete, outcome="b_mf.frail", exposure="PD", adj="")
ors_pd_mf_adj = func_logreg(data=data_base_complete, outcome="b_mf.frail", exposure="PD", adj=adjustments)

# FI
ors_pd_fi_crude = func_logreg(data=data_base_complete, outcome="b_fi.frail", exposure="PD", adj="")
ors_pd_fi_adj = func_logreg(data=data_base_complete, outcome="b_fi.frail", exposure="PD", adj=adjustments)
```

## Logistic regression: meta-analysis

Run random-effects model, assumes there are 2 sources of error: 1) sampling error and 2) variance from the fact that included study sites are not from a single, homogeneous population, thus there is distribution of true effect sizes. Thus, the random-effects model aims to model the mean of the distribution of true effects.

Create function to plot forest plot

```{r}
plot_forest_meta = function(results){
  
  mgen = meta::metagen(TE = estimate,                           # make sure log(OR) than OR only
                       seTE = std.error,
                       studlab = study.site,
                       sm = "OR",
                       fixed = TRUE,
                       random = FALSE,
                       method.tau = "DL",                       # DerSimonian-Laird estimator
                       hakn = TRUE,                             # Hartung-Knapp adjustment of SEs
                       prediction = FALSE,                       # the above line and this line allow more   uncertainty in the estimation of between-study heterogeneity and appropriate for use in random-effects   meta-analysis
                       data = results)
  
  meta::forest(mgen, 
             rightlabs = c("OR", "95% CI", "Weight"),
             print.tau2 = FALSE,
             leftcols = c("studlab"))
  
  plot = grid.grab() 
  
  return(plot)

}
```

### Parkinsonism and frailty (adjusted for age, sex, education)

```{r, fig.width = 10, fig.height = 6}
plot_pnism_fp_adj = plot_forest_meta(ors_pnism_fp_adj[-1, ])
plot_pnism_mf_adj = plot_forest_meta(ors_pnism_mf_adj[-1, ])
plot_pnism_fi_adj = plot_forest_meta(ors_pnism_fi_adj[-1, ])
```

### PD and frailty (adjusted for age, sex, education)

```{r, fig.width = 10, fig.height = 6}
plot_pd_fp_adj = plot_forest_meta(ors_pd_fp_adj[-c(1), ])
plot_pd_mf_adj = plot_forest_meta(ors_pd_mf_adj[-c(1), ])
plot_pd_fi_adj = plot_forest_meta(ors_pd_fi_adj[-c(1), ])
```

## Combine and save outputs

```{r}
plot_combined_pnism_adj = cowplot::plot_grid(plot_pnism_fp_adj, plot_pnism_mf_adj, plot_pnism_fi_adj,
                                         align = "hv",
                                         labels = "AUTO", 
                                         scale = 0.5,
                                         ncol = 1)

ggsave(plot = plot_combined_pnism_adj, filename = here::here("Output", "PD and frailty paper", "plots", "ors_pnism_frailty_adj.png"), width = 18, height = 24, units = "cm")

plot_combined_pd_adj = cowplot::plot_grid(plot_pd_fp_adj, plot_pd_mf_adj, plot_pd_fi_adj,
                                         align = "hv",
                                         labels = "AUTO", 
                                         scale = 0.5,
                                         ncol = 1)

ggsave(plot = plot_combined_pd_adj, filename = here::here("Output", "PD and frailty paper", "plots", "ors_pd_frailty_adj.png"), width = 18, height = 24, units = "cm")
```

# Prospective association between Parkinsonism/PD and incident frailty (complete case analysis)

## Open and merge mortality data

Open mortality status

```{r}
path = here::here("Data", "raw data", "fu folder from Matthew", "specific outcomes", "mortality", "mortality_outcome1_1.dta")
mortality_outcome = open_and_process_data(path, "dta")
```

Merge vital status

```{r}
# baseline data:
# houseid2 is composite of centreid and houseid (houseid has 4 digits)
# therefore, unique participant-level id = composite of houseid2 and PARTICID

# status_outcome_mortality_cohort:
# need to create houseid2 by combining centreid and houseid (need to add leading 0s up to 4 digits first)
# centreid
# - 10 Cuba
# - 20 Dominican Republic
# - 30 Peru (urban)
# - 40 Peru (rural)
# - 50 Venezuela
# - 60 Mexico (urban)
# - 70 Mexico (rural)
# - 100 China (urban)
# - 110 China (rural)
# - 200 Puerto Rico

# Create houseid2
mortality_outcome = mortality_outcome %>% 
  mutate(centreid_num = case_when(centreid == "Cuba" ~ 10,
                                  centreid == "DR" ~ 20,
                                  centreid == "Peru (urban)" ~ 30,
                                  centreid == "Peru (rural)" ~ 40,
                                  centreid == "Venezuela" ~ 50,
                                  centreid == "Mexico (urban)" ~ 60,
                                  centreid == "Mexico (rural)" ~ 70,
                                  centreid == "China (urban)" ~ 100,
                                  centreid == "China (rural)" ~ 110,
                                  centreid == "Puerto Rico" ~ 200)) %>% 
  mutate(HOUSEID = stringr::str_pad(HOUSEID, 4, pad="0")) %>% 
  mutate(houseid2 = as.numeric(paste0(centreid_num, HOUSEID))) %>% 
  select(houseid2, PARTICID, dead2, censor_days, censor_yr, vital_ascertained)

# Merge vital status with data
data_fp1 = data_fp %>% left_join(mortality_outcome, by = c("houseid2", "PARTICID"))
data_mf1 = data_mf %>% left_join(mortality_outcome, by = c("houseid2", "PARTICID"))
data_fi1 = data_fi %>% left_join(mortality_outcome, by = c("houseid2", "PARTICID"))
```

## Create outcome variable

```{r}
data_fp1 = data_fp1 %>% 
  mutate(status = if_else(i_fp.frail==1, 1, 0, missing=0),
         status2 = case_when(Statusfu=="Died" ~ 2, i_fp.frail==1 ~ 1, TRUE ~ 0),
         time = case_when(i_fp.frail==1 ~ censor_days/2, TRUE ~ censor_days),
         time2 = case_when(i_fp.frail==1 ~ censor_days/4, TRUE ~ censor_days),
         time3 = case_when(i_fp.frail==1 ~ 3*censor_days/4, TRUE ~ censor_days))

data_mf1 = data_mf1 %>% 
  mutate(status = if_else(i_mf.frail==1, 1, 0, missing=0),
         status2 = case_when(Statusfu=="Died" ~ 2, i_mf.frail==1 ~ 1, TRUE ~ 0),
         time = case_when(i_mf.frail==1 ~ censor_days/2, TRUE ~ censor_days),
         time2 = case_when(i_mf.frail==1 ~ censor_days/4, TRUE ~ censor_days),
         time3 = case_when(i_mf.frail==1 ~ 3*censor_days/4, TRUE ~ censor_days))

data_fi1 = data_fi1 %>% 
  mutate(status = if_else(i_fi.frail==1, 1, 0, missing=0),
         status2 = case_when(Statusfu=="Died" ~ 2, i_fi.frail==1 ~ 1, TRUE ~ 0),
         time = case_when(i_fi.frail==1 ~ censor_days/2, TRUE ~ censor_days),
         time2 = case_when(i_fi.frail==1 ~ censor_days/4, TRUE ~ censor_days),
         time3 = case_when(i_fi.frail==1 ~ 3*censor_days/4, TRUE ~ censor_days))
```

## Cox proportional hazards regression model (cause-specific hazards)

Check PH assumption

```{r}
res.cox = survival::coxph(Surv(time, status) ~ PD, data = data_fp1)
test.ph = survival::cox.zph(res.cox)
test.ph

res.cox = survival::coxph(Surv(time, status) ~ PD + age + gender + PEDUC, data = data_fp1)
test.ph = survival::cox.zph(res.cox)
test.ph
```

Check if stratification fixes this

```{r}
res.cox = survival::coxph(Surv(time, status) ~ PD + age + gender + strata(PEDUC), data = data_fp1)
test.ph = survival::cox.zph(res.cox)
test.ph
```

Create function to run CoxPH regression models

```{r}
func_coxph = function(data, status, exposure, adj, time){
  
  # Create an empty output df
  output = data.frame(
    status = NA,
    sensitivity = NA,
    exposure = NA,
    adj = NA,
    hrs = NA
  )
  
  # Formula for the Cox PH regression
  outcome = paste0("Surv(", time, ", ", status, ")")
  formula = as.formula(paste0(outcome, " ~ ", exposure, adj))
    
  model = coxph(formula, data=data) # cox regression
  
  temp = tidy(model, conf.int = TRUE, conf.level = 0.95, exponentiate = TRUE) %>% # process regression output
    mutate(hrs = paste0(format.pval(round(estimate,2),nsmall=2), " (", format.pval(round(conf.low,2),nsmall=2),"-", format.pval(round(conf.high,2),nsmall=2),")")) %>% 
    mutate(estimate = log(estimate)) %>% 
    select(exposure=term, hrs)
    
  temp$status = status
  temp$sensitivity = time
  
  if (adj==""){
    temp$adj = "crude"
  } else {
    temp$adj = "adjusted"
  }
  
  temp = temp[temp$exposure==exposure, ] # select ORs for exposure of interest
    
  output = bind_rows(output, temp)
  
 return(output)
  
}
```

Run models

```{r, message=FALSE, warning=FALSE}
# Time = frailty occurs midpoint between baseline and incidence questionnaire
hrs_fp_pnism_crude = func_coxph(data=data_fp1, status="status", exposure="pnism", adj="", time="time")
hrs_mf_pnism_crude = func_coxph(data=data_mf1, status="status", exposure="pnism", adj="", time="time")
hrs_fi_pnism_crude = func_coxph(data=data_fi1, status="status", exposure="pnism", adj="", time="time")
hrs_fp_pnism_adj = func_coxph(data=data_fp1, status="status", exposure="pnism", adj=" + age + gender + strata(PEDUC)", time="time")
hrs_mf_pnism_adj = func_coxph(data=data_mf1, status="status", exposure="pnism", adj=" + age + gender + strata(PEDUC)", time="time")
hrs_fi_pnism_adj = func_coxph(data=data_fi1, status="status", exposure="pnism", adj=" + age + gender + strata(PEDUC)", time="time")

hrs_fp_pd_crude = func_coxph(data=data_fp1, status="status", exposure="PD", adj="", time="time")
hrs_mf_pd_crude = func_coxph(data=data_mf1, status="status", exposure="PD", adj="", time="time")
hrs_fi_pd_crude = func_coxph(data=data_fi1, status="status", exposure="PD", adj="", time="time")
hrs_fp_pd_adj = func_coxph(data=data_fp1, status="status", exposure="PD", adj=" + age + gender + strata(PEDUC)", time="time")
hrs_mf_pd_adj = func_coxph(data=data_mf1, status="status", exposure="PD", adj=" + age + gender + strata(PEDUC)", time="time")
hrs_fi_pd_adj = func_coxph(data=data_fi1, status="status", exposure="PD", adj=" + age + gender + strata(PEDUC)", time="time")

# Combine data
hrs_time_fp = mget(ls(pattern = 'hrs_fp')) %>%
  bind_rows() %>% 
  filter(complete.cases(.)) %>% 
  arrange(desc(exposure), desc(adj))

hrs_time_mf = mget(ls(pattern = 'hrs_mf')) %>%
  bind_rows() %>% 
  filter(complete.cases(.)) %>% 
  arrange(desc(exposure), desc(adj))

hrs_time_fi = mget(ls(pattern = 'hrs_fi')) %>%
  bind_rows() %>% 
  filter(complete.cases(.)) %>% 
  arrange(desc(exposure), desc(adj))
```

## Sensitivity analyses

Uses different time points at which frailty is assumed to occur

```{r, message=FALSE, warning=FALSE}
# Time = frailty occurs 1/4 between baseline and incidence questionnaire
hrs_fp_pnism_crude = func_coxph(data=data_fp1, status="status", exposure="pnism", adj="", time="time2")
hrs_mf_pnism_crude = func_coxph(data=data_mf1, status="status", exposure="pnism", adj="", time="time2")
hrs_fi_pnism_crude = func_coxph(data=data_fi1, status="status", exposure="pnism", adj="", time="time2")
hrs_fp_pnism_adj = func_coxph(data=data_fp1, status="status", exposure="pnism", adj=" + age + gender + strata(PEDUC)", time="time2")
hrs_mf_pnism_adj = func_coxph(data=data_mf1, status="status", exposure="pnism", adj=" + age + gender + strata(PEDUC)", time="time2")
hrs_fi_pnism_adj = func_coxph(data=data_fi1, status="status", exposure="pnism", adj=" + age + gender + strata(PEDUC)", time="time2")

hrs_fp_pd_crude = func_coxph(data=data_fp1, status="status", exposure="PD", adj="", time="time2")
hrs_mf_pd_crude = func_coxph(data=data_mf1, status="status", exposure="PD", adj="", time="time2")
hrs_fi_pd_crude = func_coxph(data=data_fi1, status="status", exposure="PD", adj="", time="time2")
hrs_fp_pd_adj = func_coxph(data=data_fp1, status="status", exposure="PD", adj=" + age + gender + strata(PEDUC)", time="time2")
hrs_mf_pd_adj = func_coxph(data=data_mf1, status="status", exposure="PD", adj=" + age + gender + strata(PEDUC)", time="time2")
hrs_fi_pd_adj = func_coxph(data=data_fi1, status="status", exposure="PD", adj=" + age + gender + strata(PEDUC)", time="time2")

# Combine data
hrs_time2_fp = mget(ls(pattern = 'hrs_fp')) %>%
  bind_rows() %>% 
  filter(complete.cases(.)) %>% 
  arrange(desc(exposure), desc(adj))

hrs_time2_mf = mget(ls(pattern = 'hrs_mf')) %>%
  bind_rows() %>% 
  filter(complete.cases(.)) %>% 
  arrange(desc(exposure), desc(adj))

hrs_time2_fi = mget(ls(pattern = 'hrs_fi')) %>%
  bind_rows() %>% 
  filter(complete.cases(.)) %>% 
  arrange(desc(exposure), desc(adj))
```

```{r, message=FALSE, warning=FALSE}
# Time = frailty occurs 3/4 between baseline and incidence questionnaire
hrs_fp_pnism_crude = func_coxph(data=data_fp1, status="status", exposure="pnism", adj="", time="time3")
hrs_mf_pnism_crude = func_coxph(data=data_mf1, status="status", exposure="pnism", adj="", time="time3")
hrs_fi_pnism_crude = func_coxph(data=data_fi1, status="status", exposure="pnism", adj="", time="time3")
hrs_fp_pnism_adj = func_coxph(data=data_fp1, status="status", exposure="pnism", adj=" + age + gender + strata(PEDUC)", time="time3")
hrs_mf_pnism_adj = func_coxph(data=data_mf1, status="status", exposure="pnism", adj=" + age + gender + strata(PEDUC)", time="time3")
hrs_fi_pnism_adj = func_coxph(data=data_fi1, status="status", exposure="pnism", adj=" + age + gender + strata(PEDUC)", time="time3")

hrs_fp_pd_crude = func_coxph(data=data_fp1, status="status", exposure="PD", adj="", time="time3")
hrs_mf_pd_crude = func_coxph(data=data_mf1, status="status", exposure="PD", adj="", time="time3")
hrs_fi_pd_crude = func_coxph(data=data_fi1, status="status", exposure="PD", adj="", time="time3")
hrs_fp_pd_adj = func_coxph(data=data_fp1, status="status", exposure="PD", adj=" + age + gender + strata(PEDUC)", time="time3")
hrs_mf_pd_adj = func_coxph(data=data_mf1, status="status", exposure="PD", adj=" + age + gender + strata(PEDUC)", time="time3")
hrs_fi_pd_adj = func_coxph(data=data_fi1, status="status", exposure="PD", adj=" + age + gender + strata(PEDUC)", time="time3")

# Combine data
hrs_time3_fp = mget(ls(pattern = 'hrs_fp')) %>%
  bind_rows() %>% 
  filter(complete.cases(.)) %>% 
  arrange(desc(exposure), desc(adj))

hrs_time3_mf = mget(ls(pattern = 'hrs_mf')) %>%
  bind_rows() %>% 
  filter(complete.cases(.)) %>% 
  arrange(desc(exposure), desc(adj))

hrs_time3_fi = mget(ls(pattern = 'hrs_fi')) %>%
  bind_rows() %>% 
  filter(complete.cases(.)) %>% 
  arrange(desc(exposure), desc(adj))
```

```{r, message=FALSE, warning=FALSE}
# Status = status2 (cause-specific hazards considering death as a competing outcome)
# Time = frailty occurs midpoint between baseline and incidence questionnaire
hrs_fp_pnism_crude = func_coxph(data=data_fp1, status="status2==1", exposure="pnism", adj="", time="time")
hrs_mf_pnism_crude = func_coxph(data=data_mf1, status="status2==1", exposure="pnism", adj="", time="time")
hrs_fi_pnism_crude = func_coxph(data=data_fi1, status="status2==1", exposure="pnism", adj="", time="time")
hrs_fp_pnism_adj = func_coxph(data=data_fp1, status="status2==1", exposure="pnism", adj=" + age + gender + strata(PEDUC)", time="time")
hrs_mf_pnism_adj = func_coxph(data=data_mf1, status="status2==1", exposure="pnism", adj=" + age + gender + strata(PEDUC)", time="time")
hrs_fi_pnism_adj = func_coxph(data=data_fi1, status="status2==1", exposure="pnism", adj=" + age + gender + strata(PEDUC)", time="time")

hrs_fp_pd_crude = func_coxph(data=data_fp1, status="status2==1", exposure="PD", adj="", time="time")
hrs_mf_pd_crude = func_coxph(data=data_mf1, status="status2==1", exposure="PD", adj="", time="time")
hrs_fi_pd_crude = func_coxph(data=data_fi1, status="status2==1", exposure="PD", adj="", time="time")
hrs_fp_pd_adj = func_coxph(data=data_fp1, status="status2==1", exposure="PD", adj=" + age + gender + strata(PEDUC)", time="time")
hrs_mf_pd_adj = func_coxph(data=data_mf1, status="status2==1", exposure="PD", adj=" + age + gender + strata(PEDUC)", time="time")
hrs_fi_pd_adj = func_coxph(data=data_fi1, status="status2==1", exposure="PD", adj=" + age + gender + strata(PEDUC)", time="time")

# Save data
hrs_csh_time_fp = mget(ls(pattern = 'hrs_fp')) %>%
  bind_rows() %>% 
  filter(complete.cases(.)) %>% 
  arrange(desc(exposure), desc(adj))

hrs_csh_time_mf = mget(ls(pattern = 'hrs_mf')) %>%
  bind_rows() %>% 
  filter(complete.cases(.)) %>% 
  arrange(desc(exposure), desc(adj))

hrs_csh_time_fi = mget(ls(pattern = 'hrs_fi')) %>%
  bind_rows() %>% 
  filter(complete.cases(.)) %>% 
  arrange(desc(exposure), desc(adj))
```

Combine and save data

```{r}
hrs_fp = list(hrs_time_fp, hrs_time2_fp, hrs_time3_fp, hrs_csh_time_fp) %>% bind_rows() 
hrs_mf = list(hrs_time_mf, hrs_time2_mf, hrs_time3_mf, hrs_csh_time_mf) %>% bind_rows()
hrs_fi = list(hrs_time_fi, hrs_time2_fi, hrs_time3_fi, hrs_csh_time_fi) %>% bind_rows()

save_hrs = hrs_fp %>% 
  select(status, sensitivity, exposure, adj, hrs.fp=hrs) %>% 
  left_join(select(hrs_mf, status, sensitivity, exposure, adj, hrs.mf=hrs), by = c("status", "sensitivity", "exposure", "adj")) %>% 
  left_join(select(hrs_fi, status, sensitivity, exposure, adj, hrs.fi=hrs), by = c("status", "sensitivity", "exposure", "adj")) %>% 
  arrange(status, sensitivity, desc(exposure), desc(adj))

save_hrs

write.csv(save_hrs, here::here("Output", "PD and frailty paper", "Table_hrs.csv"))
```
