---
title: "Multiple imputation analysis of cross-sectional associations"
output: html_document
date: "2023-10-04"
---

Multiple imputation analysis of the cross-sectional associations between parkinsonism and PD with frailty (defined according to the Fried frailty phenotype, multidimensional frailty, and Rockwood frailty index) using the baseline 10/66 survey.

## Open dataset and libraries

Libraries
```{r}
library(cowplot)
library(data.table)
library(here)         # for easy file referencing by using the top-level directory of a file project
library(gridGraphics) # for grid.grab()
library(kableExtra)
library(knitr)
library(meta)
library(mice)
library(tidyverse)
```

Source codes
```{r}
source(here::here("Script", "Functions", "Data process", "func_open_and_process_data.R"))
```

Open Baseline phase data

```{r}
# Create data path
path = here::here("Data", "raw data", "baseline survey", "prevalence_survey_data_1_3.dta")

# Open and process data
data_baseline = open_and_process_data(path, "dta") # this function opens a Stata dataset (dta) and converts Stata's labelled variables into factors

# Subset participants in Latin America
data_baseline = data_baseline %>% 
  filter(centreid %in% c("Cuba", "DR", "Peru (urban)", "Peru (rural)", "Venezuela", "Mexico (urban)", "Mexico (rural)", "Puerto Rico"))

# drop unused factor levels
data_baseline$centreid = droplevels(data_baseline$centreid)
data_baseline$countryid = droplevels(data_baseline$countryid)
  
data_baseline$countryid = factor(data_baseline$countryid, levels = c("Cuba", "DR", "Peru", "Venezuela", "Mexico", "Puerto Rico"),
                        labels = c("Cuba", "Dominican Republic", "Peru", "Venezuela", "Mexico", "Puerto Rico"))

# Select relevant variables for frailty 
data_base = data_baseline %>% 
  select(houseid2, PARTICID, countryid, centreid, age, gender, PMARRY, PEDUC, Nassets, illnocat, CARENEED, # demographic variables
         NEO14G, NEO6AU, NEO6AL, NEO6BU, NEO6BL, NEO4E, NEO4F, NOE1, NEO14E, PCVA, PARK, # parkinsonism and PD variables
         Q531, Q481, NEO12B, PDAS7, PACTIVE, # FP variables
         cogscore, peyeint, pearint, ARMCIRC, # MF variables 
         Q1705, q17912, cvadiag, cdem1066, PARTH, PCOUGH, PRESP, hyperten, heartisc,
         PGUT, PSKIN, PTOLDDM, PEYE, PEAR, WSTCIRC, HIPCIRC, 
         euro6, Q871, SRQ18, SRQ20, Q451) %>% 
  mutate(whr = WSTCIRC/HIPCIRC)

# View data
temp = data_base %>% 
  select(-houseid2, -PARTICID) %>%
  mutate(PEDUC = fct_recode(PEDUC, NULL = "6"),
         NOE1 = fct_recode(NOE1, NULL = "7")) %>% # exclude factor levels with very low counts
  mutate(WSTCIRC = if_else(WSTCIRC>500, NA_real_, WSTCIRC)) %>% # exclude extreme values
  mutate(across(c(everything(), -age, -cogscore, -ARMCIRC, -WSTCIRC, -HIPCIRC, -whr, -NEO12B), ~as.factor(.x)))
summary(temp)

temp %>% 
  select_if(is.numeric) %>% 
  map2(., .y=colnames(.), ~ggplot(temp, aes(x=.x)) +
         geom_histogram() + 
         xlab(.y)
       )
```

## Calculate missingness in PD and frailty variables

```{r}
tab_missing = as.data.frame(map(temp, ~mean(is.na(.))*100)) %>% 
  pivot_longer(cols = everything(), names_to = "Variable", values_to = "Missing_pct") %>% 
  mutate(Missing_pct = round(Missing_pct, 1))

# Label variables
demovars = c("age", "gender", "PMARRY", "PEDUC", "Nassets", "illnocat", "CARENEED", "countryid", "centreid")
pdvars = c("NEO14G", "NEO6AU", "NEO6AL", "NEO6BU", "NEO6BL", "NEO4E", "NEO4F", "NOE1", "NEO14E", "PCVA", "PARK")
fpvars = c("Q531", "Q481", "NEO12B", "PDAS7", "PACTIVE")
mfvars = c("NEO12B", "PDAS7", "cogscore", "peyeint", "pearint", "ARMCIRC")
fivars = c("Q1705", "q17912", "cvadiag", "cdem1066", "PARTH", "PCOUGH", "PRESP", "hyperten", "heartisc",
         "PGUT", "PSKIN", "PTOLDDM", "PEYE", "PEAR", "WSTCIRC", "HIPCIRC", 
         "euro6", "Q871", "SRQ18", "SRQ20", "Q451",
         "Q531", "Q481", "PACTIVE", "cogscore", "ARMCIRC")

tab_missing = tab_missing %>% 
  mutate(demographic = if_else(Variable %in% demovars, "X", NA_character_),
         pd = if_else(Variable %in% pdvars, "X", NA_character_),
         fp = if_else(Variable %in% fpvars, "X", NA_character_),
         mf = if_else(Variable %in% mfvars, "X", NA_character_),
         fi = if_else(Variable %in% fivars, "X", NA_character_)) %>% 
  arrange(Missing_pct)

tab_missing

path = here::here("Output", "PD and frailty paper", "Table_missing_vars.csv")
write.csv(tab_missing, path)
```

The self-reported PD variable (`PARK`) has very high missingness, therefore exclude from the imputation model.

Highest level of missingness is 11% (`NEO12B`), thus 10 imputations likely to be sufficient.

## Multiple imputation

```{r}
# Create a separate df for mice
toimpute = data_base %>% 
  select(-houseid2, -PARTICID, -centreid, -PARK, -whr) %>%     # delete variables not required for imputation
  mutate(PEDUC = fct_recode(PEDUC, NULL = "6"),
         NOE1 = fct_recode(NOE1, NULL = "7")) %>%               # exclude factor levels with very low counts
  mutate(WSTCIRC = if_else(WSTCIRC>500, NA_real_, WSTCIRC)) %>% # make extreme values missing
  mutate(across(c(everything(), -age, -cogscore, -ARMCIRC, -WSTCIRC, -HIPCIRC, -NEO12B), ~as.factor(.x)))  # create factors
  #%>%sample_n(1000) # select a random subset to analyse
```

### Impute data

Using the mice package, impute 10 datasets using 10 iterations (check convergence later).

```{r}
# create initial predictor matrix and imputation methods
ini = mice::mice(toimpute, maxit=0, print=F)
pred = ini$pred
method = ini$meth
method

# Modify predictor matrix if required
#pred[, c("id", "source")]=0 # to exclude predictor from imutation process
#method[c("gender")] = "logreg" # other methods are: pmm, norm, polyreg, polyr
#method[c("PMARRY", "PEDUC", "Nassets", "illnocat", "CARENEED", "NEO14G", "NEO6AU", "NEO6AL", "NEO6BU", "NEO6BL", "NEO4E", "NEO4F", "NOE1", "NEO14E", "Q531", "Q481", "PDAS7", "PACTIVE", "Q1705", "q17912", "PARTH", "PCOUGH", "PRESP", "PGUT", "PSKIN", "PEYE", "PEAR", "Q871", "Q451")] = "pmm"

impnum = 10 # 10 imputations
itnum = 10 # 10 iterations

# Conduct multiple imputation in mice
impData = mice(toimpute, m=impnum, maxit=itnum, seed=123, method=method, predictorMatrix=pred, visitSequence="revmonotone", print=FALSE)
```

Save imputed data as RDS object
```{r}
# Save imputed data as rds file
path = here::here("Output", "PD and frailty paper", "temp_imputed_data.rds")
saveRDS(impData, file=path)
#impData = readRDS(path)
```

### Imputation diagnostic checks

```{r}
# View imputed values, imputation matrix, predictor matrix and the visiting sequence
head(impData$imp$hyperten)

impMethod = impData$method
impPred = impData$predictorMatrix
impSeq = impData$vis # visiting sequence, the sequence with which mice() imputes incomplete variables
  # visitSequence="revmonotone" ordered high to low proportion of missing data

impMethod
head(impPred[ ,1:10])
impSeq
```

### Inspect distribution of imputed and original data

Check there is no missing data

```{r}
#Now look at the "complete" data
for (i in 1:impnum){
 print(anyNA(data.table(complete(impData, i))))
}
```

Density plot

```{r}
densityplot(impData)
```
Blue lines represent the observed data and the purple show the imputed data. The red points differ from each other, which represents uncertainty about the true values of missing data.

### Convergence monitoring

Mean of the imputed values for each iteration

```{r}
impData$chainMean # contains means of the imputed values for each iteration. 
  # No. of chains = No. iteration
  # a chain refers to the chain of regression models that is used to generate the imputed values
```

Trace plots

```{r}
plot(impData) # layout=c(col,row)
```

mice() runs m parallel chains, each with a certain number of iterations and imputes values from the final iteration. View trace plots to monitor convergence, which plot estimates against the number of iterations. If the variance between the imputation chain is almost equal to the variance within the chains, it is an indication of healthy convergence.

## Analysis of multiply imputed datasets

Compute new variables in each imputed dataset

```{r}
all.impdata = complete(impData, "long", include=TRUE)

all.impdata = all.impdata %>% 
  # compute waist-to-hip ratio
  mutate(whr = WSTCIRC/HIPCIRC) %>% 
  # compute FP
  mutate(b_weight_loss = case_when(Q531==1 ~ 1, 
                                   Q531==0 ~ 0, 
                                   TRUE ~ NA_real_),
         b_exhaust = case_when(Q481==1 | Q481==2 ~ 1, 
                               Q481==0 ~ 0,
                               TRUE ~ NA_real_),
         walkdiff = case_when(PDAS7=="none" | PDAS7=="mild difficulty" | PDAS7=="moderate difficulty" ~ 0,
                              PDAS7=="severe difficulty" | PDAS7=="extreme difficulty/ cannot do" ~ 1,
                              TRUE ~ NA_real_),         
         walkslow = case_when(NEO12B>=1 & NEO12B<16 ~ 0,
                              NEO12B>=16 & NEO12B<992 ~ 1, 
                              TRUE ~ NA_real_),
         b_walkslow = case_when(walkdiff==0 & (is.na(NEO12B) | NEO12B==0) ~ 0,
                                walkdiff==1 & (is.na(NEO12B) | NEO12B==0) ~ 1,
                                walkdiff==0 & is.na(NEO12B) ~ 0,
                                TRUE ~ walkslow),
         b_underactive = if_else(PACTIVE=="not at all", 1, 0)) %>% 
  mutate(b_fp.count = rowSums(.[c("b_weight_loss", "b_exhaust", "b_walkslow", "b_underactive")], na.rm=FALSE),
         b_fp.frail = as.factor(if_else(b_fp.count>=2, 1, 0))) %>% 
  # compute MF
  mutate(b_cognition = if_else(cogscore<29.5, 1, 0),
         b_sensory = case_when(peyeint=="yes" | pearint=="yes" ~ 1,
                             is.na(peyeint) & is.na(pearint) ~ NA_real_,
                             TRUE ~ 0),
         b_nutrition = if_else(ARMCIRC<22, 1, 0),
         b_physical = b_walkslow) %>% 
  mutate(b_mf.count = rowSums(.[c("b_cognition", "b_sensory", "b_nutrition", "b_physical")], na.rm=FALSE),
         b_mf.frail = as.factor(if_else(b_mf.count>=2, 1, 0))) %>% 
  # Compute FI
  mutate(b_fi_active = case_when(PACTIVE=="very physically active" ~ 0,
                               PACTIVE=="fairly" ~ 0.3,
                               PACTIVE=="not very" ~ 0.6,
                               PACTIVE=="not at all" ~ 1,
                               TRUE ~ NA_real_),
         b_fi_weight_loss = case_when(Q531==0 ~ 0,
                                    Q531==1 ~ 1,
                                    TRUE ~ NA_real_),
         b_fi_exhaust = case_when(Q481==0 ~ 0,
                                Q481==1 ~ 0.5,
                                Q481==2 ~ 1,
                                TRUE ~ NA_real_),
         b_fi_stroke = case_when(cvadiag=="no" ~ 0,
                               cvadiag=="yes" ~ 1,
                               TRUE ~ NA_real_),
         b_fi_dementia = case_when(cdem1066=="non-case" ~ 0,
                                 cdem1066=="case" ~ 1,
                                 TRUE ~ NA_real_),
         b_fi_arth = case_when(PARTH=="no problem" ~ 0,
                             PARTH=="has problem, interferes not at all" ~ 0,
                             PARTH=="has problem, interferes a little" ~ 0.5,
                             PARTH=="has problem, interferes a lot" ~ 1,
                             TRUE ~ NA_real_),
         b_fi_cough = case_when(PCOUGH=="no problem" ~ 0,
                             PCOUGH=="has problem, interferes not at all" ~ 0,
                             PCOUGH=="has problem, interferes a little" ~ 0.5,
                             PCOUGH=="has problem, interferes a lot" ~ 1,
                             TRUE ~ NA_real_),
         b_fi_resp = case_when(PRESP=="no problem" ~ 0,
                             PRESP=="has problem, interferes not at all" ~ 0,
                             PRESP=="has problem, interferes a little" ~ 0.5,
                             PRESP=="has problem, interferes a lot" ~ 1,
                             TRUE ~ NA_real_),
         b_fi_hyperten = case_when(hyperten=="no" ~ 0,
                                 hyperten=="yes" ~ 1,
                                 TRUE ~ NA_real_),
         b_fi_heartisc = case_when(heartisc=="no" ~ 0,
                                 heartisc=="yes" ~ 1,
                                 TRUE ~ NA_real_),
         b_fi_gut = case_when(PGUT=="no problem" ~ 0,
                            PGUT=="has problem, interferes not at all" ~ 0,
                            PGUT=="has problem, interferes a little" ~ 0.5,
                            PGUT=="has problem, interferes a lot" ~ 1,
                            TRUE ~ NA_real_),
         b_fi_skin = case_when(PSKIN=="no problem" ~ 0,
                            PSKIN=="has problem, interferes not at all" ~ 0,
                            PSKIN=="has problem, interferes a little" ~ 0.5,
                            PSKIN=="has problem, interferes a lot" ~ 1,
                            TRUE ~ NA_real_),
         b_fi_diabetes = case_when(PTOLDDM=="no" ~ 0,
                                 PTOLDDM=="yes" ~ 1,
                                 TRUE ~ NA_real_),
         #b_fi_copd = case_when(COAD=="does not met criteria for COPD" ~ 0,
        #                     COAD=="meets criteria for COPD" ~ 1,
        #                     TRUE ~ NA_real_),
         b_fi_eye = case_when(PEYE=="no problem" ~ 0,
                            PEYE=="has problem, interferes not at all" ~ 0,
                            PEYE=="has problem, interferes a little" ~ 0.5,
                            PEYE=="has problem, interferes a lot" ~ 1,
                            TRUE ~ NA_real_),
         b_fi_ear = case_when(PEAR=="no problem" ~ 0,
                            PEAR=="has problem, interferes not at all" ~ 0,
                            PEAR=="has problem, interferes a little" ~ 0.5,
                            PEAR=="has problem, interferes a lot" ~ 1,
                            TRUE ~ NA_real_),
         b_fi_paralysis = case_when(Q1705==1 | Q1705==2 | q17912==1 ~ 1,
                                  Q1705==0 | q17912==0 ~ 0,
                                  TRUE ~ NA_real_),
         b_fi_cognition = if_else(cogscore<29.5, 1, 0),
         b_fi_interest = case_when(euro6=="symptom absent" ~ 0,
                              euro6=="symptom present" ~ 1,
                              TRUE ~ NA_real_),
         b_fi_lonely = case_when(Q871==0 ~ 0,
                               Q871==1 ~ 0.5,
                               Q871==2 ~ 1,
                              TRUE ~ NA_real_),
         #b_fi_socialsupp = case_when(wenger=="family dependent" ~ 0,
        #                    wenger=="locally integrated" ~ 0,
         #                   wenger=="locally self-contained" ~ 1,
         #                   wenger=="wider community focussed" ~ 0,
        #                    wenger=="private" ~ 1,
        #                    TRUE ~ NA_real_),
         b_fi_nutrition = if_else(ARMCIRC<22, 1, 0), 
         b_fi_whr = case_when(whr>2 | is.na(whr) ~ NA_real_,
                            whr>=0.9 & gender=="male" ~ 1,
                            whr>=0.85 & gender=="female" ~ 1,
                            TRUE ~ 0),
         #b_fi_walkdiff = case_when(walkdiff=="no or moderate difficulty in walking 1km" ~ 0, 
        #                         walkdiff=="severe difficulty or cannot walk" ~ 1, 
        #                         TRUE ~ NA_real_),
         b_fi_tired = case_when(SRQ18=="yes, symptom present" | SRQ20=="yes, symptom present" ~ 1,
                              SRQ18=="no" | SRQ20=="no" ~ 0,
                              TRUE ~ NA_real_),
         b_fi_looksfrail = case_when(Q451==0 ~ 0,
                                Q451==1 ~ 0.5,
                                Q451==2 ~ 1,
                                TRUE ~ NA_real_))

all.impdata = all.impdata %>% 
  mutate(b_fi.count = rowSums(across(starts_with("b_fi_")), na.rm=TRUE)) %>% 
  mutate(b_fi.score = b_fi.count/length(all.impdata %>% select(starts_with("b_fi_")) %>% names),
         b_fi.frail = as.factor(if_else(b_fi.score>=0.25, 1, 0)),
         b_fi.cat = factor(case_when(is.na(b_fi.score) ~ NA_character_,
                                   b_fi.score>=0.25 ~ "Frail",
                                   b_fi.score>=0.1 ~ "Pre-frail",
                                   TRUE ~ "Non-frail"), levels = c("Non-frail", "Pre-frail", "Frail")),
         b_fi.score0.1 = b_fi.score/0.1) # to estimate per 0.1 unit effect estimates

all.impdata = all.impdata %>%
    ## Parkinsonism
    # 1. Index individuals with bradykinesia (NEO14G) AND rigidity (NEO6AU/AL/BU/AL)
    mutate(pnism1 = if_else(((NEO14G=="somewhat slow movements" | NEO14G=="very slow movements") & (NEO6AU=="slightly increased tone" | NEO6AU=="much increased tone" |NEO6AL=="slightly increased tone" |NEO6AL=="much increased tone" | NEO6BU=="slightly increased tone" |NEO6BU=="much increased tone" | NEO6BL=="slightly increased tone" | NEO6BL=="much increased tone")), 1, 0)) %>%  
    mutate(pnism1 = if_else(is.na(NEO14G) & (is.na(NEO6AU) | NEO6AU=="normal tone") & (is.na(NEO6AL) | NEO6AL=="normal tone") & (is.na(NEO6BU) | NEO6BU=="normal tone") & (is.na(NEO6BL) | NEO6BL=="normal tone"), NA_real_, pnism1)) %>% 
    # Stata treats missing data differently (removes observations in the calculation when there is missing data), so the above line of codes does that in R
    
    # 2. Index individuals with bradykinesia (NEO14G) AND resting tremor (NEO4E/F)
    mutate(pnism2 = if_else(((NEO14G=="somewhat slow movements" | NEO14G=="very slow movements") & ((!NEO4E=="no tremor") | (!NEO4F=="no tremor"))), 1, 0)) %>% 
    
    # 3. Index individuals with either #1 or #2
    mutate(pnism = if_else(pnism1==1 | pnism2==1, 1, pnism1)) %>% 
    select(-pnism1, -pnism2) %>% 

    ## Parkinson's disease
    mutate(PD = if_else(pnism==1 & (NOE1=="normal upgaze" & NEO14E=="normal gait" & PCVA=="no"), 1, 0)) %>% 
    mutate(PD = if_else(is.na(pnism) & (is.na(NOE1) | is.na(NEO14E) | is.na(PCVA)), NA_real_, PD))

# Convert back to a mids object
new_impData = as.mids(all.impdata)
```

## Baseline characteristics

Mean age
```{r, eval=FALSE}
# Compute mean and standard deviation in each imputed dataset
pool_mean = with(all.impdata, by(all.impdata, .imp, function(x) mean(x$age)))
pool_mean

Reduce("+",pool_mean)/length(pool_mean)
sd(pool_mean) # sd for the mean over the imputed datasets
```

SD age
```{r, eval=FALSE}
# Compute mean and standard deviation in each imputed dataset
pool_mean = with(all.impdata, by(all.impdata, .imp, function(x) sd(x$age)))
pool_mean

Reduce("+",pool_mean)/length(pool_mean)
sd(pool_mean) # sd for the mean over the imputed datasets
```

Prevalence of demographic factors
```{r, eval=FALSE}
# Compute mean and standard deviation in each imputed dataset
pool_prev = with(all.impdata, by(all.impdata, .imp, function(x) c(summary(x$PEDUC),
                                                                  summary(x$PEDUC)/1000,
                                                                  summary(x$Nassets))))
pool_prev

Reduce("+",pool_prev)/length(pool_prev)
```

## Logistic regression

```{r}
func_logreg = function(data, outcome, exposure, adj){
  
  # Create an empty output df
  output = data.frame(
    outcome = NA,
    exposure = NA,
    study.site = NA,
    ors = NA,
    estimate = NA,
    std.error = NA
  )
  
  # List countries to iterate logistic regression through
  #countries = c("Cuba", "DR", "Peru (urban)", "Peru (rural)", "Venezuela", "Mexico (urban)", "Mexico (rural)", "Puerto Rico")
  countries = c("Cuba", "Dominican Republic", "Peru", "Venezuela", "Mexico", "Puerto Rico")
  
  for (i in countries){
    # logistic regression
    fit = with(data=data, {
      formula = as.formula(paste0(outcome, " ~ ", exposure, adj)) # formula for the logistic regression needs to be inside the with() block as we are not passing data= into the modelling function. Otherwise, objects will not be identified
      exp=glm(formula, family=binomial(link='logit'), subset=countryid==i) # make sure subset column is correct - either centreid or countryid
      }) 
  
    temp = summary(pool(fit), conf.int=TRUE, exponentiate=TRUE) %>% 
            mutate(ors = paste0(format.pval(round(estimate,2),nsmall=2), " (", format.pval(round(`2.5 %`,2),nsmall=2),"-", format.pval(round(`97.5 %`,2),nsmall=2),")")) %>% 
            mutate(estimate = log(estimate)) %>% 
            select(exposure=term, ors, estimate, std.error)
    
    temp$outcome = outcome # label outcome
    temp$study.site = i #label study site
    
    temp = temp[temp$exposure==exposure, ] # select ORs for exposure of interest
    
    output = bind_rows(output, temp)
  
  }
  
  return(output)
  
}

```

Run models

```{r, message=FALSE, warning=FALSE}
adjustments = " + age + gender + PEDUC"

################# Parkinsonism #####################

ors_pnism_fp_adj = func_logreg(data=new_impData, outcome="b_fp.frail", exposure="pnism", adj=adjustments)
ors_pnism_mf_adj = func_logreg(data=new_impData, outcome="b_mf.frail", exposure="pnism", adj=adjustments)
ors_pnism_fi_adj = func_logreg(data=new_impData, outcome="b_fi.frail", exposure="pnism", adj=adjustments)

################# PD #####################

ors_pd_fp_adj = func_logreg(data=new_impData, outcome="b_fp.frail", exposure="PD", adj=adjustments)
ors_pd_mf_adj = func_logreg(data=new_impData, outcome="b_mf.frail", exposure="PD", adj=adjustments)
ors_pd_fi_adj = func_logreg(data=new_impData, outcome="b_fi.frail", exposure="PD", adj=adjustments)
```

## Logistic regression: meta-analysis

Run random-effects model, assumes there are 2 sources of error: 1) sampling error and 2) variance from the fact that included study sites are not from a single, homogeneous population, thus there is distribution of true effect sizes. Thus, the random-effects model aims to model the mean of the distribution of true effects.

Create function to plot forest plot

```{r}
plot_forest_meta = function(results){
  
  mgen = meta::metagen(TE = estimate,                           # make sure log(OR) than OR only
                       seTE = std.error,
                       studlab = study.site,
                       sm = "OR",
                       fixed = TRUE,
                       random = FALSE,
                       method.tau = "DL",                       # DerSimonian-Laird estimator
                       hakn = TRUE,                             # Hartung-Knapp adjustment of SEs
                       prediction = FALSE,                       # the above line and this line allow more   uncertainty in the estimation of between-study heterogeneity and appropriate for use in random-effects   meta-analysis
                       data = results)
  
  meta::forest(mgen, 
             rightlabs = c("OR", "95% CI", "Weight"),
             print.tau2 = FALSE,
             leftcols = c("studlab"))
  
  plot = grid::grid.grab() 
  
  return(plot)

}

```

Plot

```{r, fig.width = 10, fig.height = 6}
plot_pnism_fp_adj = plot_forest_meta(ors_pnism_fp_adj[-c(1), ])
plot_pnism_mf_adj = plot_forest_meta(ors_pnism_mf_adj[-c(1), ])
plot_pnism_fi_adj = plot_forest_meta(ors_pnism_fi_adj[-c(1), ])
plot_pd_fp_adj = plot_forest_meta(ors_pd_fp_adj[-c(1), ])
plot_pd_mf_adj = plot_forest_meta(ors_pd_mf_adj[-c(1), ])
plot_pd_fi_adj = plot_forest_meta(ors_pd_fi_adj[-c(1), ])
```

## Combine and save outputs

```{r}
plot_combined_pnism_adj = cowplot::plot_grid(plot_pnism_fp_adj, plot_pnism_mf_adj, plot_pnism_fi_adj,
                                         align = "hv",
                                         labels = "AUTO", 
                                         scale = 0.5,
                                         ncol = 1)

ggsave(plot = plot_combined_pnism_adj, filename = here::here("Output", "PD and frailty paper", "plots", "mi_ors_pnism_frailty_adj.png"), width = 18, height = 24, units = "cm")

plot_combined_pd_adj = cowplot::plot_grid(plot_pd_fp_adj, plot_pd_mf_adj, plot_pd_fi_adj,
                                         align = "hv",
                                         labels = "AUTO", 
                                         scale = 0.5,
                                         ncol = 1)

ggsave(plot = plot_combined_pd_adj, filename = here::here("Output", "PD and frailty paper", "plots", "mi_ors_pd_frailty_adj.png"), width = 18, height = 24, units = "cm")
```
