---
title: "Association between Parkinsonism/PD and mortality"
output: html_document
date: "2022-12-02"
---

### Open libraries

```{r}
library(broom)      # for tidy()
library(cowplot)
library(descr)      # for crosstab(), descriptive statistics package
library(gridGraphics) # for grid.grab()
library(here)       # for easy file referencing by using the top-level directory of a file project
library(knitr)
library(meta)
library(survival)
library(tableone)
library(tidyverse)
```

What is the top-level of current project?

```{r}
here::here()
```

### Open 10/66 baseline dataset

Source codes

```{r}
source(here::here("Script", "Functions", "Data process", "func_open_and_process_data.R"))
source(here::here("Script", "Functions", "Data process", "func_compute_pd_variables.R"))
```

Set path for function input

```{r}
path = here::here("Data", "raw data", "fu folder from Matthew", "specific outcomes", "mortality", "baseline_survey_for_mortality_1_0.sav")
```

Open dataset

```{r}
data = open_and_process_data(path, "sav") # this function opens a Stata dataset (dta) and converts Stata's labelled variables into factors
```

### Open mortality status

```{r}
path = here::here("Data", "raw data", "fu folder from Matthew", "specific outcomes", "mortality", "status_outcome (mortality cohort)_1_0.dta")
status_outcome_mortality_cohort = open_and_process_data(path, "dta")

path = here::here("Data", "raw data", "fu folder from Matthew", "specific outcomes", "mortality", "mortality_outcome1_1.dta")
mortality_outcome = open_and_process_data(path, "dta")
```

### Process dataset

Process Parkinsonism and PD variables

```{r}
data = compute_pd_variables(data)
```

Drop observations from China or India

```{r}
data = data %>% filter(!countryid %in% c("China", "India"))

# drop unused factor levels
data$countryid = droplevels(data$countryid)
```

Subset relevant variables

```{r}
varnames = data %>% 
  select(houseid2, PARTICID, countryid, centreid, age, gender, rural, Nassets, PMARRY, CARENEED, illnocat, cdem1066, PEDUC, PTOLDDM, PSMOKE, PALCNOW, PALCPAST, PACTIVE, PMEATFRQ, PFISHFRQ, PVEGS, NEO14G, NEO6AU, NEO6AL, NEO6BU, NEO6BL, NEO4E, NEO4F, NOE1, NEO14E, PCVA, medserv, PHOSAD, pnism, JorgePD, parkinsonism, PARK) %>% 
  names()

data = data %>% select_if(names(.) %in% varnames)
```

Merge vital status

```{r}
# baseline data:
# houseid2 is composite of centreid and houseid (houseid has 4 digits)
# therefore, unique participant-level id = composite of houseid2 and PARTICID

# status_outcome_mortality_cohort:
# need to create houseid2 by combining centreid and houseid (need to add leading 0s up to 4 digits first)
# centreid
# - 10 Cuba
# - 20 Dominican Republic
# - 30 Peru (urban)
# - 40 Peru (rural)
# - 50 Venezuela
# - 60 Mexico (urban)
# - 70 Mexico (rural)
# - 100 China (urban)
# - 110 China (rural)
# - 200 Puerto Rico

# Create houseid2
mortality_outcome = mortality_outcome %>% 
  mutate(centreid_num = case_when(centreid == "Cuba" ~ 10,
                                  centreid == "DR" ~ 20,
                                  centreid == "Peru (urban)" ~ 30,
                                  centreid == "Peru (rural)" ~ 40,
                                  centreid == "Venezuela" ~ 50,
                                  centreid == "Mexico (urban)" ~ 60,
                                  centreid == "Mexico (rural)" ~ 70,
                                  centreid == "China (urban)" ~ 100,
                                  centreid == "China (rural)" ~ 110,
                                  centreid == "Puerto Rico" ~ 200)) %>% 
  mutate(HOUSEID = stringr::str_pad(HOUSEID, 4, pad="0")) %>% 
  mutate(houseid2 = as.numeric(paste0(centreid_num, HOUSEID)))

# Merge vital status data with baseline data
data = data %>% 
  left_join(select(mortality_outcome, houseid2, PARTICID, dead2, censor_days, censor_yr, vital_ascertained), by = c("houseid2", "PARTICID"))
```

Recode `parkinsonism` variable

```{r}
data = data %>% 
  mutate(parkinsonism = if_else(parkinsonism == "Parkinsonian", 1, 0, NA_real_))

summary(as.factor(data$parkinsonism))
```

Create a PD variable that combines the algorithm-based dx (`JorgePD`) and self-reported dx (`PARK`)

```{r}
# Create a PD variable that combines the algorithm-based dx (`JorgePD`) and self-reported dx (`PARK`)
data = data %>% 
  mutate(JorgePD_or_selfPD = case_when(JorgePD==1 | PARK=="probable" | PARK=="certain" ~ 1, 
                                       JorgePD==0 | PARK=="no" ~ 0, 
                                       TRUE ~ NA_real_))

summary(as.factor(data$JorgePD_or_selfPD))
```

Create dummy mortality variable

```{r}
summary(data$vital_ascertained)
summary(data$dead2)
```

Characteristics of participants with and without vital status ascertained

```{r}
temp = data %>% 
  mutate(vital_yesno = if_else(vital_ascertained == "no" | is.na(vital_ascertained), 0, 1))
  
vars = c("age", "gender", "PMARRY", "PEDUC", "Nassets",  "illnocat", "pnism", "JorgePD_or_selfPD", "medserv", "PHOSAD", "CARENEED")
factorVars = c("gender", "PMARRY", "PEDUC", "Nassets",  "illnocat", "pnism", "JorgePD_or_selfPD", "medserv", "PHOSAD", "CARENEED")

tab1 = tableone::CreateTableOne(data = temp,
                                vars = vars,
                                factorVars = factorVars,
                                strata = c("vital_yesno"),
                                addOverall = TRUE)

table1 = print(tab1)
```

Save tables

```{r}
path = here::here("Output", "PD outcomes paper", "Table1-vitalstatus.csv")
write.csv(table1, path)
```

1049 participants included in the `baseline_survey_for_mortality_1_0.sav` dataset 10315 had vital status acertained; had missing follow-up status; 1501 did not - exclude these last two group of people from the subsequent analysis.

```{r}
data = data %>% 
  filter(vital_ascertained == "yes") %>% 
  mutate(died = case_when(dead2 == "dead" ~ 1,
                          TRUE ~ 0))

summary(as.factor(data$died))
```

10315 participants included in the following analysis.

# Analysis

## Cross-tabulation and chi-square test

### Parkinsonism and mortality

```{r}
descr::crosstab(data$died, data$pnism, prop.c=TRUE, chisq=TRUE)
```

### PD and mortality

```{r}
descr::crosstab(data$died, data$JorgePD, prop.c=TRUE,  chisq=TRUE)
```

### JorgePD_or_selfPD and mortality

```{r}
descr::crosstab(data$died, data$JorgePD_or_selfPD, prop.c=TRUE,  chisq=TRUE)
```

## Check PH assumption

```{r}
res.cox = survival::coxph(Surv(censor_days, died) ~ pnism, data = data)
test.ph = survival::cox.zph(res.cox)
test.ph

res.cox = survival::coxph(Surv(censor_days, died) ~ pnism + age + gender + illnocat + PEDUC, data = data)
test.ph = survival::cox.zph(res.cox)
test.ph

res.cox = survival::coxph(Surv(censor_days, died) ~ JorgePD, data = data)
test.ph = survival::cox.zph(res.cox)
test.ph

res.cox = survival::coxph(Surv(censor_days, died) ~ JorgePD + age + gender + illnocat + PEDUC, data = data)
test.ph = survival::cox.zph(res.cox)
test.ph

res.cox = survival::coxph(Surv(censor_days, died) ~ parkinsonism, data = data)
test.ph = survival::cox.zph(res.cox)
test.ph

res.cox = survival::coxph(Surv(censor_days, died) ~ parkinsonism + age + gender + illnocat + PEDUC, data = data)
test.ph = survival::cox.zph(res.cox)
test.ph

res.cox = survival::coxph(Surv(censor_days, died) ~ JorgePD_or_selfPD, data = data)
test.ph = survival::cox.zph(res.cox)
test.ph

res.cox = survival::coxph(Surv(censor_days, died) ~ JorgePD_or_selfPD + age + gender + illnocat + PEDUC, data = data)
test.ph = survival::cox.zph(res.cox)
test.ph
```

From the output above, the test is statistically significant for the `illnocat` variable, and the global test is also statistically significant. Therefore, we can assume the proportional hazards is violated. One solution would be to conduct a stratified Cox PH - the covariate with nonproportional effects is included in the Cox model as stratification variable rather than a predictor.

Check if stratification fixes this

```{r}
res.cox = survival::coxph(Surv(censor_days, died) ~ JorgePD + age + gender + strata(illnocat) + PEDUC, data = data)
test.ph = survival::cox.zph(res.cox)
test.ph

res.cox = survival::coxph(Surv(censor_days, died) ~ JorgePD_or_selfPD + age + gender + strata(illnocat) + PEDUC, data = data)
test.ph = survival::cox.zph(res.cox)
test.ph
```

## Cox PH regression: country-specific estimates

Create function to run CoxPH regression models

```{r}
func_coxph = function(data, exposure, adj, country){
  
  # Create an empty output df
  output = data.frame(
    exposure = NA,
    study.site = NA,
    hrs = NA,
    estimate = NA,
    std.error = NA
  )
  
  # List countries to iterate Cox PH regression through
  #countries = c("Cuba", "DR", "Peru (urban)", "Peru (rural)", "Venezuela", "Mexico (urban)", "Mexico (rural)", "Puerto Rico") 
  countries = c("Cuba", "DR", "Peru", "Venezuela", "Mexico", "Puerto Rico") # using study sites results in small numbers, use country-level variable
  
  # Formula for the Cox PH regression
  outcome = "Surv(censor_days, died)"
  formula = as.formula(paste0(outcome, " ~ ", exposure, adj))
  
  for (i in countries){
    
    model = coxph(formula, data=data, subset=countries==i) # cox regression
  
    temp = tidy(model, conf.int = TRUE, conf.level = 0.95, exponentiate = TRUE) %>% # process regression output
      mutate(hrs = paste0(format.pval(round(estimate,2),nsmall=2), " (", format.pval(round(conf.low,2),nsmall=2),"-", format.pval(round(conf.high,2),nsmall=2),")")) %>% 
      mutate(estimate = log(estimate)) %>% 
      select(exposure=term, hrs, estimate, std.error)
    
    temp$study.site = i #label study site
    
    temp = temp[temp$exposure==exposure, ] # select ORs for exposure of interest
    
    output = bind_rows(output, temp)
  
  }
  
  return(output)
  
}
```

Run models

```{r, message=FALSE, warning=FALSE}
hrs_pnism_died_crude = func_coxph(data=data, exposure="pnism", adj="")
hrs_pnism_died_adj = func_coxph(data=data, exposure="pnism", adj=" + age + gender + PEDUC + strata(illnocat)")
hrs_pd_died_crude = func_coxph(data=data, exposure="JorgePD", adj="")
hrs_pd_died_adj = func_coxph(data=data, exposure="JorgePD", adj=" + age + gender + PEDUC + strata(illnocat)")
hrs_pd2_died_crude = func_coxph(data=data, exposure="JorgePD_or_selfPD", adj="")
hrs_pd2_died_adj = func_coxph(data=data, exposure="JorgePD_or_selfPD", adj=" + age + gender + PEDUC + strata(illnocat)")
```

### Parkinsonism and all-cause mortality (Adjusted for age, sex, education, and no. illnesses)

```{r}
kable(hrs_pnism_died_adj[-1, 1:4])
```

### PD and all-cause mortality (Adjusted for age, sex, education, and no. illnesses)

```{r}
kable(hrs_pd_died_adj[-1, 1:4])
```

### JorgePD_or_selfPD and mortality (Adjusted for age, sex, education, and no. illnesses)

```{r}
kable(hrs_pd2_died_adj[-1, 1:4])
```

## Cox PH regression: meta-analysis

Run random-effects model, assumes there are 2 sources of error: 1) sampling error and 2) variance from the fact that included study sites are not from a single, homogeneous population, thus there is distribution of true effect sizes. Thus, the random-effects model aims to model the mean of the distribution of true effects.

### Parkinsonism and all-cause mortality

#### Crude

```{r, fig.width = 10, fig.height = 6}
mgen = meta::metagen(TE = estimate,                           # make sure log(OR) than OR only
                     seTE = std.error,
                     studlab = study.site,
                     sm = "HR",
                     fixed = TRUE,
                     random = FALSE,
                     method.tau = "DL",                       # DerSimonian-Laird estimator
                     hakn = TRUE,                             # Hartung-Knapp adjustment of SEs
                     prediction = FALSE,                       # the above line and this line allow more uncertainty in the estimation of between-study heterogeneity and appropriate for use in random-effects meta-analysis
                     data = hrs_pnism_died_crude[-1, ],
                     title = "Association between Parkinsonism and all-cause mortality")

meta::forest(mgen, 
             rightlabs = c("HR", "95% CI", "Weight"),
             print.tau2 = FALSE,
             leftcols = c("studlab")
             )

plot_pnism_died_crude = grid.grab() 
```

#### Adjusted for age, sex, education, and no. illnessess

```{r, fig.width = 10, fig.height = 6}
mgen = meta::metagen(TE = estimate,
                     seTE = std.error,
                     studlab = study.site,
                     sm = "HR",
                     fixed = TRUE,
                     random = FALSE,
                     method.tau = "DL",                       # DerSimonian-Laird estimator
                     hakn = TRUE,                             # Hartung-Knapp adjustment of SEs
                     prediction = FALSE,                       # the above line and this line allow more uncertainty in the estimation of between-study heterogeneity and appropriate for use in random-effects meta-analysis
                     data = hrs_pnism_died_adj[-1, ],
                     title = "Association between Parkinsonism and all-cause mortality")

meta::forest(mgen, 
             rightlabs = c("HR", "95% CI", "Weight"),
             print.tau2 = FALSE,
             leftcols = c("studlab"))

plot_pnism_died_adj = grid.grab()
```

### PD and all-cause mortality

#### Crude

```{r, fig.width = 10, fig.height = 6}
mgen = meta::metagen(TE = estimate,
                     seTE = std.error,
                     studlab = study.site,
                     sm = "HR",
                     fixed = TRUE,
                     random = FALSE,
                     method.tau = "DL",                       # DerSimonian-Laird estimator
                     hakn = TRUE,                             # Hartung-Knapp adjustment of SEs
                     prediction = FALSE,                       # the above line and this line allow more uncertainty in the estimation of between-study heterogeneity and appropriate for use in random-effects meta-analysis
                     data = hrs_pd_died_crude[-1, ],
                     title = "Association between PD and all-cause mortality")

meta::forest(mgen,
             rightlabs = c("HR", "95% CI", "Weight"),
             print.tau2 = FALSE,
             leftcols = c("studlab"))

plot_pd_died_crude = grid.grab()
```

#### Adjusted for age, sex, education, and no. illnesses

```{r, fig.width = 10, fig.height = 6}
mgen = meta::metagen(TE = estimate,
                     seTE = std.error,
                     studlab = study.site,
                     sm = "HR",
                     fixed = TRUE,
                     random = FALSE,
                     method.tau = "DL",                       # DerSimonian-Laird estimator
                     hakn = TRUE,                             # Hartung-Knapp adjustment of SEs
                     prediction = FALSE,                       # the above line and this line allow more uncertainty in the estimation of between-study heterogeneity and appropriate for use in random-effects meta-analysis
                     data = hrs_pd_died_adj[-1, ],
                     title = "Association between PD and all-cause mortality")

meta::forest(mgen, 
             rightlabs = c("HR", "95% CI", "Weight"),
             print.tau2 = FALSE,
             leftcols = c("studlab"))
plot_pd_died_adj = grid.grab()
```

### JorgePD_or_selfPD and all-cause mortality

#### Crude

```{r, fig.width = 10, fig.height = 6}
mgen = meta::metagen(TE = estimate,
                     seTE = std.error,
                     studlab = study.site,
                     sm = "HR",
                     fixed = TRUE,
                     random = FALSE,
                     method.tau = "DL",                       # DerSimonian-Laird estimator
                     hakn = TRUE,                             # Hartung-Knapp adjustment of SEs
                     prediction = FALSE,                       # the above line and this line allow more uncertainty in the estimation of between-study heterogeneity and appropriate for use in random-effects meta-analysis
                     data = hrs_pd2_died_crude[-1, ],
                     title = "Association between PD and all-cause mortality")

meta::forest(mgen, 
             rightlabs = c("HR", "95% CI", "Weight"),
             print.tau2 = FALSE,
             leftcols = c("studlab"))
plot_pd2_died_crude = grid.grab()
```

#### Adjusted for age, sex, education and no. illnesses

```{r, fig.width = 10, fig.height = 6}
mgen = meta::metagen(TE = estimate,
                     seTE = std.error,
                     studlab = study.site,
                     sm = "HR",
                     fixed = TRUE,
                     random = FALSE,
                     method.tau = "DL",                       # DerSimonian-Laird estimator
                     hakn = TRUE,                             # Hartung-Knapp adjustment of SEs
                     prediction = FALSE,                       # the above line and this line allow more uncertainty in the estimation of between-study heterogeneity and appropriate for use in random-effects meta-analysis
                     data = hrs_pd2_died_adj[-1, ],
                     title = "Association between PD and all-cause mortality")

meta::forest(mgen, 
             rightlabs = c("HR", "95% CI", "Weight"),
             print.tau2 = FALSE,
             leftcols = c("studlab"))
plot_pd2_died_adj = grid.grab()
```

## Combine and save outputs

### Main results

```{r}
plot_combined_crude = cowplot::plot_grid(plot_pnism_died_crude, plot_pd2_died_crude,
                                         align = "v",
                                         labels = "AUTO", 
                                         scale = 0.5,
                                         ncol = 1)

plot_combined_crude

ggsave(plot = plot_combined_crude, filename = here::here("Output", "PD outcomes paper", "plots", "hrs_mortality_crude.png"), width = 18, height = 15, units = "cm") # height = 20 for 3 rows; height = 15 for 2 rows

plot_combined_adj = cowplot::plot_grid(plot_pnism_died_adj, plot_pd2_died_adj,
                                         align = "v",
                                         labels = "AUTO", 
                                         scale = 0.5,
                                         ncol = 1)

plot_combined_adj

ggsave(plot = plot_combined_adj, filename = here::here("Output", "PD outcomes paper", "plots", "hrs_mortality_adj.png"), width = 18, height = 15, units = "cm")
```

### Sensitivity analysis: Association between JorgePD and mortality

Save plot as rds

```{r}
saveRDS(plot_pd_died_adj, file = here::here("Output", "PD outcomes paper", "plots", "temp_plot_JorgePD_died.rds"))
```