---
title: "Check frailty variables"
output: html_document
date: "2023-08-14"
---

Open libraries

```{r}
library(broom)      # for tidy()
library(corrplot)
library(data.table)
library(here)       # for easy file referencing by using the top-level directory of a file project
library(kableExtra)
library(knitr)
library(survival)
library(tableone)
library(tidyverse)
```

## Open dataset

Source codes

```{r}
source(here::here("Script", "Functions", "Data process", "func_open_and_process_data.R"))
```

Open Baseline phase data

```{r, message=FALSE}
# Set path
path = here::here("Data", "raw data", "baseline survey", "prevalence_survey_data_1_3.dta")

# Open data
data = open_and_process_data(path, "dta") # this function opens a Stata dataset (dta) and converts Stata's labelled variables into factors

# Subset participants living in Latin America
#data = data %>% filter(centreid %in% c("Cuba", "DR", "Peru (urban)", "Peru (rural)", "Venezuela", "Mexico (urban)", "Mexico (rural)", "Puerto Rico"))

# Drop unused factor levels
#data$centreid = droplevels(data$centreid)

# Select and process relevant variables
data_base = data %>% 
  select(houseid2, PARTICID, countryid, centreid, FR_weight_loss, FR_exhaust, FR_walkslow, FR_underactive, cogscore, peyeint, pearint, FR_armdic, contains("frail"), NEO12B, PDAS7, PACTIVE, Q531, Q481, ARMCIRC)

# Summary statistics
temp = data %>% 
  select(FR_weight_loss, FR_exhaust, FR_walkslow, FR_underactive, cogscore, peyeint, pearint, FR_armdic, contains("frail"), NEO12B, PDAS7, PACTIVE, Q531, Q481, ARMCIRC, -FRAILTY_D) %>% 
  mutate(across(c(FR_weight_loss, FR_exhaust, FR_walkslow, FR_underactive, pearint, peyeint, PDAS7, PACTIVE, Q531, Q481, contains("frail")), ~as.factor(.x)))
summary(temp)
```


## #1 Compute frailty scores using existing frailty variables

 - Including missing data as '0'

```{r}
frailty_base_original = data_base %>% 
  # compute frailty phenotype score
  mutate(fp_count = rowSums(.[c("FR_weight_loss", "FR_exhaust", "FR_walkslow", "FR_underactive")], na.rm=TRUE),
         fp_frail = as.factor(if_else(fp_count>=2, 1, 0))) %>% 
  # Compute multidimensional frailty score
  mutate(cognition = if_else(cogscore<29.5, 1, 0),
         sensory = case_when(peyeint=="yes" | pearint=="yes" ~ 1,
                             is.na(peyeint) & is.na(pearint) ~ NA_real_,
                             TRUE ~ 0),
         nutrition = FR_armdic,
         physical = FR_walkslow) %>% 
  mutate(mf_count = rowSums(.[c("cognition", "sensory", "nutrition", "physical")], na.rm=TRUE),
         mf_frail = as.factor(if_else(mf_count>=2, 1, 0)))
```

**Check that these agree with the existing frailty scores**

Frailty phenotype
```{r}
summary(as.factor(data_base$frail2))    # FP score in original data
summary(frailty_base_original$fp_frail) # FP score calculated from original frailty variables
```

Multidimensional frailty
```{r}
summary(as.factor(data_base$multifrail)) # MF score in original data
summary(frailty_base_original$mf_frail)  # MF score calculated from original frailty variables
```

Perfect match!

## #2 Compute frailty scores from scratch

```{r}
frailty_base_scratch = data_base %>% 
  # compute individual frailty phenotype variables
  mutate(weight_loss_dani = if_else(Q531==1, 1, 0),
         exhaust_dani = if_else(Q481==1, 1, 0),
         walkslow_dani = if_else(NEO12B>16, 1, 0),
         walkslow2_dani = if_else(NEO12B>16 | PDAS7=="severe difficulty" | PDAS7=="extreme difficulty/ cannot do", 1, 0),
         underactive_dani = if_else(PACTIVE=="not at all", 1, 0)) %>% 
  # compute FP score
  mutate(fp_count = rowSums(.[c("weight_loss_dani", "exhaust_dani", "walkslow_dani", "underactive_dani")], na.rm=TRUE),
         fp_frail = as.factor(if_else(fp_count>=2, 1, 0))) %>% 
  # compute individual multidimensional frailty variables
  mutate(cognition = if_else(cogscore<29.5, 1, 0, missing=0),
         sensory = case_when(peyeint=="yes" | pearint=="yes" ~ 1,
                             is.na(peyeint) & is.na(pearint) ~ NA_real_,
                             TRUE ~ 0),
         nutrition = if_else(ARMCIRC<22, 1, 0),
         physical = walkslow_dani) %>% 
  # compute MF score
  mutate(mf_count = rowSums(.[c("cognition", "sensory", "nutrition", "physical")], na.rm=TRUE),
         mf_frail = as.factor(if_else(mf_count>=2, 1, 0)))
```

## Compare frailty scores - original (#1) versus computed from scratch (#2)

### Individual frailty phenotype variables

**Weight loss**

```{r}
summary(as.factor(data_base$FR_weight_loss))
summary(as.factor(frailty_base_scratch$weight_loss_dani))
```

**Exhaustion**

```{r}
summary(as.factor(data_base$FR_exhaust))
summary(as.factor(frailty_base_scratch$exhaust_dani))
```

**Slow walking speed**

```{r}
summary(as.factor(data_base$FR_walkslow))
summary(as.factor(frailty_base_scratch$walkslow_dani))
```

**Low physical activity**

```{r}
summary(as.factor(data_base$FR_underactive))
summary(as.factor(frailty_base_scratch$underactive_dani))
```

**Cognition**
```{r}
summary(as.factor(frailty_base_original$cognition))
summary(as.factor(frailty_base_scratch$cognition))
```

**Sensory**
```{r}
summary(as.factor(frailty_base_original$sensory))
summary(as.factor(frailty_base_scratch$sensory))
```

**Nutrition**
```{r}
summary(as.factor(frailty_base_original$nutrition))
summary(as.factor(frailty_base_scratch$nutrition))
```

### Overall score

**Frailty phenotype**

```{r}
summary(as.factor(data_base$frail2))
summary(frailty_base_scratch$fp_frail)
```

My calculation results in 298 fewer frail.

**Multidimensional frailty**

```{r}
summary(as.factor(data_base$multifrail))
summary(frailty_base_scratch$mf_frail)
```

My calculation results in 75 fewer frail.

## Check potential frailty index deficits

```{r}
# Select and process relevant variables
data_fi= data %>% 
  select(houseid2, PARTICID, countryid, centreid, gender, age, agegrp, agegrp2, PMARRY, PEDUC, Nassets, illnocat, CARENEED, medserv, PPC, PHOSAD,
         cogscore, peyeint, pearint, NEO12B, PDAS7, PACTIVE, Q531, Q481, ARMCIRC, Q1705, q17912,
         cvadiag, cdem1066, PARTH, PCOUGH, PRESP, hyperten, PGUT, PSKIN, PFAINT, PTOLDDM, COAD, heartisc,
         PEYE, PEAR, WSTCIRC, HIPCIRC, euro5, euro6, PDAS6, imprec, eurocase, Q871, wenger,
         walkdiff, SRQ18, SRQ20, adlsevere, adl3plus, dsmdisab, muchcare, IMPAIRMENT_D, CHOREDIS, FEEDDIS, DRESSDIS, TOILDIS, Q451, PADMIT, FALLSNO, comorbid, illno) %>% 
  mutate(whr = WSTCIRC/HIPCIRC)

temp = data_fi %>% 
  mutate(across(c(everything(), -houseid2, -PARTICID, -cogscore, -ARMCIRC, -WSTCIRC, -HIPCIRC, -whr, -age), ~as.factor(.x)))
summary(temp)
```

### Code frailty deficits

```{r}
data_fi = data_fi %>% 
  mutate(fi_active = case_when(PACTIVE=="very physically active" ~ 0,
                               PACTIVE=="fairly" ~ 0.3,
                               PACTIVE=="not very" ~ 0.6,
                               PACTIVE=="not at all" ~ 1,
                               TRUE ~ NA_real_),
         fi_weight_loss = case_when(Q531==0 ~ 0,
                                    Q531==1 ~ 1,
                                    TRUE ~ NA_real_),
         fi_exhaust = case_when(Q481==0 ~ 0,
                                Q481==1 ~ 0.5,
                                Q481==2 ~ 1,
                                TRUE ~ NA_real_),
         fi_stroke = case_when(cvadiag=="no" ~ 0,
                               cvadiag=="yes" ~ 1,
                               TRUE ~ NA_real_),
         fi_dementia = case_when(cdem1066=="non-case" ~ 0,
                                 cdem1066=="case" ~ 1,
                                 TRUE ~ NA_real_),
         fi_arth = case_when(PARTH=="no problem" ~ 0,
                             PARTH=="has problem, interferes not at all" ~ 0,
                             PARTH=="has problem, interferes a little" ~ 0.5,
                             PARTH=="has problem, interferes a lot" ~ 1,
                             TRUE ~ NA_real_),
         fi_cough = case_when(PCOUGH=="no problem" ~ 0,
                             PCOUGH=="has problem, interferes not at all" ~ 0,
                             PCOUGH=="has problem, interferes a little" ~ 0.5,
                             PCOUGH=="has problem, interferes a lot" ~ 1,
                             TRUE ~ NA_real_),
         fi_resp = case_when(PRESP=="no problem" ~ 0,
                             PRESP=="has problem, interferes not at all" ~ 0,
                             PRESP=="has problem, interferes a little" ~ 0.5,
                             PRESP=="has problem, interferes a lot" ~ 1,
                             TRUE ~ NA_real_),
         fi_hyperten = case_when(hyperten=="no" ~ 0,
                                 hyperten=="yes" ~ 1,
                                 TRUE ~ NA_real_),
         fi_heartisc = case_when(heartisc=="no" ~ 0,
                                 heartisc=="yes" ~ 1,
                                 TRUE ~ NA_real_),
         fi_gut = case_when(PGUT=="no problem" ~ 0,
                            PGUT=="has problem, interferes not at all" ~ 0,
                            PGUT=="has problem, interferes a little" ~ 0.5,
                            PGUT=="has problem, interferes a lot" ~ 1,
                            TRUE ~ NA_real_),
         fi_skin = case_when(PSKIN=="no problem" ~ 0,
                            PSKIN=="has problem, interferes not at all" ~ 0,
                            PSKIN=="has problem, interferes a little" ~ 0.5,
                            PSKIN=="has problem, interferes a lot" ~ 1,
                            TRUE ~ NA_real_),
         fi_faint = case_when(PFAINT=="no problem" ~ 0,
                            PFAINT=="has problem, interferes not at all" ~ 0,
                            PFAINT=="has problem, interferes a little" ~ 0.5,
                            PFAINT=="has problem, interferes a lot" ~ 1,
                            TRUE ~ NA_real_),
         fi_diabetes = case_when(PTOLDDM=="no" ~ 0,
                                 PTOLDDM=="yes" ~ 1,
                                 TRUE ~ NA_real_),
         fi_copd = case_when(COAD=="does not met criteria for COPD" ~ 0,
                             COAD=="meets criteria for COPD" ~ 1,
                             TRUE ~ NA_real_),
         fi_eye = case_when(PEYE=="no problem" ~ 0,
                            PEYE=="has problem, interferes not at all" ~ 0,
                            PEYE=="has problem, interferes a little" ~ 0.5,
                            PEYE=="has problem, interferes a lot" ~ 1,
                            TRUE ~ NA_real_),
         fi_ear = case_when(PEAR=="no problem" ~ 0,
                            PEAR=="has problem, interferes not at all" ~ 0,
                            PEAR=="has problem, interferes a little" ~ 0.5,
                            PEAR=="has problem, interferes a lot" ~ 1,
                            TRUE ~ NA_real_),
         fi_paralysis = case_when(Q1705==1 | Q1705==2 | q17912==1 ~ 1,
                                  Q1705==0 | q17912==0 ~ 0,
                                  TRUE ~ NA_real_),
         fi_sleep = case_when(euro5=="symptom absent" ~ 0,
                              euro5=="symptom present" ~ 1,
                              TRUE ~ NA_real_),
         fi_cognition = if_else(cogscore<29.5, 1, 0),
         fi_concentrate = case_when(PDAS6=="none" ~ 0,
                            PDAS6=="mild difficulty" ~ 0.3,
                            PDAS6=="moderate difficulty" ~ 0.6,
                            PDAS6=="seevere difficulty" ~ 1,
                            PDAS6=="extreme difficulty/ cannot do" ~ 1,
                            TRUE ~ NA_real_),
         fi_interest = case_when(euro6=="symptom absent" ~ 0,
                              euro6=="symptom present" ~ 1,
                              TRUE ~ NA_real_),
         fi_recall = case_when(imprec=="not impaired" ~ 0,
                               imprec=="impaired" ~ 1,
                               TRUE ~ NA_real_),
         fi_depressed = case_when(eurocase=="score of 3 or less on EURO-D" ~ 0,
                                  eurocase=="score of 4 or more on EURO-D" ~ 1,
                                  TRUE ~ NA_real_),
         fi_lonely = case_when(Q871==0 ~ 0,
                               Q871==1 ~ 0.5,
                               Q871==2 ~ 1,
                              TRUE ~ NA_real_),
         fi_socialsupp = case_when(wenger=="family dependent" ~ 0,
                            wenger=="locally integrated" ~ 0,
                            wenger=="locally self-contained" ~ 1,
                            wenger=="wider community focussed" ~ 0,
                            wenger=="private" ~ 1,
                            TRUE ~ NA_real_),
         fi_nutrition = if_else(ARMCIRC<22, 1, 0), 
         fi_whr = case_when(whr>2 | is.na(whr) ~ NA_real_,
                            whr>=0.9 & gender=="male" ~ 1,
                            whr>=0.85 & gender=="female" ~ 1,
                            TRUE ~ 0),
         fi_walkdiff = case_when(walkdiff=="no or moderate difficulty in walking 1km" ~ 0, 
                                 walkdiff=="severe difficulty or cannot walk" ~ 1, 
                                 TRUE ~ NA_real_),
         fi_tired = case_when(SRQ18=="yes, symptom present" | SRQ20=="yes, symptom present" ~ 1,
                              SRQ18=="no" | SRQ20=="no" ~ 0,
                              TRUE ~ NA_real_),
         fi_adlsevere = case_when(adlsevere==0 ~ 0,
                                  adlsevere==1 | adlsevere==2 ~ 0.5,
                                  adlsevere>=3 ~ 1,
                                  TRUE ~ NA_real_),
         fi_dsmdisab = case_when(dsmdisab==0 ~ 0,
                                 dsmdisab==1 | dsmdisab==2 ~ 0.3,
                                 dsmdisab==3 | dsmdisab==4 ~ 0.6,
                                 dsmdisab>=5 ~ 1,
                                 TRUE ~ NA_real_),
         fi_careneed = case_when(CARENEED=="does not need care; they are able to do everything for thems" ~ 0,
                                 CARENEED=="needs care some of the time" ~ 0.5,
                                 CARENEED=="needs care much of the time" ~ 1,
                                 TRUE ~ NA_real_),
         fi_looksfrail = case_when(Q451==0 ~ 0,
                                Q451==1 ~ 0.5,
                                Q451==2 ~ 1,
                                TRUE ~ NA_real_))

temp = data_fi %>% 
  select(starts_with("fi_")) %>% 
  mutate(across(everything(), ~as.factor(.x)))
summary(temp)
```

### Description of FI

Prevalence of individual frailty deficit (=1)
```{r}
temp = data_fi %>% 
  select(starts_with("fi_")) %>% 
  mutate(across(everything(), ~factor(case_when(.x==1 ~ "Full deficit",
                                                .x<1 & .x>0 ~ "Partial deficit",
                                                .x==0 ~ "No deficit",
                                                TRUE ~ "Missing"), levels = c("Full deficit", 
                                                                           "Partial deficit", 
                                                                           "No deficit", 
                                                                           "Missing"))
                )
         )

pct_plot = temp %>% 
  pivot_longer(everything(), names_to = "deficit") %>% 
  group_by(deficit, value) %>% 
  tally() %>% 
  mutate(pct = n/nrow(temp)*100)

table_save = pct_plot %>% 
  select(-n) %>% 
  mutate(pct = round(pct, 1)) %>% 
  pivot_wider(names_from = value, values_from=pct) %>% 
  arrange(-`Full deficit`)

path = here::here("Output", "PD and frailty paper", "Table_deficit_prev.csv")
write.csv(table_save, path)
```

Prevalence of individual frailty deficit by age group
```{r}
temp = data_fi %>% 
  filter(!is.na(agegrp2)) %>% # exclude 17 participants missing agegrp
  select(agegrp2, starts_with("fi_")) %>% 
  mutate(across(starts_with("fi_"), ~case_when(.x==1 ~ "Full deficit",
                                         .x<1 & .x>0 ~ "Partial deficit",
                                         .x==0 ~ "No deficit",
                                         TRUE ~ "Missing")))

pct_plot_age = temp %>% 
  pivot_longer(starts_with("fi_"), names_to = "deficit") %>%
  group_by(agegrp2, deficit, value) %>% 
  tally() %>% 
  ungroup() %>% 
  group_by(agegrp2, deficit) %>% 
  mutate(sum = sum(n)) %>% 
  mutate(pct = n/sum*100) %>% 
  arrange(deficit, agegrp2, value)

pct_plot_age
```

 - Full deficits
```{r}
plot_deficit_age = pct_plot_age %>% 
  filter(value=="Full deficit") %>% 
  ggplot(data=.) +
  geom_bar(aes(x=agegrp2, y=round(pct,1)), width=0.5, stat="identity") +
  #scale_y_continuous(labels = scales::percent) +
  labs(x="Age group", y ="Prevalence (%)") +
  facet_wrap(~deficit, scales = "free", ncol=7) +
  theme_bw()

plot_deficit_age

ggsave(plot = plot_deficit_age, filename = here::here("Output", "PD and frailty paper", "plots", "prev_deficit_full_by_age.png"), width = 45, height = 27, units = "cm")
```

- Partial deficits

```{r}
plot_deficit_age = pct_plot_age %>% 
  filter(value=="Partial deficit") %>% 
  ggplot(data=.) +
  geom_bar(aes(x=agegrp2, y=round(pct,1)), width=0.5, stat="identity") +
  #scale_y_continuous(labels = scales::percent) +
  labs(x="Age group", y ="Prevalence (%)") +
  facet_wrap(~deficit, scales = "free", ncol=4) +
  theme_bw()

plot_deficit_age

ggsave(plot = plot_deficit_age, filename = here::here("Output", "PD and frailty paper", "plots", "prev_deficit_partial_by_age.png"), width = 30, height = 20, units = "cm")
```

Correlation between full deficits
```{r}
temp = data_fi %>% 
  select(starts_with("fi_")) %>% 
  mutate(across(everything(), ~case_when(.x==1 ~ 1,
                                         .x<1 & .x>0 ~ NA_real_,
                                         .x==0 ~ 0,
                                         TRUE ~ NA_real_)))

#cor(temp, use = "pairwise.complete.obs", method="kendall)
p1 <- {
  corrplot::corrplot(cor(temp, use="pairwise.complete.obs"));
  # Call the recordPlot() function to record the plot
  recordPlot()
       }

# In case if you want to save the image using ggsave
# replayPlot basically prints the plot.
ggsave(filename = here::here("Output", "PD and frailty paper", "plots", "corrplot_deficits.png"), plot = replayPlot(p1))
```

*Compute FI score*
```{r}
data_fi = data_fi %>% # Compute FI scores and levels
  select(-fi_faint, -fi_depressed, -fi_concentrate, -fi_recall, -fi_active, -fi_dsmdisab, -fi_adlsevere, -fi_careneed, -fi_faint, -fi_sleep) # exclude these deficits from the fi
  
length(data_fi %>% select(starts_with("fi_")) %>% names)

data_fi = data_fi %>% 
  mutate(fi.count = rowSums(across(starts_with("fi_"))),
         fi.score = fi.count/length(data_fi %>% select(starts_with("fi_")) %>% names),
         fi.frail = if_else(fi.score>=0.25, 1, 0),
         fi.cat = factor(case_when(is.na(fi.score) ~ NA_character_,
                                   fi.score>=0.25 ~ "Frail",
                                   fi.score>=0.1 ~ "Pre-frail",
                                   TRUE ~ "Non-frail"), levels = c("Non-frail", "Pre-frail", "Frail")))

data_fi = data_fi %>% 
  mutate(fi.score1 = fi.score/0.1) # to estimate per 0.1 unit effect estimates
```

Distribution of FI score
```{r}
summary(data_fi$fi.score)
summary(as.factor(data_fi$fi.cat))
hist(data_fi$fi.score)
```

```{r}
data_fi %>% 
  ggplot(aes(x=fi.score)) +
  geom_histogram(binwidth=0.05, fill="grey", color="black")+
  scale_x_continuous(breaks=seq(0, 0.7, 0.1))+
  labs(x="FI score", y="Count")+
  theme_classic()
```
```{r}
data_fi %>% 
  filter(!is.na(fi.score)) %>% 
  ggplot(aes(y=fi.score, x=fi.cat)) +
  geom_boxplot(width=0.25) +
  labs(x="Frailty level", y="FI score") +
  theme_classic()
```

Demographic characteristics by FI levels
```{r}
vars = c("age", "gender", "PMARRY", "PEDUC", "Nassets", "illnocat", "CARENEED")
factorVars = c("gender", "PMARRY", "PEDUC", "Nassets", "illnocat", "CARENEED")

tab1 = tableone::CreateTableOne(data = data_fi,
                                vars = vars,
                                factorVars = factorVars,
                                strata = c("fi.cat"),
                                addOverall = TRUE)

table1 = print(tab1)

path = here::here("Output", "PD and frailty paper", "Table1_ficat.csv")
write.csv(table1, path)
```

### Association with outcomes

- Health service use (seen primary care doctor)

```{r}
model = glm(PPC ~ fi.cat + age + gender + PEDUC, family = binomial(link="logit"), data=data_fi)
summary(model)

output = tidy(model, conf.int = TRUE, conf.level = 0.95, exponentiate = TRUE) %>% # process regression output
    mutate(ors = paste0(format.pval(round(estimate,2),nsmall=2), " (", format.pval(round(conf.low,2),nsmall=2),"-", format.pval(round(conf.high,2),nsmall=2),")")) %>% 
    select(exposure=term, ors)
output 

model = glm(PPC ~ fi.score1 + age + gender + PEDUC, family = binomial(link="logit"), data=data_fi)
summary(model)

output = tidy(model, conf.int = TRUE, conf.level = 0.95, exponentiate = TRUE) %>% # process regression output
    mutate(ors = paste0(format.pval(round(estimate,2),nsmall=2), " (", format.pval(round(conf.low,2),nsmall=2),"-", format.pval(round(conf.high,2),nsmall=2),")")) %>% 
    select(exposure=term, ors)
output
```

- Health service use (admitted to hospital)

```{r}
model = glm(PHOSAD ~ fi.cat + age + gender + PEDUC, family = binomial(link="logit"), data=data_fi)
summary(model)

output = tidy(model, conf.int = TRUE, conf.level = 0.95, exponentiate = TRUE) %>% # process regression output
    mutate(ors = paste0(format.pval(round(estimate,2),nsmall=2), " (", format.pval(round(conf.low,2),nsmall=2),"-", format.pval(round(conf.high,2),nsmall=2),")")) %>% 
    select(exposure=term, ors)
output 

model = glm(PHOSAD ~ fi.score1 + age + gender + PEDUC, family = binomial(link="logit"), data=data_fi)
summary(model)

output = tidy(model, conf.int = TRUE, conf.level = 0.95, exponentiate = TRUE) %>% # process regression output
    mutate(ors = paste0(format.pval(round(estimate,2),nsmall=2), " (", format.pval(round(conf.low,2),nsmall=2),"-", format.pval(round(conf.high,2),nsmall=2),")")) %>% 
    select(exposure=term, ors)
output 
```
- Mortality

Open mortality status
```{r}
path = here::here("Data", "raw data", "fu folder from Matthew", "specific outcomes", "mortality", "status_outcome (mortality cohort)_1_0.dta")
status_outcome_mortality_cohort = open_and_process_data(path, "dta")

path = here::here("Data", "raw data", "fu folder from Matthew", "specific outcomes", "mortality", "mortality_outcome1_1.dta")
mortality_outcome = open_and_process_data(path, "dta")
```

Merge vital status
```{r}
# baseline data:
# houseid2 is composite of centreid and houseid (houseid has 4 digits)
# therefore, unique participant-level id = composite of houseid2 and PARTICID

# status_outcome_mortality_cohort:
# need to create houseid2 by combining centreid and houseid (need to add leading 0s up to 4 digits first)
# centreid
# - 10 Cuba
# - 20 Dominican Republic
# - 30 Peru (urban)
# - 40 Peru (rural)
# - 50 Venezuela
# - 60 Mexico (urban)
# - 70 Mexico (rural)
# - 100 China (urban)
# - 110 China (rural)
# - 200 Puerto Rico

# Create houseid2
mortality_outcome = mortality_outcome %>% 
  mutate(centreid_num = case_when(centreid == "Cuba" ~ 10,
                                  centreid == "DR" ~ 20,
                                  centreid == "Peru (urban)" ~ 30,
                                  centreid == "Peru (rural)" ~ 40,
                                  centreid == "Venezuela" ~ 50,
                                  centreid == "Mexico (urban)" ~ 60,
                                  centreid == "Mexico (rural)" ~ 70,
                                  centreid == "China (urban)" ~ 100,
                                  centreid == "China (rural)" ~ 110,
                                  centreid == "Puerto Rico" ~ 200)) %>% 
  mutate(HOUSEID = stringr::str_pad(HOUSEID, 4, pad="0")) %>% 
  mutate(houseid2 = as.numeric(paste0(centreid_num, HOUSEID)))

# Merge vital status data with baseline data
data1 = data_fi %>% 
  left_join(select(mortality_outcome, houseid2, PARTICID, dead2, censor_days, censor_yr, vital_ascertained), by = c("houseid2", "PARTICID"))
```

Select participants whose vital status was ascertained
```{r}
data1 = data1 %>% 
  filter(vital_ascertained == "yes") %>% 
  mutate(died = case_when(dead2 == "dead" ~ 1,
                          TRUE ~ 0))

summary(as.factor(data1$died))
```

Check PH assumption
```{r}
res.cox = survival::coxph(Surv(censor_days, died) ~ fi.cat, data = data1)
test.ph = survival::cox.zph(res.cox)
test.ph

res.cox = survival::coxph(Surv(censor_days, died) ~ fi.cat + age + gender + PEDUC, data = data1)
test.ph = survival::cox.zph(res.cox)
test.ph
```

Check if stratification fixes this

```{r}
res.cox = survival::coxph(Surv(censor_days, died) ~ fi.cat + age + gender + strata(PEDUC), data = data1)
test.ph = survival::cox.zph(res.cox)
test.ph
```

Run CoxPH regression models

```{r}
model = survival::coxph(Surv(censor_days, died) ~ fi.cat + age + gender + strata(PEDUC), data=data1) # cox regression
  
output = tidy(model, conf.int = TRUE, conf.level = 0.95, exponentiate = TRUE) %>% # process regression output
  mutate(hrs = paste0(format.pval(round(estimate,2),nsmall=2), " (", format.pval(round(conf.low,2),nsmall=2),"-", format.pval(round(conf.high,2),nsmall=2),")")) %>% 
  mutate(estimate = log(estimate)) %>% 
  select(exposure=term, hrs, estimate, std.error)
output

model = survival::coxph(Surv(censor_days, died) ~ fi.score1 + age + gender + strata(PEDUC), data=data1) # cox regression
  
output = tidy(model, conf.int = TRUE, conf.level = 0.95, exponentiate = TRUE) %>% # process regression output
  mutate(hrs = paste0(format.pval(round(estimate,2),nsmall=2), " (", format.pval(round(conf.low,2),nsmall=2),"-", format.pval(round(conf.high,2),nsmall=2),")")) %>% 
  mutate(estimate = log(estimate)) %>% 
  select(exposure=term, hrs, estimate, std.error)
output
```
