---
title: "Check frailty variables from Miao"
output: html_document
date: "2023-08-08"
---

## Open dataset

Source codes
```{r}
source(here::here("Script", "Functions", "Data process", "func_open_and_process_data.R"))
```

### Open Miao's data 

Set path for function input 
```{r}
path = "C:/Users/k2258693/OneDrive - King's College London/Desktop/PINNACLE project/6 Paper PD and frailty/Stata files from Miao/Frailty_dataset_Miao_for_Dani.dta"
```

Open dataset
```{r}
data = open_and_process_data(path, "dta") # this function opens a Stata dataset (dta) and converts Stata's labelled variables into factors
```

Drop observations from China or India
```{r}
data = data %>% filter(centreid %in% c("Cuba", "DR", "Peru (urban)", "Peru (rural)", "Venezuela", "Mexico (urban)", "Mexico (rural)", "Puerto Rico"))

# drop unused factor levels
data$centreid = droplevels(data$centreid)
```

Subset relevant data
```{r}
data_miao = data %>% 
  select(HOUSEID, PARTICID, houseid2, countryid, centreid, FR_weight_loss, FR_exhaust, FR_walkslow, FR_underactive, cogscore, peyeint, pearint, FR_armdic, contains("miao"), contains("frail"), NEO12B, PDAS7, PACTIVE, Q531, Q481, ARMCIRC)
```

### Open my data

Baseline phase

```{r}
path = here::here("Data", "raw data", "baseline survey", "prevalence_survey_data_1_3.dta")
data = open_and_process_data(path, "dta") # this function opens a Stata dataset (dta) and converts Stata's labelled variables into factors
data = data %>% filter(centreid %in% c("Cuba", "DR", "Peru (urban)", "Peru (rural)", "Venezuela", "Mexico (urban)", "Mexico (rural)", "Puerto Rico"))
# drop unused factor levels
data$centreid = droplevels(data$centreid)
data_dani = data %>% select(houseid2, PARTICID, countryid, centreid, FR_weight_loss, FR_exhaust, FR_walkslow, FR_underactive, cogscore, peyeint, pearint, FR_armdic, contains("frail"), NEO12B, PDAS7, PACTIVE, Q531, Q481, ARMCIRC)

temp = data_dani %>% 
  mutate(across(c(starts_with("FR"), contains("frail"), pearint, peyeint, NEO12B, PDAS7, PACTIVE, Q531, Q481), ~as.factor(.x)))

summary(temp)
```
Incidence phase

```{r}
# Merge in follow-up status at incidence phase
path = here::here("Data", "raw data", "fu folder from Matthew", "incidence cohort (all survey outcomes)", "other countries", "status_outcome (survey cohort)_1_0.sav")
status_outcome = open_and_process_data(path, "sav")

# Merge in dependency data from incidence phase
path = here::here("Data", "raw data", "fu folder from Matthew", "incidence cohort (all survey outcomes)", "other countries", "full follow up_1_2.dta")
data_full_fu12 = open_and_process_data(path, "dta")

# Select frailty variables from incidence phase
data_full_fu12 = data_full_fu12 %>% 
  select(centreid, HOUSEID, PARTICID, f_cogscore, f_PEYE, f_PEAR, f_NEO12B, f_PDAS7, f_PACTIVE, f_Q531, f_Q481, f_ARMCIRC) %>% 
  mutate(centreid_num = case_when(centreid == "Cuba" ~ 10,
                                  centreid == "DR" ~ 20,
                                  centreid == "Peru (urban)" ~ 30,
                                  centreid == "Peru (rural)" ~ 40,
                                  centreid == "Venezuela" ~ 50,
                                  centreid == "Mexico (urban)" ~ 60,
                                  centreid == "Mexico (rural)" ~ 70,
                                  centreid == "China (urban)" ~ 100,
                                  centreid == "China (rural)" ~ 110,
                                  centreid == "Puerto Rico" ~ 200)) %>% 
  mutate(HOUSEID = stringr::str_pad(HOUSEID, 4, pad="0")) %>% 
  mutate(houseid2 = as.numeric(paste0(centreid_num, HOUSEID))) %>% 
  select(-HOUSEID, -centreid, -centreid_num)

status_outcome = status_outcome %>% 
  mutate(centreid_num = case_when(centreid == "Cuba" ~ 10,
                                  centreid == "DR" ~ 20,
                                  centreid == "Peru (urban)" ~ 30,
                                  centreid == "Peru (rural)" ~ 40,
                                  centreid == "Venezuela" ~ 50,
                                  centreid == "Mexico (urban)" ~ 60,
                                  centreid == "Mexico (rural)" ~ 70,
                                  centreid == "China (urban)" ~ 100,
                                  centreid == "China (rural)" ~ 110,
                                  centreid == "Puerto Rico" ~ 200)) %>% 
  mutate(HOUSEID = stringr::str_pad(HOUSEID, 4, pad="0")) %>% 
  mutate(houseid2 = as.numeric(paste0(centreid_num, HOUSEID))) %>% 
  select(-HOUSEID, -centreid, -centreid_num)

data_full_fu12 = data_full_fu12 %>% 
  left_join(status_outcome, by = c("houseid2", "PARTICID")) 

inc_data = data_full_fu12

temp = data_full_fu12 %>% mutate(across(c(f_PEYE, f_PEAR, f_NEO12B, f_PDAS7, f_PACTIVE, f_Q531, f_Q481), ~as.factor(.x)))
summary(temp)

#### Incidence phase data excludes participants who died, refused, were uncontactable or not recorded

# Merge cohort to baseline data
#data2 = data_full_fu12 %>% left_join(data2, by = c("houseid2", "PARTICID"))
```

## Code up and compare frailty phenotype

### Replicate Miao's data

#### Summary of variables
```{r}
temp = data_miao %>% 
  mutate(across(c(starts_with("FR_"), ends_with("miao"), ends_with("miao2"), starts_with("frail")), ~as.factor(.x)))

summary(temp)
```

#### Replicate FP variables at baseline

```{r}
# Compute baseline frailty variables
data_temp = data_miao %>% 
  mutate(weight_loss_dani = case_when(Q531==1 ~ 1, 
                                      Q531==0 ~ 0, 
                                      TRUE ~ NA_real_),
         exhaust_dani = case_when(Q481==1 | Q481==2 ~ 1, 
                                  Q481==0 ~ 0,
                                  TRUE ~ NA_real_),
         walkdiff = case_when(PDAS7=="none" | PDAS7=="mild difficulty" | PDAS7=="moderate difficulty" ~ 0,
                              PDAS7=="severe difficulty" | PDAS7=="extreme difficulty/ cannot do" ~ 1,
                              TRUE ~ NA_real_),         
         walkslow = case_when(NEO12B>=1 & NEO12B<16 ~ 0,
                              NEO12B>=16 & NEO12B<992 ~ 1, 
                              TRUE ~ NA_real_),
         walkslow_dani = case_when(walkdiff==0 & (is.na(NEO12B) | NEO12B==0) ~ 0,
                                   walkdiff==1 & (is.na(NEO12B) | NEO12B==0) ~ 1,
                                   walkdiff==0 & is.na(NEO12B) ~ 0,
                                   TRUE ~ walkslow),
         underactive_dani = if_else(PACTIVE=="not at all", 1, 0)) %>% 
  mutate(fp_count = rowSums(.[c("weight_loss_dani", "exhaust_dani", "walkslow_dani", "underactive_dani")], na.rm=FALSE),
         fp_frail = as.factor(if_else(fp_count>=2, 1, 0)))
```

```{r}
summary(as.factor(data_temp$weight_loss_dani))
summary(as.factor(data_temp$weight_loss_miao))

summary(as.factor(data_temp$exhaust_dani))
summary(as.factor(data_temp$exhausted_miao))

summary(as.factor(data_temp$walkslow_dani))
summary(as.factor(data_temp$walkslow_miao))

summary(as.factor(data_temp$underactive_dani))
summary(as.factor(data_temp$underactive_miao))

# Overall frail count
summary(data_temp$fp_frail)                       # my replication of miao's code
summary(as.factor(data_temp$frailty_status_miao)) # miao's code
summary(as.factor(data_temp$frail2))              # original FP variable in 10/66
```
#### Replicate FP variables at follow-up

```{r}
# Compute baseline frailty variables
data_temp = inc_data %>% 
  mutate(weight_loss_dani = case_when(f_Q531==1 ~ 1, 
                                      f_Q531==0 ~ 0, 
                                      TRUE ~ NA_real_),
         exhaust_dani = case_when(f_Q481==1 | f_Q481==2 ~ 1, 
                                  f_Q481==0 ~ 0,
                                  TRUE ~ NA_real_),
         walkdiff = case_when(f_PDAS7=="none" | f_PDAS7=="mild difficulty" | f_PDAS7=="moderate difficulty" ~ 0,
                              f_PDAS7=="severe difficulty" | f_PDAS7=="extreme difficulty/ cannot do" ~ 1,
                              TRUE ~ NA_real_),
         walkslow_dani = case_when(f_NEO12B>=1 & f_NEO12B<16 ~ 0,
                                   f_NEO12B>=16 & f_NEO12B<=900 ~ 1, 
                                   walkdiff==1 & (is.na(f_NEO12B) | f_NEO12B==0) ~ 1,
                                   walkdiff==0 & (is.na(f_NEO12B) | f_NEO12B==0) ~ 0,
                                   walkdiff==0 & is.na(f_NEO12B) ~ 0,
                                   TRUE ~ NA_real_),
         underactive_dani = case_when(f_PACTIVE=="not at all" ~ 1, 
                                      is.na(f_PACTIVE) ~ NA_real_,
                                      TRUE ~ 0)) %>% 
  mutate(fp_count = rowSums(.[c("weight_loss_dani", "exhaust_dani", "walkslow_dani", "underactive_dani")], na.rm=FALSE),
         fp_frail = as.factor(if_else(fp_count>=2, 1, 0)))
```

```{r}
# Merge in Miao's follow-up variables
## merge on houseid2 (composite of centreid and houseid) AND PARTICID

data_compare = data_miao %>% 
  select(houseid2, PARTICID, f_weight_loss_miao, f_exhausted_miao, f_walkslow_miao, f_underactive_miao, f_frailty_status_miao) %>% 
  left_join(select(data_temp, houseid2, PARTICID, weight_loss_dani, exhaust_dani, walkslow_dani, underactive_dani, fp_frail), by = c("houseid2", "PARTICID")) %>% 
  filter(complete.cases(.))

# Do mine and Miao's coding match?
all(data_compare$f_weight_loss_miao == data_compare$weight_loss_dani) # all() tests whether all logicals are true
all(data_compare$f_exhausted_miao == data_compare$exhaust_dani) 
all(data_compare$f_walkslow_miao == data_compare$walkslow_dani) 
all(data_compare$f_underactive_miao == data_compare$underactive_dani) 

# All match except walkslow variable
length(which((data_compare$f_walkslow_miao == data_compare$walkslow_dani)==FALSE)) # 390 differences- why??

# Overall frail count
summary(data_compare$fp_frail)                          # my replication of miao's code
summary(as.factor(data_compare$f_frailty_status_miao))  # miao's code
```

#### My data (move to another R markdown)

Calculate frailty scores, including missing data as '0'
```{r}
# FP at baseline - calculate the individual FP variables from scratch
test = data_dani %>% 
  mutate(weight_loss_dani = if_else(Q531==1, 1, 0),
         exhaust_dani = if_else(Q481==1, 1, 0),
         walkslow_dani = if_else(NEO12B>16, 1, 0),
         walkslow2_dani = if_else(NEO12B>16 | PDAS7=="severe difficulty" | PDAS7=="extreme difficulty/ cannot do", 1, 0),
         underactive_dani = if_else(PACTIVE=="not at all", 1, 0)) %>% 
  mutate(fp_count = rowSums(.[c("weight_loss_dani", "exhaust_dani", "walkslow_dani", "underactive_dani")], na.rm=TRUE),
         fp_frail = as.factor(if_else(fp_count>=2, 1, 0))) %>% 
  mutate(cognition = if_else(cogscore<29.5, 1, 0),
         sensory = case_when(peyeint=="yes" | pearint=="yes" ~ 1,
                             is.na(peyeint) & is.na(pearint) ~ NA_real_,
                             TRUE ~ 0),
         nutrition = if_else(ARMCIRC<22, 1, 0),
         physical = walkslow_dani) %>% 
  mutate(mf_count = rowSums(.[c("cognition", "sensory", "nutrition", "physical")], na.rm=TRUE),
         mf_frail = as.factor(if_else(mf_count>=2, 1, 0)))

# FP at baseline - calculate using existing FP variables
data_dani = data_dani %>% 
  mutate(fp_count = rowSums(.[c("FR_weight_loss", "FR_exhaust", "FR_walkslow", "FR_underactive")], na.rm=TRUE),
         fp_frail = as.factor(if_else(fp_count>=2, 1, 0))) %>% 
  mutate(cognition = if_else(cogscore<29.5, 1, 0),
         sensory = case_when(peyeint=="yes" | pearint=="yes" ~ 1,
                             is.na(peyeint) & is.na(pearint) ~ NA_real_,
                             TRUE ~ 0),
         nutrition = FR_armdic,
         physical = FR_walkslow) %>% 
  mutate(mf_count = rowSums(.[c("cognition", "sensory", "nutrition", "physical")], na.rm=TRUE),
         mf_frail = as.factor(if_else(mf_count>=2, 1, 0)))

# FP at follow-up - calculate the individual FP variables from scratch
test2 = inc_data %>% 
  mutate(weight_loss_dani = if_else(f_Q531==1, 1, 0),
         exhaust_dani = if_else(f_Q481==1, 1, 0),
         walkslow_dani = if_else(f_NEO12B>16, 1, 0),
         walkslow2_dani = if_else(f_NEO12B>16 | f_PDAS7=="severe difficulty" | f_PDAS7=="extreme difficulty/ cannot do", 1, 0),
         underactive_dani = if_else(f_PACTIVE=="not at all", 1, 0)) %>% 
  mutate(fp_count = rowSums(.[c("weight_loss_dani", "exhaust_dani", "walkslow_dani", "underactive_dani")], na.rm=TRUE),
         fp_frail = as.factor(if_else(fp_count>=2, 1, 0))) %>% 
  mutate(cognition = if_else(f_cogscore<29.5, 1, 0),
         sensory = case_when(f_PEYE=="yes" | f_PEAR=="yes" ~ 1,
                             is.na(f_PEYE) & is.na(f_PEAR) ~ NA_real_,
                             TRUE ~ 0),
         nutrition = if_else(f_ARMCIRC<22, 1, 0),
         physical = walkslow_dani) %>% 
  mutate(mf_count = rowSums(.[c("cognition", "sensory", "nutrition", "physical")], na.rm=TRUE),
         mf_frail = as.factor(if_else(mf_count>=2, 1, 0)))


summary(test$fp_frail)
summary(data_dani$fp_frail)

summary(test$mf_frail)
summary(data_dani$mf_frail)
```

```{r}
summary(as.factor(test$weight_loss_dani))
summary(as.factor(data_dani$FR_weight_loss))


summary(as.factor(test$exhaust_dani))
summary(as.factor(data_dani$FR_exhaust))


summary(as.factor(test$walkslow_dani))
summary(as.factor(data_dani$FR_walkslow))


summary(as.factor(test$underactive_dani))
summary(as.factor(data_dani$FR_underactive))
```

```{r}
summary(as.factor(data_dani$frail2))
summary(as.factor(data_dani$multifrail))
```

