---
title: "Competing risk survival analysis"
output: html_document
date: "2023-08-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Competing risk survival analysis background

*Jeon Y, Lee WK. Competing Risk Model in Survival Analysis. Cardiovasc Prev Pharmacother. 2020;2(3):77-84.*

  - Competing risk survival analysis is performed instead of Cox proportional hazards regression if the outcome may not occur because of a 'competing' outcome like mortality.
  - There are 3 types of competing risk models:
    1. The cumulative incidence funciton
    2. The cause-specific hazard function (obtain hazard ratio)
    3. Fine and Gray's Subdistribution hazard function (obtain hazard ratio)
  - In competing risk analysis, individuals experiencing competing risk have zero probability of experiencing the event of interest. Conversely, naive Kaplan-Meier approach assumes that these individuals have the same probability of event, so always provides an overestimation of the risk of event (compared to competing risk analysis).
    
**Cause-specific hazard function**

  - CSH model calculates HRs for those who are at risk of event and treats those who experience other outcomes as censored (i.e. non-informative censoring)
  - Interpreted as... the incidence rate of the event of interest in subjects who have not yet experienced any type of events.
  - CSH model commonly used for aetiological research.
  - R's `survival::coxph()` can be used for CSH function.
  
**Subdistribution hazard function (Fine and Gray)**

  - In SDH, subjects who have experienced competing events are not censored but remain in risk sets (i.e. informative censoring). Because individuals are maintained in the risk set, the SDH tends to be lower than CSH.
  - Interpreted as... incidence rate of the event of interest in subjects including those experienced competing risk. (Interpretation is tricky as people only die once)
  - Fine and Gray model appropriate for prognostic study or predicting an individual's risk.
  - R's `cmprsk::crr()` can be used for the SDH regression.
  
Both CSH and SDH methods account for competing risk but use different hazard functions are used.

**Useful references**
https://www.emilyzabor.com/tutorials/survival_analysis_in_r_tutorial.html#Part_3:_Competing_Risks (Example of coding in R)
http://dx.doi.org/10.21037/atm.2016.08.62 (Approaches to check proportionality)

```{r cars}
summary(cars)
```

## Open data

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
