---
title: "What's in the data files from Matthew"
output: html_document
date: "2022-11-16"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE)
```

### Open libraries

```{r}
library(epiR)       # for epi.conf() to calculate CIs for prevalence
library(haven)      # for opening Stata dta files and converting relevant variables into factors as_factor()
library(here)       # for easy file referencing by using the top-level directory of a file project
library(knitr)
library(labelled)   # for var_label() to get variable labels
library(openxlsx)   # for write.xlsx()
library(readxl)     # for read_excel()
library(tableone)
library(tidyverse)
```

What is the top-level of current project?
```{r}
here::here()
```

## Open data

```{r}
# First, open source codes which contain codes to process data:
source(here::here("Script", "Functions", "Data process", "func_open_and_process_data.R"))
```

```{r}
# here::here("Data", "raw data", "baseline survey", "prevalence_survey_data_1_3.dta")
# using here() means that file paths can be created from any physical place as long as fold structure is equivalent

##############################
#### Incidence phase data ####
##############################

path = here::here("Data", "raw data", "fu folder from Matthew", "incidence cohort (all survey outcomes)", "other countries", "full follow up_1_2.dta")
data_full_fu12 = open_and_process_data(path, "dta")

path = here::here("Data", "raw data", "fu folder from Matthew", "incidence cohort (all survey outcomes)", "other countries", "person_years1_1.dta")
data_personyrs11 = open_and_process_data(path, "dta")

path = here::here("Data", "raw data", "fu folder from Matthew", "incidence cohort (all survey outcomes)", "other countries", "baseline data for incidence sites (survey outcomes) 1_0.sav")
baselinedat_inc = open_and_process_data(path, "sav")

path = here::here("Data", "raw data", "fu folder from Matthew", "incidence cohort (all survey outcomes)", "other countries", "status_outcome (survey cohort)_1_0.sav")
status_outcome = open_and_process_data(path, "sav")

##############################
####### Mortality data #######
##############################

path = here::here("Data", "raw data", "fu folder from Matthew", "specific outcomes", "mortality", "mortality_outcome1_1.dta")
mortality_outcome = open_and_process_data(path, "dta")

path = here::here("Data", "raw data", "fu folder from Matthew", "specific outcomes", "mortality", "status_outcome (mortality cohort)_1_0.dta")
status_outcome_mortality_cohort = open_and_process_data(path, "dta")

path = here::here("Data", "raw data", "fu folder from Matthew", "specific outcomes", "mortality", "baseline_survey_for_mortality_1_0.sav")
baselinedat_mor = open_and_process_data(path, "sav")

#####################
####### Other #######
#####################

path = here::here("Data", "raw data", "fu folder from Matthew", "cdem1066_CR_dfdeath_outcome1_1.sav")
cdem1066 = open_and_process_data(path, "sav")
```

## View data for the Incidence cohort

14,896 participants appeared to be included in the incidence cohort. Of these, 10743 were either reinterviewed or refused interview; 2449 died; 1704 were not traced. 

### Data full follow-up

This dataset has the same (or similar) variables as the baseline dataset. The variable names are also the same with a 'f_' prefix.

However, dataset only includes 10,549 observations - why?

```{r}
test = data_full_fu12 %>% 
  select(HOUSEID, PARTICID, centreid) %>% 
  left_join(status_outcome, by = c("HOUSEID", "PARTICID", "centreid"))

summary(as.factor(test$Statusfu))
```
9951 were interviewed; 3 not traced; (i.e. particpants who died, refused to interview, uncontactable or not recorded are excluded from incidence data) Were the 595 remaining new participants added at the incidence phase?

### Person-years

```{r}
kable(head(data_personyrs11))
```

The person-years data appears to contain the following data for 14,896 participants included in the incidence phase dataset:

 - b_DATE: date of interview at baseline
 - fu_DATE: date of interview at follow-up
 - death_date: date of death
 - censor_days: interval in days between baseline interview date and date of death or follow-up (*if missing both what date was used??*)
 - censor_yr: interval in years between baseline itnerview date and date of death or follow-up (*if missing both what date was used??*)
 - dead: dead by follow-up?
    - 0 alive at follow-up - reinterviewed or refused
    - 1 dead
 - dead2: vital status, including 'not known (not traced)'
    - 0 found alive
    - 1 dead
    - 9 vital status not determined (uncontactable/not traced)'
 - vital_ascertainment
    - 0 no
    - 1 yes
    
**Counts**
    
```{r}
summary(as.factor(data_personyrs11$dead))
summary(as.factor(data_personyrs11$dead2))
summary(as.factor(data_personyrs11$vital_ascertained))
```
**Summary**

```{r}
summary(data_personyrs11)
```

### Status outcome

```{r}
kable(head(status_outcome))
```

The `Statusfu` variable shows status at follow-up, coded as:

 - 1 Died
 - 2 Refused
 - 3 Interviewed
 - 4 Uncontactable 
 - 5 Not traced
 - 9 Not recorded
 
Among the 14,896 participants in the incidence phase dataset, the follow-up status at the incidence wave is:

```{r}
table(as.factor(status_outcome$Statusfu))
```
 
 
## View data for the mortality cohort

15,901 participants appeared to be included in the mortality cohort. Of these, 10546 were interviewed; 791 refused interview; 2603 died; 873 were uncontactable; 630 not traced; and 458 not recorded.

### Baseline data for mortality cohort

This is the baseline dataset for the mortality cohort. However, dataset includes 16,032 observations - why? where do the extra 131 participants come from?

```{r}
test = baselinedat_mor %>% 
  select(HOUSEID, PARTICID, centreid) %>% 
  left_join(status_outcome_mortality_cohort, by = c("HOUSEID", "PARTICID", "centreid"))

summary(as.factor(test$Statusfu))
```

### Mortality outcome

```{r}
kable(head(mortality_outcome))
```

The mortality outcome has the same variables included in the person-years data for the incidence phase (see person years dataset above) and contain the follow-up data and vital status for the 15,901 participants included in the mortality cohort:
    
**Counts**
    
```{r}
summary(as.factor(mortality_outcome$dead))
summary(as.factor(mortality_outcome$dead2))
summary(as.factor(mortality_outcome$vital_ascertained))
```

**Summary**

```{r}
summary(mortality_outcome)
```

### Status outcome

```{r}
kable(head(status_outcome_mortality_cohort))
```

The `Statusfu` variable shows status at follow-up, coded as:

 - 1 Died
 - 2 Refused
 - 3 Interviewed
 - 4 Uncontactable 
 - 5 Not traced
 - 9 Not recorded
 
Among the 15,701 participants in the mortality dataset, the follow-up status at the incidence wave is:

```{r}
table(as.factor(status_outcome_mortality_cohort$Statusfu))
```
 