---
title: "PD MCI and dementia - incident MCI/dementia analysis"
output: html_document
date: "2023-05-24"
---

# Data

### Open libraries

```{r}
library(broom)      # for tidy()
library(cowplot)
library(data.table) # for rbindlist()
library(descr)      # for crosstab(), descriptive statistics package
library(epiR)       # for epi.conf() to calculate CIs for prevalence
library(gridGraphics) # for grid.grab()
library(here)       # for easy file referencing by using the top-level directory of a file project
library(knitr)
library(tableone)
library(tidyverse)
```

What is the top-level of current project?

```{r}
here::here()
```

### Open 10/66 baseline dataset

Source codes

```{r}
source(here::here("Script", "Functions", "Data process", "func_open_and_process_data.R"))
source(here::here("Script", "Functions", "Data process", "func_compute_pd_variables.R"))
```

Set path for function input 

```{r}
path = here::here("Data", "raw data", "baseline survey", "prevalence_survey_data_1_3.dta")
```

Open dataset

```{r}
data = open_and_process_data(path, "dta") # this function opens a Stata dataset (dta) and converts Stata's labelled variables into factors
```

### Process dataset

Process Parkinsonism and PD variables

```{r}
data = compute_pd_variables(data)
```

Drop observations from China or India

```{r}
data = data %>% filter(centreid %in% c("Cuba", "DR", "Peru (urban)", "Peru (rural)", "Venezuela", "Mexico (urban)", "Mexico (rural)", "Puerto Rico"))

# drop unused factor levels
data$centreid = droplevels(data$centreid)
```

Subset relevant variables

```{r}
varnames = data %>% 
  select(houseid2, PARTICID, countryid, centreid, age, gender, rural, Nassets, PMARRY, CARENEED, illnocat, cdem1066, PEDUC, PTOLDDM, PSMOKE, PALCNOW, PALCPAST, PACTIVE, PMEATFRQ, PFISHFRQ, PVEGS, NEO14G, NEO6AU, NEO6AL, NEO6BU, NEO6BL, NEO4E, NEO4F, NOE1, NEO14E, PCVA, medserv, PPC, PHOSP, POTH, PPD, PDENT, PTH, PHOSAD, pnism, JorgePD, parkinsonism, PARK, mci, mcinosmi) %>% 
  names()

data = data %>% select_if(names(.) %in% varnames)
```

Recode `parkinsonism` variable

```{r}
data = data %>% 
  mutate(parkinsonism = if_else(parkinsonism == "Parkinsonian", 1, 0, NA_real_))

summary(as.factor(data$parkinsonism))
```

Create a PD variable that combines the algorithm-based dx (`JorgePD`) and self-reported dx (`PARK`)

```{r}
# Create a PD variable that combines the algorithm-based dx (`JorgePD`) and self-reported dx (`PARK`)
data = data %>% 
  mutate(PD = case_when(JorgePD==1 | PARK=="probable" | PARK=="certain" ~ 1, 
                                       JorgePD==0 | PARK=="no" ~ 0, 
                                       TRUE ~ NA_real_))

summary(as.factor(data$PD))
```

Choose which MCI variable to use

  - mci
  - mcinosmi
  
```{r}
#data = data %>%  mutate(mci = factor(mci, levels=c("does not meet MCI criteria", "meets MCI criteria")))

# OR #

data = data %>% mutate(mci = factor(mcinosmi, levels=c("does not meet criteria for MCI", "meets crtieria for MCI"), labels=c("does not meet MCI criteria", "meets MCI criteria")))
```

Create new and dummy variables

```{r}
data = data %>% 
  mutate(agegrp = case_when(is.na(age) ~ NA_character_,
                            age<75 ~ "65-74",
                            age<85 ~ "75-84",
                            TRUE ~ "85+"))
```

### Incident dependency and other follow-up info

Open relevant data

```{r}
# Open follow-up status at incidence phase
path = here::here("Data", "raw data", "fu folder from Matthew", "incidence cohort (all survey outcomes)", "other countries", "status_outcome (survey cohort)_1_0.sav")
status_outcome = open_and_process_data(path, "sav")

# Open follow-up data 
path = here::here("Data", "raw data", "fu folder from Matthew", "incidence cohort (all survey outcomes)", "other countries", "person_years1_1.sav")
fu_data = open_and_process_data(path, "sav")

# Open data from incidence phase
path = here::here("Data", "raw data", "fu folder from Matthew", "incidence cohort (all survey outcomes)", "other countries", "full follow up_1_2.dta")
data_full_fu12 = open_and_process_data(path, "dta")
```

Select relevant variables from other datasets

```{r}
# Select dependecy at follow-up
data_full_fu12 = data_full_fu12 %>% 
  select(centreid, HOUSEID, PARTICID, f_cdem1066, f_mci, f_mcinosmi) %>% 
  mutate(centreid_num = case_when(centreid == "Cuba" ~ 10,
                                  centreid == "DR" ~ 20,
                                  centreid == "Peru (urban)" ~ 30,
                                  centreid == "Peru (rural)" ~ 40,
                                  centreid == "Venezuela" ~ 50,
                                  centreid == "Mexico (urban)" ~ 60,
                                  centreid == "Mexico (rural)" ~ 70,
                                  centreid == "China (urban)" ~ 100,
                                  centreid == "China (rural)" ~ 110,
                                  centreid == "Puerto Rico" ~ 200)) %>% 
  mutate(HOUSEID = stringr::str_pad(HOUSEID, 4, pad="0")) %>% 
  mutate(houseid2 = as.numeric(paste0(centreid_num, HOUSEID))) %>% 
  select(-HOUSEID, -centreid, -centreid_num)

# Select outcome status at follow-up
status_outcome = status_outcome %>% 
  mutate(centreid_num = case_when(centreid == "Cuba" ~ 10,
                                  centreid == "DR" ~ 20,
                                  centreid == "Peru (urban)" ~ 30,
                                  centreid == "Peru (rural)" ~ 40,
                                  centreid == "Venezuela" ~ 50,
                                  centreid == "Mexico (urban)" ~ 60,
                                  centreid == "Mexico (rural)" ~ 70,
                                  centreid == "China (urban)" ~ 100,
                                  centreid == "China (rural)" ~ 110,
                                  centreid == "Puerto Rico" ~ 200)) %>% 
  mutate(HOUSEID = stringr::str_pad(HOUSEID, 4, pad="0")) %>% 
  mutate(houseid2 = as.numeric(paste0(centreid_num, HOUSEID))) %>% 
  select(-HOUSEID, -centreid, -centreid_num)

# Select censor days 
fu_data = fu_data %>% 
  select(centreid, HOUSEID, PARTICID, censor_days, dead2) %>% 
  mutate(centreid_num = case_when(centreid == "Cuba" ~ 10,
                                  centreid == "DR" ~ 20,
                                  centreid == "Peru (urban)" ~ 30,
                                  centreid == "Peru (rural)" ~ 40,
                                  centreid == "Venezuela" ~ 50,
                                  centreid == "Mexico (urban)" ~ 60,
                                  centreid == "Mexico (rural)" ~ 70,
                                  centreid == "China (urban)" ~ 100,
                                  centreid == "China (rural)" ~ 110,
                                  centreid == "Puerto Rico" ~ 200)) %>% 
  mutate(HOUSEID = stringr::str_pad(HOUSEID, 4, pad="0")) %>% 
  mutate(houseid2 = as.numeric(paste0(centreid_num, HOUSEID))) %>% 
  select(-HOUSEID, -centreid, -centreid_num)
```

Merge data into baseline data

```{r}
# Merge data
data_fu = data_full_fu12 %>% 
  full_join(status_outcome, by = c("houseid2", "PARTICID")) %>% 
  full_join(fu_data, by = c("houseid2", "PARTICID"))

#### Incidence phase data excludes participants who died, refused, were uncontactable or not recorded

# Merge new data onto original data
data = data %>% 
  left_join(data_fu, by = c("houseid2", "PARTICID")) %>% 
  filter(Statusfu == "Interviewed") %>% # filter participants who were interviewed at follow-up
  mutate(inc_dem = if_else(f_cdem1066 == "case", 1, 0),
         #inc_mci = if_else(f_mci == 1, 1, 0),
         inc_mci = if_else(f_mcinosmi == 1, 1, 0)
         )
```

Subset participants who do NOT have MCI/dementia at baseline

```{r}
# Subset participants who do NOT have MCI at baseline
data1 = data %>% filter(mci=="does not meet MCI criteria") 

# Subset participants who do NOT have dementia at baseline
data2 = data %>% filter(cdem1066=="non-case") 
```

# Association between Parkinsonism/PD and incident MCI/dementia

## Check PH assumption

```{r}
res.cox = survival::coxph(Surv(censor_days/2, inc_mci) ~ pnism, data = data1)
test.ph = survival::cox.zph(res.cox)
test.ph

res.cox = survival::coxph(Surv(censor_days/2, inc_mci) ~ pnism + age + gender + illnocat + PEDUC, data = data1)
test.ph = survival::cox.zph(res.cox)
test.ph

res.cox = survival::coxph(Surv(censor_days/2, inc_mci) ~ PD, data = data1)
test.ph = survival::cox.zph(res.cox)
test.ph

res.cox = survival::coxph(Surv(censor_days/2, inc_mci) ~ PD + age + gender + illnocat + PEDUC, data = data1)
test.ph = survival::cox.zph(res.cox)
test.ph

res.cox = survival::coxph(Surv(censor_days/2, inc_dem) ~ pnism, data = data2)
test.ph = survival::cox.zph(res.cox)
test.ph

res.cox = survival::coxph(Surv(censor_days/2, inc_dem) ~ pnism + age + gender + illnocat + PEDUC, data = data2)
test.ph = survival::cox.zph(res.cox)
test.ph

res.cox = survival::coxph(Surv(censor_days/2, inc_dem) ~ PD, data = data2)
test.ph = survival::cox.zph(res.cox)
test.ph

res.cox = survival::coxph(Surv(censor_days/2, inc_dem) ~ PD + age + gender + illnocat + PEDUC, data = data2)
test.ph = survival::cox.zph(res.cox)
test.ph
```
From the output above, the test is statistically significant for the `PEDUC` variable in the incident MCI/dementia analysis. Therefore, we can assume the proportional hazards is violated. One solution would be to conduct a stratified Cox PH - the covariate with nonproportional effects is included in the Cox model as stratification variable rather than a predictor.


## Cox Proportional hazards regression: site-specific estimates

Create function to run Cox PH regression models

```{r}
func_coxph = function(data, outcome, exposure, adj, country){
  
  # Create an empty output df
  output = data.frame(
    exposure = NA,
    study.site = NA,
    hrs = NA,
    estimate = NA,
    std.error = NA
  )
  
  # List countries to iterate Cox PH regression through
  #countries = c("Cuba", "DR", "Peru (urban)", "Peru (rural)", "Venezuela", "Mexico (urban)", "Mexico (rural)", "Puerto Rico") 
  countries = c("Cuba", "DR", "Peru", "Venezuela", "Mexico", "Puerto Rico") # using study sites results in small numbers, use country-level variable
  
  # Formula for the Cox PH regression
  outcome = paste0("Surv(censor_days/2, ", outcome, ")")
  formula = as.formula(paste0(outcome, " ~ ", exposure, adj))
  
  for (i in countries){
    
    model = coxph(formula, data=data, subset=countries==i) # cox regression
  
    temp = tidy(model, conf.int = TRUE, conf.level = 0.95, exponentiate = TRUE) %>% # process regression output
      mutate(hrs = paste0(format.pval(round(estimate,2),nsmall=2), " (", format.pval(round(conf.low,2),nsmall=2),"-", format.pval(round(conf.high,2),nsmall=2),")")) %>% 
      mutate(estimate = log(estimate)) %>% 
      select(exposure=term, hrs, estimate, std.error)
    
    temp$study.site = i #label study site
    
    temp = temp[temp$exposure==exposure, ] # select ORs for exposure of interest
    
    output = bind_rows(output, temp)
  
  }
  
  return(output)
  
}
```

Run models

```{r, message=FALSE, warning=FALSE}
hrs_pnism_mci_crude = func_coxph(data=data1, outcome="inc_mci", exposure="pnism", adj="")
hrs_pd_mci_crude = func_coxph(data=data1, outcome="inc_mci", exposure="PD", adj="")

hrs_pnism_mci_adj = func_coxph(data=data1, outcome="inc_mci", exposure="pnism", adj=" + age + gender + illnocat + strata(PEDUC)")
hrs_pd_mci_adj = func_coxph(data=data1, outcome="inc_mci", exposure="PD", adj=" + age + gender + illnocat + strata(PEDUC)")
```

```{r, message=FALSE, warning=FALSE}
hrs_pnism_dem_crude = func_coxph(data=data2, outcome="inc_dem", exposure="pnism", adj="")
hrs_pd_dem_crude = func_coxph(data=data2, outcome="inc_dem", exposure="PD", adj="")

hrs_pnism_dem_adj = func_coxph(data=data2, outcome="inc_dem", exposure="pnism", adj=" + age + gender + illnocat + strata(PEDUC)")
hrs_pd_dem_adj = func_coxph(data=data2, outcome="inc_dem", exposure="PD", adj=" + age + gender + illnocat + strata(PEDUC)")
```

## Cox PH regression: meta-analysis

Run random-effects model, assumes there are 2 sources of error: 1) sampling error and 2) variance from the fact that included study sites are not from a single, homogeneous population, thus there is distribution of true effect sizes. Thus, the random-effects model aims to model the mean of the distribution of true effects.

Create function to plot forest plot

```{r}
plot_forest_meta = function(results){
  
  mgen = meta::metagen(TE = estimate,                           # make sure log(OR) than OR only
                       seTE = std.error,
                       studlab = study.site,
                       sm = "HR",
                       fixed = TRUE,
                       random = FALSE,
                       method.tau = "DL",                       # DerSimonian-Laird estimator
                       hakn = TRUE,                             # Hartung-Knapp adjustment of SEs
                       prediction = FALSE,                       # the above line and this line allow more   uncertainty in the estimation of between-study heterogeneity and appropriate for use in random-effects   meta-analysis
                       data = results)
  
  meta::forest(mgen, 
             rightlabs = c("HR", "95% CI", "Weight"),
             print.tau2 = FALSE,
             leftcols = c("studlab"))
  
  plot = grid.grab() 
  
  return(plot)

}
```

Parkinsonism/PD and incident mci (adjusted for age, sex, and illnocat, stratified by education)

```{r, fig.width = 10, fig.height = 6}
plot_pnism_mci_crude = plot_forest_meta(hrs_pnism_mci_crude[-1, ])
plot_pd_mci_crude = plot_forest_meta(hrs_pd_mci_crude[-c(1,3), ])
plot_pnism_mci_adj = plot_forest_meta(hrs_pnism_mci_adj[-1, ])
plot_pd_mci_adj = plot_forest_meta(hrs_pd_mci_adj[-c(1,3), ])
```

Parkinsonism/PD and incident dementia (adjusted for age, sex, and illnocat, stratified by education)

```{r, fig.width = 10, fig.height = 6}
plot_pnism_dem_crude = plot_forest_meta(hrs_pnism_dem_crude[-1, ])
plot_pd_dem_crude = plot_forest_meta(hrs_pd_dem_crude[-c(1,2), ])
plot_pnism_dem_adj = plot_forest_meta(hrs_pnism_dem_adj[-1, ])
plot_pd_dem_adj = plot_forest_meta(hrs_pd_dem_adj[-c(1,2), ])
```

Save data

```{r}
temp1 = bind_rows("crude" = hrs_pd_mci_crude, "adjusted" = hrs_pd_mci_adj, .id = "model")
temp2 = bind_rows("crude" = hrs_pnism_mci_crude, "adjusted" = hrs_pnism_mci_adj, .id = "model")
output1 = bind_rows(temp1, temp2)
output1

temp1 = bind_rows("crude" = hrs_pd_dem_crude, "adjusted" = hrs_pd_dem_adj, .id = "model")
temp2 = bind_rows("crude" = hrs_pnism_dem_crude, "adjusted" = hrs_pnism_dem_adj, .id = "model")
output2 = bind_rows(temp1, temp2)
output2
```


## Cox Proportional hazards regression: overall estimates

Create function to run Cox PH regression models

```{r}
func_coxph_overall = function(data, outcome, exposure, adj){
  
  # Create an empty output df
  output = data.frame(
    exposure = NA,
    hrs = NA,
    estimate = NA,
    std.error = NA
  )
 
  # Formula for the Cox PH regression
  outcome = paste0("Surv(censor_days/2, ", outcome, ")")
  formula = as.formula(paste0(outcome, " ~ ", exposure, adj))

  model = coxph(formula, data=data) # cox regression
  
  temp = tidy(model, conf.int = TRUE, conf.level = 0.95, exponentiate = TRUE) %>% # process regression output
      mutate(hrs = paste0(format.pval(round(estimate,2),nsmall=2), " (", format.pval(round(conf.low,2),nsmall=2),"-", format.pval(round(conf.high,2),nsmall=2),")")) %>% 
      mutate(estimate = log(estimate)) %>% 
      select(exposure=term, hrs, estimate, std.error)
    
  output = temp[temp$exposure==exposure, ] # select ORs for exposure of interest
  
  return(output)
  
}
```

Run models

```{r, message=FALSE, warning=FALSE}
hrs_pnism_mci_crude = func_coxph_overall(data=data1, outcome="inc_mci", exposure="pnism", adj="")
hrs_pd_mci_crude = func_coxph_overall(data=data1, outcome="inc_mci", exposure="PD", adj="")

hrs_pnism_mci_adj = func_coxph_overall(data=data1, outcome="inc_mci", exposure="pnism", adj=" + age + gender + illnocat + PEDUC")
hrs_pd_mci_adj = func_coxph_overall(data=data1, outcome="inc_mci", exposure="PD", adj=" + age + gender + illnocat + PEDUC")
```

```{r, message=FALSE, warning=FALSE}
hrs_pnism_dem_crude = func_coxph_overall(data=data2, outcome="inc_dem", exposure="pnism", adj="")
hrs_pd_dem_crude = func_coxph_overall(data=data2, outcome="inc_dem", exposure="PD", adj="")

hrs_pnism_dem_adj = func_coxph_overall(data=data2, outcome="inc_dem", exposure="pnism", adj=" + age + gender + illnocat + strata(PEDUC)")
hrs_pd_dem_adj = func_coxph_overall(data=data2, outcome="inc_dem", exposure="PD", adj=" + age + gender + illnocat + strata(PEDUC)")
```

Save data

```{r}
temp1 = bind_rows("crude" = hrs_pd_dem_crude, "adjusted" = hrs_pd_dem_adj, .id = "model")
temp2 = bind_rows("crude" = hrs_pnism_dem_crude, "adjusted" = hrs_pnism_dem_adj, .id = "model")
output_dementia_overall = bind_rows(temp1, temp2)
output_dementia_overall

temp1 = bind_rows("crude" = hrs_pd_mci_crude, "adjusted" = hrs_pd_mci_adj, .id = "model")
temp2 = bind_rows("crude" = hrs_pnism_mci_crude, "adjusted" = hrs_pnism_mci_adj, .id = "model")
output_mci_overall = bind_rows(temp1, temp2)
output_mci_overall
```