---
title: "PD MCI and dementia"
output: html_document
date: "2023-05-17"
---

# Data

### Open libraries

```{r}
library(broom)      # for tidy()
library(cowplot)
library(data.table) # for rbindlist()
library(descr)      # for crosstab(), descriptive statistics package
library(epiR)       # for epi.conf() to calculate CIs for prevalence
library(gridGraphics) # for grid.grab()
library(here)       # for easy file referencing by using the top-level directory of a file project
library(knitr)
library(tableone)
library(tidyverse)
```

What is the top-level of current project?

```{r}
here::here()
```

### Open 10/66 baseline dataset

Source codes

```{r}
source(here::here("Script", "Functions", "Data process", "func_open_and_process_data.R"))
source(here::here("Script", "Functions", "Data process", "func_compute_pd_variables.R"))
```

Set path for function input 

```{r}
path = here::here("Data", "raw data", "baseline survey", "prevalence_survey_data_1_3.dta")
```

Open dataset

```{r}
data = open_and_process_data(path, "dta") # this function opens a Stata dataset (dta) and converts Stata's labelled variables into factors
```

### Process dataset

Process Parkinsonism and PD variables

```{r}
data = compute_pd_variables(data)
```

Drop observations from China or India

```{r}
data = data %>% filter(centreid %in% c("Cuba", "DR", "Peru (urban)", "Peru (rural)", "Venezuela", "Mexico (urban)", "Mexico (rural)", "Puerto Rico"))

# drop unused factor levels
data$centreid = droplevels(data$centreid)
```

Subset relevant variables

```{r}
varnames = data %>% 
  select(houseid2, PARTICID, countryid, centreid, age, gender, rural, Nassets, PMARRY, CARENEED, illnocat, cdem1066, PEDUC, PTOLDDM, PSMOKE, PALCNOW, PALCPAST, PACTIVE, PMEATFRQ, PFISHFRQ, PVEGS, NEO14G, NEO6AU, NEO6AL, NEO6BU, NEO6BL, NEO4E, NEO4F, NOE1, NEO14E, PCVA, medserv, PPC, PHOSP, POTH, PPD, PDENT, PTH, PHOSAD, pnism, JorgePD, parkinsonism, PARK, mci, mcinosmi, cdrbox, cogscore, recall, STORY, objname, langexpr, langcomp, orientti, orientsp, ANIMALS) %>% 
  names()

data = data %>% select_if(names(.) %in% varnames)
```

Recode `parkinsonism` variable

```{r}
data = data %>% 
  mutate(parkinsonism = if_else(parkinsonism == "Parkinsonian", 1, 0, NA_real_))

summary(as.factor(data$parkinsonism))
```

Create a PD variable that combines the algorithm-based dx (`JorgePD`) and self-reported dx (`PARK`)

```{r}
# Create a PD variable that combines the algorithm-based dx (`JorgePD`) and self-reported dx (`PARK`)
data = data %>% 
  mutate(PD = case_when(JorgePD==1 | PARK=="probable" | PARK=="certain" ~ 1, 
                                       JorgePD==0 | PARK=="no" ~ 0, 
                                       TRUE ~ NA_real_))

summary(as.factor(data$PD))
```

Choose which MCI variable to use

  - mci
  - mcinosmi
  
```{r}
#data = data %>%  mutate(mci = factor(mci, levels=c("does not meet MCI criteria", "meets MCI criteria")))

# OR #

data = data %>% mutate(mci = factor(mcinosmi, levels=c("does not meet criteria for MCI", "meets crtieria for MCI"), labels=c("does not meet MCI criteria", "meets MCI criteria")))
```

Create new and dummy variables

```{r}
data = data %>% 
  mutate(agegrp = case_when(is.na(age) ~ NA_character_,
                            age<75 ~ "65-74",
                            age<85 ~ "75-84",
                            TRUE ~ "85+")) %>% 
  mutate(cogimp = if_else(mci=="meets MCI criteria" | cdem1066 == "case", 1, 0)) %>% 
  mutate(pd_mci = if_else(PD==1 & mci=="meets MCI criteria", 1, 0),
         pd_dem = if_else(PD==1 & cdem1066=="case", 1, 0),
         pnism_mci = if_else(pnism==1 & mci=="meets MCI criteria", 1, 0),
         pnism_dem = if_else(pnism==1 & cdem1066=="case", 1, 0),
         pd_cog = if_else(PD==1 & cogimp==1, 1, 0),
         pnism_cog = if_else(pnism==1 & cogimp==1, 1, 0))
```

Open mortality status

```{r}
path = here::here("Data", "raw data", "fu folder from Matthew", "specific outcomes", "mortality", "status_outcome (mortality cohort)_1_0.dta")
status_outcome_mortality_cohort = open_and_process_data(path, "dta")

path = here::here("Data", "raw data", "fu folder from Matthew", "specific outcomes", "mortality", "mortality_outcome1_1.dta")
mortality_outcome = open_and_process_data(path, "dta")
```

Merge vital status

```{r}
# baseline data:
# houseid2 is composite of centreid and houseid (houseid has 4 digits)
# therefore, unique participant-level id = composite of houseid2 and PARTICID

# status_outcome_mortality_cohort/mortality_outcome:
# need to create houseid2 by combining centreid and houseid (need to add leading 0s up to 4 digits first)
# centreid
# - 10 Cuba
# - 20 Dominican Republic
# - 30 Peru (urban)
# - 40 Peru (rural)
# - 50 Venezuela
# - 60 Mexico (urban)
# - 70 Mexico (rural)
# - 100 China (urban)
# - 110 China (rural)
# - 200 Puerto Rico

# Create houseid2
mortality_outcome = mortality_outcome %>% 
  mutate(centreid_num = case_when(centreid == "Cuba" ~ 10,
                                  centreid == "DR" ~ 20,
                                  centreid == "Peru (urban)" ~ 30,
                                  centreid == "Peru (rural)" ~ 40,
                                  centreid == "Venezuela" ~ 50,
                                  centreid == "Mexico (urban)" ~ 60,
                                  centreid == "Mexico (rural)" ~ 70,
                                  centreid == "China (urban)" ~ 100,
                                  centreid == "China (rural)" ~ 110,
                                  centreid == "Puerto Rico" ~ 200)) %>% 
  mutate(HOUSEID = stringr::str_pad(HOUSEID, 4, pad="0")) %>% 
  mutate(houseid2 = as.numeric(paste0(centreid_num, HOUSEID)))

# Merge vital status data with baseline data
data = data %>% 
  left_join(select(mortality_outcome, houseid2, PARTICID, vital_ascertained, dead2, fu_DATE, death_date, censor_days, censor_yr), by = c("houseid2", "PARTICID"))
```

# Descriptive analysis

## Cross-tabulation of variables

PD and MCI

```{r}
table(data$PD, data$mci, useNA="ifany")
```

Parkinsonism and MCI

```{r}
table(data$parkinsonism, data$mci, useNA="ifany")
```

PD and dementia

```{r}
table(data$PD, data$cdem1066, useNA="ifany")
```

Parkinsonism and dementia

```{r}
table(data$parkinsonism, data$cdem1066, useNA="ifany")
```

PD and cognitive impairment (MCI or dementia)

```{r}
table(data$PD, data$cogimp, useNA="ifany")
```

Parkinsonism and cognitive impairment (MCI or dementia)

```{r}
table(data$parkinsonism, data$cogimp, useNA="ifany")
```

## Cognitive variables

```{r}
temp = data %>% 
  select(cdrbox, cogscore, recall, STORY, objname, langexpr, langcomp, orientti, orientsp, ANIMALS) %>% 
  mutate(lang = langexpr+langcomp,
         orient = orientti+orientsp)
temp %>% summary()

temp %>% 
  select(cdrbox, cogscore, recall, STORY, objname, lang, orient, ANIMALS) %>% 
  gather() %>% 
  ggplot(aes(value)) +
  geom_histogram()+
  facet_wrap(~key, scales = 'free')
```

# Analysis

## Prevalence of PD and MCI/dementia by age group, sex, and country at baseline

Calculate prevalence and confidence interval using `epiR::epi.conf(,ctype="prop.single")` function

```{r}
# Select relevant variables
temp = data %>% select(agegrp, gender, pd_mci, pd_dem, pnism_mci, pnism_dem, pd_cog, pnism_cog)

get_prop3 = function(x) {

  case = sum(x, na.rm=TRUE)
  noncase = length(na.omit(x)) - case
  
  dat = as.matrix(cbind(case, noncase))
  
  temp = format(round(epi.conf(dat = dat, ctype = "prop.single")*100, digits = 1), nsmall=1)
  
  output = paste0(temp$est, "% (",  temp$lower, "%-", temp$upper, "%)")
    
  return(output)
}
 
# apply function by group 
output_list_age = by(temp, temp$agegrp, function(x){
  prop = apply(x[,-c(1:2)], 2, get_prop3)
  prop
})
output_list_sex = by(temp, temp$gender, function(x){
  prop = apply(x[,-c(1:2)], 2, get_prop3)
  prop
})

# apply function overall
overall_pct = apply(temp[,-c(1:2)], 2, get_prop3)
overall_pct = data.frame(
  group = "Overall",
  pd_mci = overall_pct[[1]],
  pd_dem = overall_pct[[2]],
  pnism_mci = overall_pct[[3]],
  pnism_dem = overall_pct[[4]],
  pd_cog = overall_pct[[5]],
  pnism_cog = overall_pct[[6]]
)

# combine output
cs_prop_grouped1 = as.data.frame(do.call(rbind, output_list_age))

cs_prop_grouped1$group = dimnames(cs_prop_grouped1)[[1]]

cs_prop_grouped2 = as.data.frame(do.call(rbind, output_list_sex))

cs_prop_grouped2$group = dimnames(cs_prop_grouped2)[[1]]

cs_prop_grouped = cs_prop_grouped2 %>% 
  bind_rows(cs_prop_grouped1) %>% 
  select(group, everything())

cs_prop_grouped = bind_rows(overall_pct, cs_prop_grouped)

kable(cs_prop_grouped)

write.csv(cs_prop_grouped, file = here::here("Output", "PD MCI and dementia paper", "Table1 prevalence of PD and MCI or dementia.csv"))
```

### Country-specific prevalence at baseline

Calculate prevalence and confidence interval using `epiR::epi.conf(,ctype="prop.single")` function

```{r}
# Select relevant variables
temp = data %>% 
  select(countryid, agegrp, gender, pd_dem, pnism_dem, pnism_mci) %>% 
  mutate(countrygender = factor(paste0(countryid, gender), 
                                levels = c("Cubafemale", "Cubamale", "DRfemale", "DRmale", "Mexicofemale", "Mexicomale", "Perufemale", "Perumale", "Puerto Ricofemale", "Puerto Ricomale", "Venezuelafemale", "Venezuelamale"),
                                labels = c("FCuba", "MCuba",
                                           "FDR", "MDR",
                                           "FMexico", "MMexico",
                                           "FPeru", "MPeru",
                                           "FPuerto Rico", "MPuerto Rico",
                                           "FVenezuela", "MVenezuela")),
         countryagegrp = factor(paste0(countryid, agegrp),
                                levels = c("Cuba65-74", "Cuba75-84", "Cuba85+",
                                           "DR65-74", "DR75-84", "DR85+",
                                           "Mexico65-74", "Mexico75-84", "Mexico85+",
                                           "Peru65-74", "Peru75-84", "Peru85+",
                                           "Puerto Rico65-74", "Puerto Rico75-84", "Puerto Rico85+",
                                           "Venezuela65-74", "Venezuela75-84", "Venezuela85+"),
                                labels = c("1Cuba", "2Cuba", "3Cuba",
                                           "1DR", "2DR", "3DR",
                                           "1Mexico", "2Mexico", "3Mexico",
                                           "1Peru", "2Peru", "3Peru",
                                           "1Puerto Rico", "2Puerto Rico", "3Puerto Rico",
                                           "1Venezuela", "2Venezuela", "3Venezuela"))) %>% 
  select(countryid, countryagegrp, countrygender, pd_dem, pnism_dem, pnism_mci)

get_prop3 = function(x) {

  case = sum(x, na.rm=TRUE)
  noncase = length(na.omit(x)) - case
  
  dat = as.matrix(cbind(case, noncase))
  
  temp = format(round(epi.conf(dat = dat, ctype = "prop.single")*100, digits = 1), nsmall=1)
  
  output = paste0(temp$est, "% (",  temp$lower, "%-", temp$upper, "%)")
    
  return(output)
}
 
# apply function by group 
output_list_age = by(temp, temp$countryagegrp, function(x){
  prop = apply(x[,-c(1:3)], 2, get_prop3)
  prop
})
output_list_sex = by(temp, temp$countrygender, function(x){
  prop = apply(x[,-c(1:3)], 2, get_prop3)
  prop
})

# apply function overall
overall_pct =  by(temp, temp$countryid, function(x){
  prop = apply(x[,-c(1:3)], 2, get_prop3)
  prop
})

# combine output
cs_prop_overall = as.data.frame(do.call(rbind, overall_pct))
cs_prop_overall$country = dimnames(cs_prop_overall)[[1]]
cs_prop_overall$level = "Overall"

cs_prop_grouped1 = as.data.frame(do.call(rbind, output_list_age))
cs_prop_grouped1$group = dimnames(cs_prop_grouped1)[[1]]

cs_prop_grouped2 = as.data.frame(do.call(rbind, output_list_sex))
cs_prop_grouped2$group = dimnames(cs_prop_grouped2)[[1]]

cs_prop_grouped = cs_prop_grouped2 %>% 
  bind_rows(cs_prop_grouped1) %>% 
  select(group, everything()) %>% 
  separate(group, c("level", "country"), 1)

cs_prop_grouped = bind_rows(cs_prop_overall, cs_prop_grouped)

output_pnism_mci = cs_prop_grouped %>% 
  select(-pd_dem, -pnism_dem) %>% 
  pivot_wider(names_from = country, values_from = pnism_mci)

output_pnism_dem = cs_prop_grouped %>% 
  select(-pd_dem, -pnism_mci) %>% 
  pivot_wider(names_from = country, values_from = pnism_dem)

output_pd_dem = cs_prop_grouped %>% 
  select(-pnism_dem, -pnism_mci) %>% 
  pivot_wider(names_from = country, values_from = pd_dem)

kable(output_pnism_mci)
kable(output_pnism_dem)
kable(output_pd_dem)

write.csv(output_pnism_mci, file = here::here("Output", "PD MCI and dementia paper", "Table1 prevalence of Pnism and MCI by country.csv"))
write.csv(output_pnism_dem, file = here::here("Output", "PD MCI and dementia paper", "Table1 prevalence of Pnism and dementia by country.csv"))
write.csv(output_pd_dem, file = here::here("Output", "PD MCI and dementia paper", "Table1 prevalence of PD and dementia by country.csv"))
```

## Table 1 - Characteristics of participants by PD and MCI/dementia status at baseline

```{r}
data1 = data %>% 
  mutate(pd_mci = paste(PD, mci),
         pd_dem = paste(PD, cdem1066),
         pnism_mci = paste(pnism, mci),
         pnism_dem = paste(pnism, cdem1066),
         pd_cog = paste(PD, cogimp),
         pnism_cog = paste(pnism, cogimp)) %>%  
  mutate(across(contains("_"), function(x) gsub("NA", NA_character_, x))) %>% 
  mutate(lang = langexpr + langcomp,
         orient = orientti + orientsp) %>% 
  select(contains("_"), age, gender, PEDUC, Nassets, rural, illnocat, cdrbox, cogscore, recall, STORY, objname, lang, orient, ANIMALS, vital_ascertained, dead2, censor_days, censor_yr)

vars = c("age", "gender", "PEDUC", "Nassets", "rural", "illnocat", "cdrbox", "cogscore", "recall", "STORY", "objname", "lang", "orient", "ANIMALS", "vital_ascertained")
factorVars = c("gender", "PEDUC", "Nassets", "rural", "illnocat", "vital_ascertained")

table1_pd_mci = tableone::CreateTableOne(data = data1,
                         vars = vars,
                         factorVars = factorVars,
                         strata = "pd_mci",
                         addOverall = TRUE)
table1_pd_dem = tableone::CreateTableOne(data = data1,
                         vars = vars,
                         factorVars = factorVars,
                         strata = "pd_dem",
                         addOverall = TRUE)
table1_pnism_mci = tableone::CreateTableOne(data = data1,
                         vars = vars,
                         factorVars = factorVars,
                         strata = "pnism_mci",
                         addOverall = TRUE)
table1_pnism_dem = tableone::CreateTableOne(data = data1,
                         vars = vars,
                         factorVars = factorVars,
                         strata = "pnism_dem",
                         addOverall = TRUE)

save_table1a = print(table1_pd_mci, quote = FALSE, noSpaces = TRUE, printToggle = FALSE, nonnormal=c("cdrbox", "cogscore", "STORY", "objname", "lang", "orient"))
save_table1b = print(table1_pd_dem, quote = FALSE, noSpaces = TRUE, printToggle = FALSE, nonnormal=c("cdrbox", "cogscore", "STORY", "objname", "lang", "orient"))
save_table1c = print(table1_pnism_mci, quote = FALSE, noSpaces = TRUE, printToggle = FALSE, nonnormal=c("cdrbox", "cogscore", "STORY", "objname", "lang", "orient"))
save_table1d = print(table1_pnism_dem, quote = FALSE, noSpaces = TRUE, printToggle = FALSE, nonnormal=c("cdrbox", "cogscore", "STORY", "objname", "lang", "orient"))

kable(save_table1a)
kable(save_table1b)
kable(save_table1c)
kable(save_table1d)

write.csv(save_table1a, file = here::here("Output",  "PD MCI and dementia paper", "Table1_PDmci.csv"))
write.csv(save_table1b, file = here::here("Output",  "PD MCI and dementia paper", "Table1_PDdem.csv"))
write.csv(save_table1c, file = here::here("Output",  "PD MCI and dementia paper", "Table1_PNISMmci.csv"))
write.csv(save_table1d, file = here::here("Output",  "PD MCI and dementia paper", "Table1_PNISMdem.csv"))
```

## Mortality status

Subset participants whose vital status was followed-up & get mortality and follow-up period

```{r}
data2 = data1 %>% 
  filter(vital_ascertained=="yes") %>% 
  mutate(across(contains("censor"), ~as.numeric(.x)))
```

```{r, include=FALSE}
vars = c("dead2", "censor_days", "censor_yr")
factorVars = c("dead2")

table2_pd_mci = tableone::CreateTableOne(data = data2,
                         vars = vars,
                         factorVars = factorVars,
                         strata = "pd_mci",
                         addOverall = TRUE)
table2_pd_dem = tableone::CreateTableOne(data = data2,
                         vars = vars,
                         factorVars = factorVars,
                         strata = "pd_dem",
                         addOverall = TRUE)
table2_pnism_mci = tableone::CreateTableOne(data = data2,
                         vars = vars,
                         factorVars = factorVars,
                         strata = "pnism_mci",
                         addOverall = TRUE)
table2_pnism_dem = tableone::CreateTableOne(data = data2,
                         vars = vars,
                         factorVars = factorVars,
                         strata = "pnism_dem",
                         addOverall = TRUE)

save_table2a = print(table2_pd_mci, quote = FALSE, noSpaces = TRUE, printToggle = FALSE)
save_table2b = print(table2_pd_dem, quote = FALSE, noSpaces = TRUE, printToggle = FALSE)
save_table2c = print(table2_pnism_mci, quote = FALSE, noSpaces = TRUE, printToggle = FALSE)
save_table2d = print(table2_pnism_dem, quote = FALSE, noSpaces = TRUE, printToggle = FALSE)

kable(save_table2a)
kable(save_table2b)
kable(save_table2c)
kable(save_table2d)
```
