---
title: "Analysis of the neuropsychiatric symptoms in Latin America (10/66)"
output: html_document
date: "2022-11-22"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE)
```

### Open libraries

```{r}
library(epiR)       # for epi.conf() to calculate CIs for prevalence
library(here)       # for easy file referencing by using the top-level directory of a file project
library(knitr)
library(labelled)   # for var_label() to get variable labels
library(openxlsx)   # for write.xlsx()
library(readxl)     # for read_excel()
library(tableone)
library(tidyverse)
```

What is the top-level of current project?
```{r}
here::here()
```

## Open data

### Open 10/66 baseline dataset

Source codes
```{r}
source(here::here("Script", "Functions", "Data process", "func_open_and_process_data.R"))
source(here::here("Script", "Functions", "Data process", "func_compute_pd_variables.R"))
```

Set path for function input 
```{r}
path = here::here("Data", "raw data", "baseline survey", "prevalence_survey_data_1_3.dta")
```

Open dataset
```{r}
data = open_and_process_data(path, "dta") # this function opens a Stata dataset (dta) and converts Stata's labelled variables into factors
```

### Process dataset

Process Parkinsonism and PD variables
```{r}
data = compute_pd_variables(data)
```

Drop observations from China or India
```{r}
data = data %>% filter(!countryid %in% c("China", "India"))

# drop unused factor levels
data$countryid = droplevels(data$countryid)
```

Subset relevant variables
```{r}
varnames = data %>% 
  select(houseid2, PARTICID, countryid, age, gender, rural, Nassets, anycare, illnocat, PCVA, cdem1066, PEDUC, zbtot, CAREEDUC, CARENEED, dsmdisab, starts_with("NPI"), starts_with("CARER"), starts_with("NEO1"), starts_with("NEO6"), starts_with("NEO4"), starts_with("NOE1"), pnism, JorgePD, combined) %>% 
  names()

data = data %>% select_if(names(.) %in% varnames)
```

Create variable = total number of the NPI symptoms present [0-12]
```{r}
temp = data %>% 
  select(starts_with("NPI"), -ends_with("D"), -ends_with("DIS"), -ends_with("SEV"), -npisev, -npidis, -combined) %>% 
  mutate(across(everything(), ~if_else(.x=="yes", 1, 0))) %>%
  mutate(npi_sum = rowSums(., na.rm = TRUE),
         npi_bin1 = if_else(npi_sum == 0, "no", "yes"),
         npi_bin3 = if_else(npi_sum >= 3, "3 or more", "<3"),
         npi_sum_cat = factor(case_when(is.na(npi_sum) ~ NA_character_,
                                        npi_sum == 0 ~ "0",
                                        npi_sum == 1 ~ "1",
                                        npi_sum == 2 ~ "2",
                                        TRUE ~ "3 or more"))) %>%
  select(npi_sum, npi_bin1, npi_bin3, npi_sum_cat)
  
mydata = bind_cols(data, temp)
```


### List of neuropsychiatric symptoms

```{r}
npi = mydata %>% 
  select(starts_with("NPI"), -starts_with("npi_")) %>% 
  labelled::var_label() %>% 
  as_tibble() %>% 
  gather(key = variable, value = description) %>% 
  mutate(description = str_sub(description, 8, -1), # removes the first 7 characters
         description = str_remove(description, "\\-"), # remove all strings after '-'
         description = str_trim(description)) # remove any leading or trailing white spaces

kable(npi)
```

## Descriptive statistics

### Table 1 Participant characteristics by group

```{r}
table1 = tableone::CreateTableOne(data = mydata,
                         vars = c("age", "gender", "PEDUC", "Nassets", "rural", "illnocat", "dsmdisab", "npisev", "npidis"),
                         factorVars = c("gender", "PEDUC", "Nassets", "rural", "illnocat"),
                         strata = "combined")
table1_tot = tableone::CreateTableOne(data = mydata,
                         vars = c("age", "gender", "PEDUC", "Nassets", "rural", "illnocat", "dsmdisab", "npisev", "npidis"),
                         factorVars = c("gender", "PEDUC", "Nassets", "rural", "illnocat"))

save_table1 = print(table1, nonnormal = c("npisev", "npidis"), quote = FALSE, noSpaces = TRUE, printToggle = FALSE)
save_table1_tot = print(table1_tot, nonnormal = c("npisev", "npidis"), quote = FALSE, noSpaces = TRUE, printToggle = FALSE)

kable(save_table1)
kable(save_table1_tot)

write.csv(save_table1, file = here::here("Output", "Neuropsychiatric symptoms in PD paper", "Table1.csv"))
write.csv(save_table1_tot, file = here::here("Output", "Neuropsychiatric symptoms in PD paper", "Table1 (total).csv"))
```
Check missingness of sociodemographic characteristics

```{r}
summary(table1_tot)
```


*Supplementary table showing difference in the characteristics of participants with dx versus those without*

```{r}
tempdata = mydata %>% 
  select(combined, age, gender, PEDUC, Nassets, rural, illnocat, dsmdisab, npi_sum_cat, npisev, npidis) %>% 
  mutate(missing = as.factor(if_else(!is.na(combined), "Has diagnosis", "Missing diagnosis")))

supptable1 = tableone::CreateTableOne(data = tempdata,
                         vars = c("age", "gender", "PEDUC", "Nassets", "rural", "illnocat", "dsmdisab", "npi_sum_cat", "npisev", "npidis"),
                         factorVars = c("gender", "PEDUC", "Nassets", "rural", "illnocat"),
                         strata = "missing")

save_supptable1 = print(supptable1, nonnormal = c("npisev", "npidis"), quote = FALSE, noSpaces = TRUE, printToggle = FALSE)

kable(save_supptable1)

write.csv(save_supptable1, file = here::here("Output", "Neuropsychiatric symptoms in PD paper", "suppTable1.csv"))
```


### Table 2 Frequency and prevalence of neuropsychiatric symptoms by group (for individual symptoms and counts)

**Histogram of the number of NPI symptoms per individual**
```{r}
temp1 = mydata %>% 
  select(starts_with("NPI"), combined, npisev, npidis)

temp2 = temp1 %>% 
  select(-ends_with("D"), -ends_with("DIS"), -ends_with("SEV"), -npisev, -npidis, -combined) %>% 
  mutate(across(everything(), ~if_else(.x=="yes", 1, 0))) %>% 
  mutate(npi_sum = rowSums(.),
         npi_sum_cat = factor(case_when(is.na(npi_sum) ~ NA_character_,
                                        npi_sum == 0 ~ "0",
                                        npi_sum == 1 ~ "1",
                                        npi_sum == 2 ~ "2",
                                        TRUE ~ "3 or more"))) %>% 
  select(npi_sum, npi_sum_cat)

hist(temp2$npi_sum)
summary(temp2$npi_sum_cat)
```

**Frequency and prevalence of NPI symptoms by group**
```{r}
temp1 = bind_cols(temp1, temp2)

table2 = tableone::CreateTableOne(data = temp1,
                                  vars = c("NPI1", "NPI2", "NPI3", "NPI4", "NPI5", "NPI6",
                                           "NPI7", "NPI8", "NPI9", "NPI10", "NPI11", "NPI12", "npi_sum_cat", "npisev", "npidis"),
                                  factorVars = c("NPI1", "NPI2", "NPI3", "NPI4", "NPI5", "NPI6",
                                           "NPI7", "NPI8", "NPI9", "NPI10", "NPI11", "NPI12", "npi_sum_cat"),
                                  strata = "combined")

table2_tot = tableone::CreateTableOne(data = temp1,
                                  vars = c("NPI1", "NPI2", "NPI3", "NPI4", "NPI5", "NPI6",
                                           "NPI7", "NPI8", "NPI9", "NPI10", "NPI11", "NPI12", "npi_sum_cat", "npisev", "npidis"),
                                  factorVars = c("NPI1", "NPI2", "NPI3", "NPI4", "NPI5", "NPI6",
                                           "NPI7", "NPI8", "NPI9", "NPI10", "NPI11", "NPI12", "npi_sum_cat"))

save_table2 = print(table2, quote = FALSE, noSpaces = TRUE, printToggle = FALSE)
save_table2_tot = print(table2_tot, quote = FALSE, noSpaces = TRUE, printToggle = FALSE)

kable(save_table2)
kable(save_table2_tot)

write.csv(save_table2, file = here::here("Output", "Neuropsychiatric symptoms in PD paper", "Table2 NPI frequency (grouped).csv"))
write.csv(save_table2_tot, file = here::here("Output", "Neuropsychiatric symptoms in PD paper", "Table2 NPI frequency (total).csv"))
```

Check missingness of NPI symptoms

```{r}
summary(table2_tot)
```

**Figure**

```{r}
temp3 = mydata %>% 
  select(starts_with("NPI"), combined) %>% 
  select(-ends_with("D"), -ends_with("DIS"), -ends_with("SEV"), combined) %>% 
  mutate(across(c(NPI1:NPI12), ~if_else(.x=="yes", 1, 0)))

get_prop = function(x) (sum(x, na.rm=TRUE) / length(na.omit(x))) * 100 # function to compute percentages
  # what to do with those missing data on NPS??? excluded these individuals in the calculation of prevalence for now using na.omit(x)

# apply function by group 
output_list = by(temp3, temp3$combined, function(x){
  prop = apply(x[,1:12], 2, get_prop)
  prop
})

# combine output
npi_prop_grouped = as.data.frame(do.call(rbind, output_list))

npi_prop_grouped$combined = dimnames(npi_prop_grouped)[[1]]

npi_prop_grouped = npi_prop_grouped %>% 
  pivot_longer(cols = -combined,
               names_to = "npi",
               values_to = "pct") %>%
  left_join(npi, by = c("npi"="variable"))
```

```{r}
# order NPS by decreasing prevlence
npi_order = npi_prop_grouped %>% 
  filter(combined=="Parkinsonism and dementia") %>% 
  arrange(desc(pct)) %>% 
  pull(description)

plot_npi_prev_grouped = npi_prop_grouped %>% 
  mutate(description = factor(description, levels = npi_order),
         combined = factor(combined, levels = c("Control", "Parkinsonism", "Dementia", "Parkinsonism and dementia"))) %>% 
  ggplot(aes(y=pct, x=combined, fill=combined)) + 
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste0(round(pct,0), "%")), hjust=0.5, vjust=1, size=3) +
  scale_fill_brewer(palette = "Set2") +
  labs(fill = "Diagnosis group",
       x = "Diagnosis group",
       y = "Prevalence (%)") +
  facet_wrap(~description, nrow=2, ncol=6, dir = "h") +
  theme_classic() +
  theme(legend.position = "bottom",
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank()) #element_text(angle=35, vjust = 1, hjust=1)

plot_npi_prev_grouped

ggsave(here::here("Output", "Neuropsychiatric symptoms in PD paper", "npi_prev_group.tiff"), plot = plot_npi_prev_grouped, width = 24, height = 12, units = "cm")
```

### Table 3 Severity of neuropsychiatric symptoms by group

```{r}
npi_sev = mydata %>% 
  filter(!is.na(combined)) %>% 
  select(starts_with("NPI"), -ends_with("DIS"), -NPI1D, combined, -npisev) %>%
  # only include participants who exhibit symptoms (i.e. as denominator)
  mutate(NPI1 = if_else(NPI1 == "no", NA_character_, as.character(NPI1SEV)),
         NPI2 = if_else(NPI2 == "no", NA_character_, as.character(NPI2SEV)),
         NPI3 = if_else(NPI3 == "no", NA_character_, as.character(NPI3SEV)),
         NPI4 = if_else(NPI4 == "no", NA_character_, as.character(NPI4SEV)),
         NPI5 = if_else(NPI5 == "no", NA_character_, as.character(NPI5SEV)),
         NPI6 = if_else(NPI6 == "no", NA_character_, as.character(NPI6SEV)),
         NPI7 = if_else(NPI7 == "no", NA_character_, as.character(NPI7SEV)),
         NPI8 = if_else(NPI8 == "no", NA_character_, as.character(NPI8SEV)),
         NPI9 = if_else(NPI9 == "no", NA_character_, as.character(NPI9SEV)),
         NPI10 = if_else(NPI10 == "no", NA_character_, as.character(NPI10SEV)),
         NPI11 = if_else(NPI11 == "no", NA_character_, as.character(NPI11SEV)),
         NPI12 = if_else(NPI12 == "no", NA_character_, as.character(NPI12SEV))) %>% 
  select(combined, starts_with("NPI"), -ends_with("SEV")) 

#head(npi_sev)

# Overall percentages
overall_freq_npi_sev = npi_sev %>% 
  pivot_longer(NPI1:NPI12, names_to = "npi", values_to = "severity") %>%
  left_join(npi, by = c("npi"="variable")) %>%  
  select(-npi, -combined) %>%
  filter(!is.na(severity)) %>% # remove observations who did not report symptoms or were missing data on severity
  group_by(description) %>% 
  count(severity) %>% 
  ungroup()

tot = overall_freq_npi_sev %>% 
  group_by(description) %>% 
  summarise(tot = sum(n))
  
# Grouped percentages
grouped_freq_npi_sev = npi_sev %>%
  pivot_longer(NPI1:NPI12, names_to = "npi", values_to = "severity") %>%
  left_join(npi, by = c("npi"="variable")) %>%  
  select(-npi) %>%
  filter(!is.na(severity)) %>% # remove observations who did not report symptoms or were missing data on severity
  group_by(combined, description) %>% 
  count(severity) %>% 
  ungroup()

tot_grouped = grouped_freq_npi_sev %>% 
  group_by(combined, description) %>% 
  summarise(tot = sum(n))

# Combine data
overall_npi_sev = overall_freq_npi_sev %>% 
  bind_rows(select(tot, description, n=tot) %>% mutate(severity="total")) %>% 
  arrange(description) %>% 
  left_join(tot, by = "description") %>%
  mutate(pct = n/tot*100,
         Total = paste0(n, " (", format(round(pct,1), nsmall=1), "%)")) %>%
  select(-n, -tot, -pct)

save_npi_sev = grouped_freq_npi_sev %>% 
  bind_rows(select(tot_grouped, combined, description, n=tot) %>% mutate(severity="total")) %>% 
  arrange(combined, description) %>% 
  left_join(tot_grouped, by = c("combined", "description")) %>% 
  mutate(pct = n/tot*100,
         n_pct = paste0(n, " (", format(round(pct,1), nsmall=1), "%)")) %>%
  select(-n, -tot, -pct) %>% 
  pivot_wider(names_from = combined,
              values_from = n_pct) %>% 
  left_join(overall_npi_sev, by = c("description", "severity")) %>% 
  mutate(severity = factor(severity, levels = c("total", "mild", "moderate", "severe"), labels = c("Total", "Mild", "Moderate", "Severe"))) %>% 
  arrange(description, severity)

# NPI order
npi_order = npi %>% 
  filter(grepl("[0-9]$", variable)) %>%  
  pull(description)

save_npi_sev = save_npi_sev %>% 
  mutate(description = factor(description, levels = npi_order)) %>% 
  arrange(description, severity) %>% 
  select(description, severity, Total, everything())

kable(save_npi_sev)

write.csv(save_npi_sev, file = here::here("Output", "Neuropsychiatric symptoms in PD paper", "Table3 Severity of NPI by group.csv"))
```

```{r, eval=FALSE, include=FALSE}
# Panelled pie charts

to_plot_npi_sev = npi_sev %>% 
  left_join(tot, by = c("combined", "description")) %>% 
  mutate(pct = n/tot,
         severity = factor(severity, levels = c("mild", "moderate", "severe"), labels = c("Mild", "Moderate", "Severe")),
         label = paste0(round(pct*100,0),"%")) %>% 
  group_by(combined, description) %>% 
  mutate(cumulative = cumsum(n),
         midpoint = cumulative-n/2)

plot_npi_sev = ggplot(to_plot_npi_sev, aes(x="", y=pct, fill=severity)) +
  geom_bar(width=1, stat="identity") +
  coord_polar("y", start=0) +
  #geom_text(aes(y=midpoint, label=label), size=2) +
  scale_fill_manual(values = c("#00BA38", "#619CFF", "#F8766D")) +
  labs(fill = "Severity") +
  facet_grid(description ~ combined) +
  theme_void()

plot_npi_sev

ggsave(here::here("Output", "Neuropsychiatric symptoms in PD paper", "npi_severity_group.png"), plot = plot_npi_sev, width = 10, height = 20, units = "cm")
```

### Table 4 Adjusted logistic regression model for the association between neuropsychiatric symptoms and diagnosis

```{r, eval=FALSE, include=FALSE}
model = glm(NPI1 ~ combined + age + gender + PEDUC, family = binomial(link="logit"), data = mydata)

summary(model)
```

```{r}
# Function to run cox models adjusted for age, sex, and region
func_logistic_regression = function(data, outcome, exposure, adjustment){ # input outcome, exposure, and adjustment as characters
  
  # formula
  formula = as.formula(paste(outcome, " ~ ", exposure, adjustment))
  
  # model
  model = glm(formula, family = binomial(link="logit"), data = data)
  
  # numbers
  tab = table(mydata[[exposure]], mydata[[outcome]])
  
  # Extract data
  results = data.frame(
    outcome = outcome,
    level = dimnames(tab)[[1]],
    case = tab[, "yes"],
    noncase = tab[, "no"],
    or = exp(model$coefficients)[1:4],
    lci = exp(confint(model))[1:4,1][1:4],
    uci = exp(confint(model))[1:4,2][1:4]
    
  )
                       
  return(results)
}

npi_ls = npi %>% select(variable) %>% 
  filter(grepl("[0-9]$", variable)) %>%  # filters variables ending with a number
  distinct() %>% 
  pull()

output_ls1 = map(npi_ls, func_logistic_regression, data=mydata, exposure="combined", adjustment="")
output_ls2 = map(npi_ls, func_logistic_regression, data=mydata, exposure="combined", adjustment=" + age + gender + PEDUC + illnocat")
output_ls3 = map(npi_ls, func_logistic_regression, data=mydata, exposure="combined", adjustment=" + age + gender + PEDUC + illnocat + CARERAGE + CARERSEX + CAREEDUC + CARERREL")
output_ls4 = map(npi_ls, func_logistic_regression, data=mydata, exposure="combined", adjustment=" + age + gender + PEDUC + illnocat + CARERAGE + CARERSEX + CAREEDUC + CARERREL + countryid")
```

Process output data
```{r}
output_data1 = do.call(rbind, output_ls1) %>% 
  left_join(npi, by = c("outcome" = "variable")) %>% 
  mutate(ors = paste0(format(round(or,2), nsmall=2), " (", format(round(lci,2), nsmall=2), "-", format(round(uci,2), nsmall=2), ")")) %>% 
  select(description, level, case, noncase, crude_ors = ors)

output_data2 = do.call(rbind, output_ls2) %>% 
  left_join(npi, by = c("outcome" = "variable")) %>% 
  mutate(ors = paste0(format(round(or,2), nsmall=2), " (", format(round(lci,2), nsmall=2), "-", format(round(uci,2), nsmall=2), ")")) %>% 
  select(description, level, adjusted_ors = ors)

output_data3 = do.call(rbind, output_ls3) %>% 
  left_join(npi, by = c("outcome" = "variable")) %>% 
  mutate(ors = paste0(format(round(or,2), nsmall=2), " (", format(round(lci,2), nsmall=2), "-", format(round(uci,2), nsmall=2), ")")) %>% 
  select(description, level, adjusted_ors = ors)

output_data4 = do.call(rbind, output_ls4) %>% 
  left_join(npi, by = c("outcome" = "variable")) %>% 
  mutate(ors = paste0(format(round(or,2), nsmall=2), " (", format(round(lci,2), nsmall=2), "-", format(round(uci,2), nsmall=2), ")")) %>% 
  select(description, level, adjusted_ors = ors)

output_data = output_data1 %>% 
  left_join(output_data2, by = c("description", "level")) %>% 
  left_join(output_data3, by = c("description", "level")) %>% 
  left_join(output_data4, by = c("description", "level")) 

output_data

write.csv(output_data, file = here::here("Output", "Neuropsychiatric symptoms in PD paper", "Table4 Logistic regression.csv"))
```

### Table 5 Clinically significant caregiver distress due to neuropsychiatric symptoms by group

*Clinically significant distress was defined as having moderate, severe, or extreme distress*

```{r}
clinical_sig = mydata %>% 
  select(NPI1D, starts_with("NPI"), -ends_with("SEV"), combined, -npidis, age, gender, PEDUC, illnocat, CARERAGE, CARERSEX, CAREEDUC, CARERREL, countryid) %>% 
  # only include participants who exhibit symptoms (i.e. as denominator)
  mutate(NPI1 = if_else(NPI1 == "no", NA_character_, as.character(NPI1D)),
         NPI2 = if_else(NPI2 == "no", NA_character_, as.character(NPI2DIS)),
         NPI3 = if_else(NPI3 == "no", NA_character_, as.character(NPI3DIS)),
         NPI4 = if_else(NPI4 == "no", NA_character_, as.character(NPI4DIS)),
         NPI5 = if_else(NPI5 == "no", NA_character_, as.character(NPI5DIS)),
         NPI6 = if_else(NPI6 == "no", NA_character_, as.character(NPI6DIS)),
         NPI7 = if_else(NPI7 == "no", NA_character_, as.character(NPI7DIS)),
         NPI8 = if_else(NPI8 == "no", NA_character_, as.character(NPI8DIS)),
         NPI9 = if_else(NPI9 == "no", NA_character_, as.character(NPI9DIS)),
         NPI10 = if_else(NPI10 == "no", NA_character_, as.character(NPI10DIS)),
         NPI11 = if_else(NPI11 == "no", NA_character_, as.character(NPI11DIS)),
         NPI12 = if_else(NPI12 == "no", NA_character_, as.character(NPI12DIS))) %>% 
  select(combined, starts_with("NPI"), -ends_with("DIS"), -NPI1D, age, gender, PEDUC, illnocat, CARERAGE, CARERSEX, CAREEDUC, CARERREL, countryid) 

clinical_sig = clinical_sig %>%
  # define non-clinically significant as having "not distressing", "minimal", or "mild" symptoms; define everything else as clinically significant (moderate, severe, extreme)
  mutate(across(NPI1:NPI12, ~as.numeric(case_when(is.na(.x) ~ NA_character_,
                                       .x == "no symptom, or not distressing" | .x == "minimal" | .x == "mild" ~ "0",
                                       TRUE ~ "1")))) %>% 
  mutate(count = rowSums(select(., NPI1:NPI12), na.rm=TRUE),
         clinical_sig_nps3 = if_else(count>=3, 1, 0))

#kable(clinical_sig)
```

```{r}
get_prop2 = function(x) {

  pct = sum(x, na.rm=TRUE) / length(na.omit(x)) * 100 # function to compute percentages
  n = sum(x, na.rm=TRUE)
  tot = length(na.omit(x))

  output = paste0(n, "/", tot, " (", format(round(pct, 1), nsmall=1), "%)")
  return(output)
}
 
# apply function by group 
output_list = by(clinical_sig, clinical_sig$combined, function(x){
  prop = apply(x[,-1], 2, get_prop2)
  prop
})

# apply function overall
overall_pct = apply(clinical_sig[,-1], 2, get_prop2)

# combine output
cs_prop_grouped = as.data.frame(do.call(rbind, output_list))

cs_prop_grouped$combined = dimnames(cs_prop_grouped)[[1]]

cs_prop_grouped = cs_prop_grouped %>% 
  pivot_longer(cols = -combined,
               names_to = "npi",
               values_to = "pct") %>%
  left_join(npi, by = c("npi"="variable")) %>% 
  select(-npi) %>% 
  pivot_wider(names_from = combined,
              values_from = pct)

cs_prop_grouped$Total = overall_pct

kable(cs_prop_grouped)

write.csv(cs_prop_grouped, file = here::here("Output", "Neuropsychiatric symptoms in PD paper", "Table5 Clinically significant symptoms.csv"))
```

Calculate prevalence and confidence interval using `epiR::epi.conf(,ctype="prop.single")` function

```{r}
get_prop3 = function(x) {

  case = sum(x, na.rm=TRUE)
  noncase = length(na.omit(x)) - case
  
  dat = as.matrix(cbind(case, noncase))
  
  temp = format(round(epi.conf(dat = dat, ctype = "prop.single")*100, digits = 0), nsmall=0)
  
  output = paste0(temp$est, "% (",  temp$lower, "%-", temp$upper, "%)")
    
  return(output)
}
 
# apply function by group 
output_list = by(clinical_sig, clinical_sig$combined, function(x){
  prop = apply(x[,-1], 2, get_prop3)
  prop
})

# apply function overall
overall_pct = apply(clinical_sig[,-1], 2, get_prop3)

# combine output
cs_prop_grouped = as.data.frame(do.call(rbind, output_list))

cs_prop_grouped$combined = dimnames(cs_prop_grouped)[[1]]

cs_prop_grouped = cs_prop_grouped %>% 
  pivot_longer(cols = -combined,
               names_to = "npi",
               values_to = "pct") %>%
  left_join(npi, by = c("npi"="variable")) %>% 
  select(-npi) %>% 
  pivot_wider(names_from = combined,
              values_from = pct)

cs_prop_grouped$Total = overall_pct

kable(cs_prop_grouped)

write.csv(cs_prop_grouped, file = here::here("Output", "Neuropsychiatric symptoms in PD paper", "Table5 Clinically significant symptoms (prevalence 95%CI).csv"))
```

What is the percentage of caregivers reporting at least one NPI symptom to be at least moderate distress?

```{r}
clinical_sig1 = clinical_sig %>% 
  filter(!if_all(NPI1:NPI12, is.na)) %>%  # exclude participants who do not report any symptoms
  rowwise() %>% 
  mutate(sum = sum(across(starts_with("NPI")), na.rm=TRUE)) %>% 
  mutate(any_cs = if_else(sum>=1, 1, 0)) %>% 
  select(-starts_with("NPI"))

summary(as.factor(clinical_sig1$any_cs))
```

Odds of 3+ NPS with clinically significant symptoms

```{r}
# Function to run cox models adjusted for age, sex, and region
func_logistic_regression1 = function(data, outcome, exposure, adjustment){ # input outcome, exposure, and adjustment as characters
  
  # formula
  formula = as.formula(paste(outcome, " ~ ", exposure, adjustment))
  
  # model
  model = glm(formula, family = binomial(link="logit"), data = data)
  
  # numbers
  tab = table(data[[exposure]], data[[outcome]])
  
  # Extract data
  results = data.frame(
    outcome = outcome,
    level = dimnames(tab)[[1]],
    case = tab[, "1"],
    noncase = tab[, "0"],
    or = exp(model$coefficients)[1:4],
    lci = exp(confint(model))[1:4,1][1:4],
    uci = exp(confint(model))[1:4,2][1:4]
    
  )
                       
  return(results)
}


output_ls1 = func_logistic_regression1(outcome="clinical_sig_nps3", data=clinical_sig, exposure="combined", adjustment="")
output_ls2 = func_logistic_regression1(outcome="clinical_sig_nps3", data=clinical_sig, exposure="combined", adjustment=" + age + gender + PEDUC + illnocat")
output_ls3 = func_logistic_regression1(outcome="clinical_sig_nps3", data=clinical_sig, exposure="combined", adjustment=" + age + gender + PEDUC + illnocat + CARERAGE + CARERSEX + CAREEDUC + CARERREL")
output_ls4 = func_logistic_regression1(outcome="clinical_sig_nps3", data=clinical_sig, exposure="combined", adjustment=" + age + gender + PEDUC + illnocat + CARERAGE + CARERSEX + CAREEDUC + CARERREL + countryid")
```

Process output data
```{r}
output_data = do.call(rbind, list("crude"=output_ls1, "model1"=output_ls2, "model2"=output_ls3, "model3"=output_ls4)) %>% 
  tibble::rownames_to_column('model') %>% 
  mutate(ors = paste0(format(round(or,2), nsmall=2), " (", format(round(lci,2), nsmall=2), "-", format(round(uci,2), nsmall=2), ")")) %>% 
  select(model, level, case, noncase, crude_ors = ors)

output_data$model = gsub("\\..*", " ", output_data$model)

output_data

write.csv(output_data, file = here::here("Output", "Neuropsychiatric symptoms in PD paper", "Table4 Logistic regression clinical sig NPS3.csv"))
```


### Table 6 Caregiver's characteristics by group

```{r}
table6 = tableone::CreateTableOne(data = mydata,
                         vars = c("CARERAGE", "CARERSEX", "CAREEDUC", "CARENEED", "CARERREL", "zbtot"),
                         factorVars = c("CARERSEX", "CAREEDUC", "CARENEED", "npi_bin3"),
                         strata = "combined")
table6_tot = tableone::CreateTableOne(data = mydata,
                         vars = c("CARERAGE", "CARERSEX", "CAREEDUC", "CARENEED", "CARERREL", "zbtot"),
                         factorVars = c("CARERSEX", "CAREEDUC", "CARENEED", "npi_bin3"))

save_table6 = print(table6, quote = FALSE, noSpaces = TRUE, printToggle = FALSE)
save_table6_tot = print(table6_tot, quote = FALSE, noSpaces = TRUE, printToggle = FALSE)

kable(save_table6)
kable(save_table6_tot)

write.csv(save_table6, file = here::here("Output", "Neuropsychiatric symptoms in PD paper", "Table6 Caregiver characteristics.csv"))
```

Get mean zarit score by the number of NPI

```{r}
mydata %>% 
  group_by(combined, npi_bin3) %>% 
  summarise(mean = mean(zbtot, na.rm=TRUE),
            sd = sd(zbtot, na.rm=TRUE)) %>% 
  mutate(across(c("mean", "sd"), ~format(round(.,2), nsmall=2))) %>% 
  mutate(mean_sd = paste0(mean, " (", sd, ")")) 

mydata %>% 
  group_by(npi_bin3) %>% 
  summarise(mean = mean(zbtot, na.rm=TRUE),
            sd = sd(zbtot, na.rm=TRUE)) %>% 
  mutate(across(c("mean", "sd"), ~format(round(.,2), nsmall=2))) %>% 
  mutate(mean_sd = paste0(mean, " (", sd, ")")) 
```