---
title: "Table 1"
output: html_document
date: "2022-12-01"
---

### Open libraries

```{r}
library(broom)      # for tidy()
library(descr)      # for crosstab(), descriptive statistics package
library(here)       # for easy file referencing by using the top-level directory of a file project
library(kableExtra)
library(knitr)
library(tableone)
library(tidyverse)
```

What is the top-level of current project?
```{r}
here::here()
```

### Open 10/66 baseline dataset

Source codes
```{r}
source(here::here("Script", "Functions", "Data process", "func_open_and_process_data.R"))
source(here::here("Script", "Functions", "Data process", "func_compute_pd_variables.R"))
```

Set path for function input 
```{r}
path = here::here("Data", "raw data", "baseline survey", "prevalence_survey_data_1_3.dta")
```

Open dataset
```{r}
data = open_and_process_data(path, "dta") # this function opens a Stata dataset (dta) and converts Stata's labelled variables into factors
```

### Open mortality status

```{r}
path = here::here("Data", "raw data", "fu folder from Matthew", "specific outcomes", "mortality", "status_outcome (mortality cohort)_1_0.dta")
status_outcome_mortality_cohort = open_and_process_data(path, "dta")

path = here::here("Data", "raw data", "fu folder from Matthew", "specific outcomes", "mortality", "mortality_outcome1_1.dta")
mortality_outcome = open_and_process_data(path, "dta")
```

### Process dataset

Process Parkinsonism and PD variables
```{r}
data = compute_pd_variables(data)
```

Drop observations from China or India
```{r}
data = data %>% filter(centreid %in% c("Cuba", "DR", "Peru (urban)", "Peru (rural)", "Venezuela", "Mexico (urban)", "Mexico (rural)", "Puerto Rico"))

# drop unused factor levels
data$centreid = droplevels(data$centreid)
```

Subset relevant variables
```{r}
varnames = data %>% 
  select(houseid2, PARTICID, countryid, centreid, age, gender, rural, Nassets, PMARRY, CARENEED, illnocat, cdem1066, PEDUC, PTOLDDM, PSMOKE, PALCNOW, PALCPAST, PACTIVE, PMEATFRQ, PFISHFRQ, PVEGS, NEO14G, NEO6AU, NEO6AL, NEO6BU, NEO6BL, NEO4E, NEO4F, NOE1, NEO14E, PCVA, medserv, PPC, PHOSP, POTH, PPD, PDENT, PTH, PHOSAD, pnism, JorgePD, PARK) %>% 
  names()

data = data %>% select_if(names(.) %in% varnames)
```

Create a PD variable that combines the algorithm-based dx (`JorgePD`) and self-reported dx (`PARK`)

```{r}
# Create a PD variable that combines the algorithm-based dx (`JorgePD`) and self-reported dx (`PARK`)
data = data %>% 
  mutate(JorgePD_or_selfPD = case_when(JorgePD==1 | PARK=="probable" | PARK=="certain" ~ 1, 
                                       JorgePD==0 | PARK=="no" ~ 0, 
                                       TRUE ~ NA_real_))

summary(as.factor(data$JorgePD_or_selfPD))
```

Merge vital status
```{r}
# baseline data:
# houseid2 is composite of centreid and houseid (houseid has 4 digits)
# therefore, unique participant-level id = composite of houseid2 and PARTICID

# status_outcome_mortality_cohort/mortality_outcome:
# need to create houseid2 by combining centreid and houseid (need to add leading 0s up to 4 digits first)
# centreid
# - 10 Cuba
# - 20 Dominican Republic
# - 30 Peru (urban)
# - 40 Peru (rural)
# - 50 Venezuela
# - 60 Mexico (urban)
# - 70 Mexico (rural)
# - 100 China (urban)
# - 110 China (rural)
# - 200 Puerto Rico

# Create houseid2
mortality_outcome = mortality_outcome %>% 
  mutate(centreid_num = case_when(centreid == "Cuba" ~ 10,
                                  centreid == "DR" ~ 20,
                                  centreid == "Peru (urban)" ~ 30,
                                  centreid == "Peru (rural)" ~ 40,
                                  centreid == "Venezuela" ~ 50,
                                  centreid == "Mexico (urban)" ~ 60,
                                  centreid == "Mexico (rural)" ~ 70,
                                  centreid == "China (urban)" ~ 100,
                                  centreid == "China (rural)" ~ 110,
                                  centreid == "Puerto Rico" ~ 200)) %>% 
  mutate(HOUSEID = stringr::str_pad(HOUSEID, 4, pad="0")) %>% 
  mutate(houseid2 = as.numeric(paste0(centreid_num, HOUSEID)))

# Merge vital status data with baseline data
data = data %>% 
  left_join(select(mortality_outcome, houseid2, PARTICID, vital_ascertained, dead2, fu_DATE, death_date, censor_days, censor_yr), by = c("houseid2", "PARTICID"))
```

## Table 1

### Baseline characteristics of the 10/66 participants from Latin American countries

```{r, include=FALSE}
vars = c("age", "gender", "PMARRY", "PEDUC", "Nassets",  "illnocat", "pnism", "JorgePD_or_selfPD", "medserv", "PPC", "PHOSP", "POTH", "PPD", "PDENT", "PTH", "PHOSAD", "CARENEED",  "vital_ascertained")
factorVars = c("gender", "PMARRY", "PEDUC", "Nassets",  "illnocat", "pnism", "JorgePD_or_selfPD", "medserv", "PPC", "PHOSP", "POTH", "PPD", "PDENT", "PTH", "PHOSAD", "CARENEED",  "vital_ascertained")

tab1 = tableone::CreateTableOne(data = data,
                                vars = vars,
                                factorVars = factorVars,
                                strata = c("countryid"),
                                addOverall = TRUE)

table1 = print(tab1)
```

```{r, echo=FALSE}
print(tab1) %>% 
  kbl() %>% 
  kable_paper("hover", full_width=FALSE)
```

### Subset participants whose vital status was followed-up & get mortality and follow-up period

```{r}
data1 = data %>% filter(vital_ascertained=="yes")
```

```{r, include=FALSE}
vars = c("dead2", "censor_days", "censor_yr")
factorVars = c("dead2")

tab2 = tableone::CreateTableOne(data = data1,
                                vars = vars,
                                factorVars = factorVars,
                                strata = c("countryid"),
                                addOverall = TRUE)

table2 = print(tab2)
```

```{r, echo=FALSE}
print(tab2) %>% 
  kbl() %>% 
  kable_paper("hover", full_width=FALSE)
```

### Baseline characteristics of mortality cohort

```{r, include=FALSE}
vars = c("age", "gender", "PMARRY", "PEDUC", "Nassets",  "illnocat", "pnism", "JorgePD_or_selfPD", "medserv", "PPC", "PHOSP", "POTH", "PPD", "PDENT", "PTH", "PHOSAD", "CARENEED")
factorVars = c("gender", "PMARRY", "PEDUC", "Nassets",  "illnocat", "pnism", "JorgePD_or_selfPD", "medserv", "PPC", "PHOSP", "POTH", "PPD", "PDENT", "PTH", "PHOSAD", "CARENEED")

tab3 = tableone::CreateTableOne(data = data1,
                                vars = vars,
                                factorVars = factorVars,
                                strata = c("countryid"),
                                addOverall = TRUE)

table3 = print(tab3)
```

### Baseline characteristics of dependency cohort

```{r}
# Subset participants who are NOT dependent at baseline
data2 = data %>% filter(!CARENEED=="needs care much of the time")

# Merge in follow-up status at incidence phase
path = here::here("Data", "raw data", "fu folder from Matthew", "incidence cohort (all survey outcomes)", "other countries", "status_outcome (survey cohort)_1_0.sav")
status_outcome = open_and_process_data(path, "sav")

# Merge in dependency data from incidence phase
path = here::here("Data", "raw data", "fu folder from Matthew", "incidence cohort (all survey outcomes)", "other countries", "full follow up_1_2.dta")
data_full_fu12 = open_and_process_data(path, "dta")

data_full_fu12 = data_full_fu12 %>% 
  select(centreid, HOUSEID, PARTICID, f_CARENEED) %>% 
  mutate(centreid_num = case_when(centreid == "Cuba" ~ 10,
                                  centreid == "DR" ~ 20,
                                  centreid == "Peru (urban)" ~ 30,
                                  centreid == "Peru (rural)" ~ 40,
                                  centreid == "Venezuela" ~ 50,
                                  centreid == "Mexico (urban)" ~ 60,
                                  centreid == "Mexico (rural)" ~ 70,
                                  centreid == "China (urban)" ~ 100,
                                  centreid == "China (rural)" ~ 110,
                                  centreid == "Puerto Rico" ~ 200)) %>% 
  mutate(HOUSEID = stringr::str_pad(HOUSEID, 4, pad="0")) %>% 
  mutate(houseid2 = as.numeric(paste0(centreid_num, HOUSEID))) %>% 
  select(-HOUSEID, -centreid, -centreid_num)

status_outcome = status_outcome %>% 
  mutate(centreid_num = case_when(centreid == "Cuba" ~ 10,
                                  centreid == "DR" ~ 20,
                                  centreid == "Peru (urban)" ~ 30,
                                  centreid == "Peru (rural)" ~ 40,
                                  centreid == "Venezuela" ~ 50,
                                  centreid == "Mexico (urban)" ~ 60,
                                  centreid == "Mexico (rural)" ~ 70,
                                  centreid == "China (urban)" ~ 100,
                                  centreid == "China (rural)" ~ 110,
                                  centreid == "Puerto Rico" ~ 200)) %>% 
  mutate(HOUSEID = stringr::str_pad(HOUSEID, 4, pad="0")) %>% 
  mutate(houseid2 = as.numeric(paste0(centreid_num, HOUSEID))) %>% 
  select(-HOUSEID, -centreid, -centreid_num)

data_full_fu12 = data_full_fu12 %>% 
  left_join(status_outcome, by = c("houseid2", "PARTICID")) 

#### Incidence phase data excludes participants who died, refused, were uncontactable or not recorded

# Merge dependency cohort to incidence data
data2 = data_full_fu12 %>% 
  left_join(data2, by = c("houseid2", "PARTICID")) %>% 
  filter(!is.na(f_CARENEED)) %>% 
  filter(!is.na(CARENEED)) %>% 
  mutate(dependency = if_else(f_CARENEED == "needs care much of the time", "Yes", "No"))
```

```{r, include=FALSE}
vars = c("age", "gender", "PMARRY", "PEDUC", "Nassets",  "illnocat", "pnism", "JorgePD_or_selfPD", "medserv", "PPC", "PHOSP", "POTH", "PPD", "PDENT", "PTH", "PHOSAD", "dependency")
factorVars = c("gender", "PMARRY", "PEDUC", "Nassets",  "illnocat", "pnism", "JorgePD_or_selfPD", "medserv", "PPC", "PHOSP", "POTH", "PPD", "PDENT", "PTH", "PHOSAD", "dependency")

tab4 = tableone::CreateTableOne(data = data2,
                                vars = vars,
                                factorVars = factorVars,
                                strata = c("countryid"),
                                addOverall = TRUE)

table4 = print(tab4)
```

### Outcomes by Parkinsonism/PD

#### Baseline HSU

```{r, include=FALSE}
vars = c("medserv", "PPC", "PHOSP", "POTH", "PPD", "PDENT", "PTH", "PHOSAD")
factorVars = c("medserv", "PPC", "PHOSP", "POTH", "PPD", "PDENT", "PTH", "PHOSAD")

tab5_hsu_pnism = tableone::CreateTableOne(data = data,
                                vars = vars,
                                factorVars = factorVars,
                                strata = c("pnism"))

table5_hsu_pnism = print(tab5_hsu_pnism)

tab5_hsu_pd = tableone::CreateTableOne(data = data,
                                vars = vars,
                                factorVars = factorVars,
                                strata = c("JorgePD_or_selfPD"))

table5_hsu_pd = print(tab5_hsu_pd)
```

#### Incident dependency among the dependency cohort

```{r, include=FALSE}
vars = c("dependency")
factorVars = c("dependency")

tab5_care_pnism = tableone::CreateTableOne(data = data2,
                                vars = vars,
                                factorVars = factorVars,
                                strata = c("pnism"))

table5_care_pnism = print(tab5_care_pnism)

tab5_care_pd = tableone::CreateTableOne(data = data2,
                                vars = vars,
                                factorVars = factorVars,
                                strata = c("JorgePD_or_selfPD"))

table5_care_pd = print(tab5_care_pd)
```

#### Mortality among the mortality cohort

```{r, include=FALSE}
vars = c("dead2")
factorVars = c("dead2")

tab5_dead_pnism = tableone::CreateTableOne(data = data1,
                                vars = vars,
                                factorVars = factorVars,
                                strata = c("pnism"))

table5_dead_pnism = print(tab5_dead_pnism)

tab5_dead_pd = tableone::CreateTableOne(data = data1,
                                vars = vars,
                                factorVars = factorVars,
                                strata = c("JorgePD_or_selfPD"))

table5_dead_pd = print(tab5_dead_pd)
```

### Get minimum follow-up by country for mortality and dependency cohort

```{r}
data %>% 
  group_by(countryid) %>% 
  summarise(min = min(censor_yr, na.rm=TRUE),
            max = max(censor_yr, na.rm=TRUE),
            mean = mean(censor_yr, na.rm=TRUE),
            sd = sd(censor_yr, na.rm=TRUE)) %>% 
  mutate(across(min:sd, round, 2)) %>% 
  mutate(fu = paste0("Mean (SD) ", mean, " (", sd, ") ", " [Range: ", min, "-", max, "]")) %>% 
  select(countryid, fu)

data %>% 
  summarise(min = min(censor_yr, na.rm=TRUE),
            max = max(censor_yr, na.rm=TRUE),
            mean = mean(censor_yr, na.rm=TRUE),
            sd = sd(censor_yr, na.rm=TRUE)) %>% 
  mutate(across(min:sd, round, 2)) %>% 
  mutate(fu = paste0("Mean (SD) ", mean, " (", sd, ") ", " [Range: ", min, "-", max, "]")) %>% 
  select(fu)

data2 %>% 
  group_by(countryid) %>% 
  summarise(min = min(censor_yr, na.rm=TRUE),
            max = max(censor_yr, na.rm=TRUE),
            mean = mean(censor_yr, na.rm=TRUE),
            sd = sd(censor_yr, na.rm=TRUE)) %>% 
  mutate(across(min:sd, round, 2)) %>% 
  mutate(fu = paste0("Mean (SD) ", mean, " (", sd, ") ", " [Range: ", min, "-", max, "]")) %>% 
  select(countryid, fu)

data2 %>% 
  summarise(min = min(censor_yr, na.rm=TRUE),
            max = max(censor_yr, na.rm=TRUE),
            mean = mean(censor_yr, na.rm=TRUE),
            sd = sd(censor_yr, na.rm=TRUE)) %>% 
  mutate(across(min:sd, round, 2)) %>% 
  mutate(fu = paste0("Mean (SD) ", mean, " (", sd, ") ", " [Range: ", min, "-", max, "]")) %>% 
  select(fu)
```

Save tables

```{r}
path = here::here("Output", "PD outcomes paper", "Table1.csv")
write.csv(table1, path)

path = here::here("Output", "PD outcomes paper", "Table1-vitalstatus.csv")
write.csv(table2, path)

path = here::here("Output", "PD outcomes paper", "Table1-mortalitycohort.csv")
write.csv(table3, path)

path = here::here("Output", "PD outcomes paper", "Table1-dependencycohort.csv")
write.csv(table4, path)

path = here::here("Output", "PD outcomes paper", "Table1-hsu-pnism.csv")
write.csv(table5_hsu_pnism, path)
path = here::here("Output", "PD outcomes paper", "Table1-hsu-pd.csv")
write.csv(table5_hsu_pd, path)
path = here::here("Output", "PD outcomes paper", "Table1-dead-pnism.csv")
write.csv(table5_dead_pnism, path)
path = here::here("Output", "PD outcomes paper", "Table1-dead-pd.csv")
write.csv(table5_dead_pd, path)
path = here::here("Output", "PD outcomes paper", "Table1-care-pnism.csv")
write.csv(table5_care_pnism, path)
path = here::here("Output", "PD outcomes paper", "Table1-care-pd.csv")
write.csv(table5_care_pd, path)
```
