---
title: "Association between Parkinsonism/PD and health service use"
output: html_document
date: "2022-12-02"
---

### Open libraries

```{r}
library(cowplot)
library(broom)      # for tidy()
library(data.table) # for rbindlist()
library(descr)      # for crosstab(), descriptive statistics package
library(gridGraphics) # for grid.grab()
library(here)       # for easy file referencing by using the top-level directory of a file project
library(knitr)
library(meta)       # meta-analysis
library(tableone)
library(tidyverse)
```

What is the top-level of current project?
```{r}
here::here()
```

### Open 10/66 baseline dataset

Source codes
```{r}
source(here::here("Script", "Functions", "Data process", "func_open_and_process_data.R"))
source(here::here("Script", "Functions", "Data process", "func_compute_pd_variables.R"))
```

Set path for function input 
```{r}
path = here::here("Data", "raw data", "baseline survey", "prevalence_survey_data_1_3.dta")
```

Open dataset
```{r}
data = open_and_process_data(path, "dta") # this function opens a Stata dataset (dta) and converts Stata's labelled variables into factors
```

### Process dataset

Process Parkinsonism and PD variables
```{r}
data = compute_pd_variables(data)
```

Drop observations from China or India
```{r}
data = data %>% filter(centreid %in% c("Cuba", "DR", "Peru (urban)", "Peru (rural)", "Venezuela", "Mexico (urban)", "Mexico (rural)", "Puerto Rico"))

# drop unused factor levels
data$centreid = droplevels(data$centreid)
```

Subset relevant variables
```{r}
varnames = data %>% 
  select(houseid2, PARTICID, countryid, centreid, age, gender, rural, Nassets, PMARRY, CARENEED, illnocat, cdem1066, PEDUC, PTOLDDM, PSMOKE, PALCNOW, PALCPAST, PACTIVE, PMEATFRQ, PFISHFRQ, PVEGS, NEO14G, NEO6AU, NEO6AL, NEO6BU, NEO6BL, NEO4E, NEO4F, NOE1, NEO14E, PCVA, medserv, PPC, PHOSP, POTH, PPD, PDENT, PTH, PHOSAD, pnism, JorgePD, parkinsonism) %>% 
  names()

data = data %>% select_if(names(.) %in% varnames)
```

Recode `parkinsonism` variable

```{r}
data = data %>% 
  mutate(parkinsonism = if_else(parkinsonism == "Parkinsonian", 1, 0, NA_real_))

summary(as.factor(data$parkinsonism))
```

# Cross-sectional association between Parkinsonism/PD and health service use

## Cross-tabulation and chi-square test

### Parkinsonism and any community HSU

```{r}
descr::crosstab(data$medserv, data$pnism, prop.c=TRUE, chisq=TRUE)
```

### Parkinsonism and hospital admission

```{r}
descr::crosstab(data$PHOSAD, data$pnism, prop.c=TRUE,  chisq=TRUE)
```

### PD and any community HSU

```{r}
descr::crosstab(data$medserv, data$JorgePD, prop.c=TRUE,  chisq=TRUE)
```

### PD and hospital admission

```{r}
descr::crosstab(data$PHOSAD, data$JorgePD, prop.c=TRUE,  chisq=TRUE)
```

### Self-reported PD and any community HSU

```{r}
descr::crosstab(data$medserv, data$parkinsonism, prop.c=TRUE,  chisq=TRUE)
```

### Self-reported PD and hospital admission

```{r}
descr::crosstab(data$PHOSAD, data$parkinsonism, prop.c=TRUE,  chisq=TRUE)
```

## Logistic regression: overall estimates

```{r}
func_logreg_overall = function(data, outcome, exposure, adj){
  
  # Formula for the logistic regression
  formula = as.formula(paste0(outcome, " ~ ", exposure, adj))
    
  model = glm(formula, family = binomial(link="logit"), data=data) # logistic regression
  
  output = tidy(model, conf.int = TRUE, conf.level = 0.95, exponentiate = TRUE) %>% # process regression output
    mutate(ors = paste0(format.pval(round(estimate,2),nsmall=2), " (", format.pval(round(conf.low,2),nsmall=2),"-", format.pval(round(conf.high,2),nsmall=2),")")) %>% 
    select(exposure=term, ors)
    
  output$outcome = outcome # label outcome
  output$n = NA  # number of events
    
  output = output[output$exposure==exposure, ] # select ORs for exposure of interest
  
  return(output)
  
}
```

```{r}
hsu = list("medserv", "PPC", "PHOSP", "POTH", "PPD", "PDENT", "PTH", "PHOSAD")

ors_pnism_hsu_adj = lapply(hsu, func_logreg_overall, data=data, exposure="pnism", adj=" + age + gender + illnocat")
ors_pd_hsu_adj = lapply(hsu, func_logreg_overall, data=data, exposure="JorgePD", adj=" + age + gender + illnocat")
ors_selfpd_hsu_adj = lapply(hsu, func_logreg_overall, data=data, exposure="parkinsonism", adj=" + age + gender + illnocat")

data.table::rbindlist(ors_pnism_hsu_adj)
data.table::rbindlist(ors_pd_hsu_adj)
data.table::rbindlist(ors_selfpd_hsu_adj)
```

## Logistic regression: site-specific estimates

Create function to run logistic regression models

```{r}
func_logreg = function(data, outcome, exposure, adj, country){
  
  # Create an empty output df
  output = data.frame(
    outcome = NA,
    exposure = NA,
    study.site = NA,
    ors = NA,
    estimate = NA,
    std.error = NA
  )
  
  # List countries to iterate logistic regression through
  countries = c("Cuba", "DR", "Peru (urban)", "Peru (rural)", "Venezuela", "Mexico (urban)", "Mexico (rural)", "Puerto Rico")
  
  # Formula for the logistic regression
  formula = as.formula(paste0(outcome, " ~ ", exposure, adj))
  
  for (i in countries){
    
    model = glm(formula, family = binomial(link="logit"), data=data, subset=centreid==i) # logistic regression
  
    temp = tidy(model, conf.int = TRUE, conf.level = 0.95, exponentiate = TRUE) %>% # process regression output
      mutate(ors = paste0(format.pval(round(estimate,2),nsmall=2), " (", format.pval(round(conf.low,2),nsmall=2),"-", format.pval(round(conf.high,2),nsmall=2),")")) %>% 
      mutate(estimate = log(estimate)) %>% 
      select(exposure=term, ors, estimate, std.error)
    
    temp$outcome = outcome # label outcome
    temp$study.site = i #label study site
    
    temp = temp[temp$exposure==exposure, ] # select ORs for exposure of interest
    
    output = bind_rows(output, temp)
  
  }
  
  return(output)
  
}
```

Run models

```{r, message=FALSE, warning=FALSE}
################# Parkinsonism #####################

# Any community service use
ors_pnism_medserv_crude = func_logreg(data=data, outcome="medserv", exposure="pnism", adj="")
ors_pnism_medserv_adj = func_logreg(data=data, outcome="medserv", exposure="pnism", adj=" + age + gender + illnocat")

# Hospital admission
ors_pnism_phosad_crude = func_logreg(data=data, outcome="PHOSAD", exposure="pnism", adj="")
ors_pnism_phosad_adj = func_logreg(data=data, outcome="PHOSAD", exposure="pnism", adj=" + age + gender + illnocat")

# Individual community service use
ors_pnism_ppc_adj = func_logreg(data=data, outcome="PPC", exposure="pnism", adj=" + age + gender + illnocat")
ors_pnism_phosp_adj = func_logreg(data=data, outcome="PHOSP", exposure="pnism", adj=" + age + gender + illnocat")
ors_pnism_poth_adj = func_logreg(data=data, outcome="POTH", exposure="pnism", adj=" + age + gender + illnocat")
ors_pnism_ppd_adj = func_logreg(data=data, outcome="PPD", exposure="pnism", adj=" + age + gender + illnocat")
ors_pnism_pdent_adj = func_logreg(data=data, outcome="PDENT", exposure="pnism", adj=" + age + gender + illnocat")
#ors_pnism_pth_adj = func_logreg(data=data, outcome="PTH", exposure="pnism", adj=" + age + gender + illnocat")

################# PD #####################

# Any community service use
ors_pd_medserv_crude = func_logreg(data=data, outcome="medserv", exposure="JorgePD", adj="")
ors_pd_medserv_adj = func_logreg(data=data, outcome="medserv", exposure="JorgePD", adj=" + age + gender + illnocat")

# Hospital admission
ors_pd_phosad_crude = func_logreg(data=data, outcome="PHOSAD", exposure="JorgePD", adj="")
ors_pd_phosad_adj = func_logreg(data=data, outcome="PHOSAD", exposure="JorgePD", adj=" + age + gender + illnocat")

# Individual community service use
ors_pd_ppc_adj = func_logreg(data=data, outcome="PPC", exposure="JorgePD", adj=" + age + gender + illnocat")
ors_pd_phosp_adj = func_logreg(data=data, outcome="PHOSP", exposure="JorgePD", adj=" + age + gender + illnocat")
ors_pd_poth_adj = func_logreg(data=data, outcome="POTH", exposure="JorgePD", adj=" + age + gender + illnocat")
ors_pd_ppd_adj = func_logreg(data=data, outcome="PPD", exposure="JorgePD", adj=" + age + gender + illnocat")
ors_pd_pdent_adj = func_logreg(data=data, outcome="PDENT", exposure="JorgePD", adj=" + age + gender + illnocat")
#ors_pd_pth_adj = func_logreg(data=data, outcome="PTH", exposure="JorgePD", adj=" + age + gender + illnocat")

################# self-reported PD #####################

# Any community service use
ors_selfpd_medserv_crude = func_logreg(data=data, outcome="medserv", exposure="parkinsonism", adj="")
ors_selfpd_medserv_adj = func_logreg(data=data, outcome="medserv", exposure="parkinsonism", adj=" + age + gender + illnocat")

# Hospital admission
ors_selfpd_phosad_crude = func_logreg(data=data, outcome="PHOSAD", exposure="parkinsonism", adj="")
ors_selfpd_phosad_adj = func_logreg(data=data, outcome="PHOSAD", exposure="parkinsonism", adj=" + age + gender + illnocat")

# Individual community service use
ors_selfpd_ppc_adj = func_logreg(data=data, outcome="PPC", exposure="parkinsonism", adj=" + age + gender + illnocat")
ors_selfpd_phosp_adj = func_logreg(data=data, outcome="PHOSP", exposure="parkinsonism", adj=" + age + gender + illnocat")
ors_selfpd_poth_adj = func_logreg(data=data, outcome="POTH", exposure="parkinsonism", adj=" + age + gender + illnocat")
ors_selfpd_ppd_adj = func_logreg(data=data, outcome="PPD", exposure="parkinsonism", adj=" + age + gender + illnocat")
ors_selfpd_pdent_adj = func_logreg(data=data, outcome="PDENT", exposure="parkinsonism", adj=" + age + gender + illnocat")
#ors_selfpd_pth_adj = func_logreg(data=data, outcome="PTH", exposure="parkinsonism", adj=" + age + gender + illnocat")
```

## Logistic regression: meta-analysis

Run random-effects model, assumes there are 2 sources of error: 1) sampling error and 2) variance from the fact that included study sites are not from a single, homogeneous population, thus there is distribution of true effect sizes. Thus, the random-effects model aims to model the mean of the distribution of true effects.

Create function to plot forest plot

```{r}
plot_forest_meta = function(results){
  
  mgen = meta::metagen(TE = estimate,                           # make sure log(OR) than OR only
                       seTE = std.error,
                       studlab = study.site,
                       sm = "OR",
                       fixed = FALSE,
                       random = TRUE,
                       method.tau = "DL",                       # DerSimonian-Laird estimator
                       hakn = TRUE,                             # Hartung-Knapp adjustment of SEs
                       prediction = TRUE,                       # the above line and this line allow more   uncertainty in the estimation of between-study heterogeneity and appropriate for use in random-effects   meta-analysis
                       data = results)
  
  meta::forest(mgen)
  plot = grid.grab() 
  
  return(plot)

}
```

### Parkinsonism and any community HSU & hospital admission (adjusted for age, sex, and illnocat)

```{r, fig.width = 10, fig.height = 6}
plot_pnism_medserv_adj = plot_forest_meta(ors_pnism_medserv_adj[-1, ])
plot_pnism_phosad_adj = plot_forest_meta(ors_pnism_phosad_adj[-c(1, 5, 7), ])
```

### PD and any community HSU & hospital admission (adjusted for age, sex, and illnocat)

```{r, fig.width = 10, fig.height = 6}
plot_pd_medserv_adj = plot_forest_meta(ors_pd_medserv_adj[-c(1, 9), ])
plot_pd_phosad_adj = plot_forest_meta(ors_pd_phosad_adj[-c(1, 2, 3, 5, 6, 7), ])
```

### Self-reported PD and any community HSU & hospital admission (adjusted for age, sex, and illnocat)

```{r, fig.width = 10, fig.height = 6}
plot_selfpd_medserv_adj = plot_forest_meta(ors_selfpd_medserv_adj[-c(1), ])
plot_selfpd_phosad_adj = plot_forest_meta(ors_selfpd_phosad_adj[-c(1, 5), ])
```

## Individual community health service use 

```{r, fig.width = 10, fig.height = 6}
plot_pd_ppc_adj = plot_forest_meta(ors_pd_ppc_adj[-c(1, 5, 9), ])
plot_pnism_ppc_adj = plot_forest_meta(ors_pnism_ppc_adj[-1, ])

plot_pd_phosp_adj = plot_forest_meta(ors_pd_phosp_adj[-1, ])
plot_pnism_phosp_adj = plot_forest_meta(ors_pnism_phosp_adj[-1, ])

plot_pd_poth_adj = plot_forest_meta(ors_pd_poth_adj[-c(1, 3:7, 9), ])
plot_pnism_poth_adj = plot_forest_meta(ors_pnism_poth_adj[-c(1,5,9), ])

plot_pd_ppd_adj = plot_forest_meta(ors_pd_ppd_adj[-c(1,2,5), ])
plot_pnism_ppd_adj = plot_forest_meta(ors_pnism_ppd_adj[-c(1:2), ])

plot_pd_pdent_adj = plot_forest_meta(ors_pd_pdent_adj[-c(1, 5), ])
plot_pnism_pdent_adj = plot_forest_meta(ors_pnism_pdent_adj[-c(1,5), ])

#plot_pd_pth_adj = plot_forest_meta(ors_pd_pth_adj[-1, ])
#plot_pnism_pth_adj = plot_forest_meta(ors_pnism_pth_adj[-1, ])
```

## Combine and save outputs

### Main results

```{r}
plot_combined_community_adj = cowplot::plot_grid(plot_pnism_medserv_adj, plot_selfpd_medserv_adj, plot_pd_medserv_adj,
                                         align = "hv",
                                         labels = "AUTO", 
                                         scale = 0.5,
                                         ncol = 1)

ggsave(plot = plot_combined_community_adj, filename = here::here("Output", "PD outcomes paper", "plots", "ors_communityHSU_adj1.png"), width = 22, height = 32, units = "cm")

plot_combined_hosp_adj = cowplot::plot_grid(plot_pnism_phosad_adj, plot_selfpd_phosad_adj, plot_pd_phosad_adj,
                                         align = "hv",
                                         labels = "AUTO", 
                                         scale = 0.5,
                                         ncol = 1)

plot_combined_hosp_adj

ggsave(plot = plot_combined_hosp_adj, filename = here::here("Output", "PD outcomes paper", "plots", "ors_hospadm_adj1.png"), width = 22, height = 32, units = "cm")
```

### Individual community HSU

```{r}
plot_combined_ppc_adj = cowplot::plot_grid(plot_pnism_ppc_adj, plot_pd_ppc_adj,
                                         align = "hv",
                                         labels = "AUTO", 
                                         scale = 0.5,
                                         ncol = 1)

plot_combined_ppc_adj

ggsave(plot = plot_combined_ppc_adj, filename = here::here("Output", "PD outcomes paper", "plots", "ors_PrimaryCare_adj.png"), width = 22, height = 20, units = "cm")


plot_combined_phosp_adj = cowplot::plot_grid(plot_pnism_phosp_adj, plot_pd_phosp_adj,
                                         align = "hv",
                                         labels = "AUTO", 
                                         scale = 0.5,
                                         ncol = 1)

plot_combined_phosp_adj

ggsave(plot = plot_combined_hosp_adj, filename = here::here("Output", "PD outcomes paper", "plots", "ors_GovHosp_adj.png"), width = 22, height = 20, units = "cm")


plot_combined_poth_adj = cowplot::plot_grid(plot_pnism_poth_adj, plot_pd_poth_adj,
                                         align = "hv",
                                         labels = "AUTO", 
                                         scale = 0.5,
                                         ncol = 1)

plot_combined_poth_adj

ggsave(plot = plot_combined_poth_adj, filename = here::here("Output", "PD outcomes paper", "plots", "ors_OtherGovHealth_adj.png"), width = 22, height = 20, units = "cm")

### Not plotted ##
plot_combined_ppd_adj = cowplot::plot_grid(plot_pnism_ppd_adj, plot_pd_ppd_adj,
                                         align = "hv",
                                         labels = "AUTO", 
                                         scale = 0.5,
                                         ncol = 1)

plot_combined_ppd_adj

ggsave(plot = plot_combined_ppd_adj, filename = here::here("Output", "PD outcomes paper", "plots", "ors_PrivateDoc_adj.png"), width = 22, height = 20, units = "cm")


plot_combined_dent_adj = cowplot::plot_grid(plot_pnism_pdent_adj, plot_pd_pdent_adj,
                                         align = "hv",
                                         labels = "AUTO", 
                                         scale = 0.5,
                                         ncol = 1)

plot_combined_dent_adj

ggsave(plot = plot_combined_dent_adj, filename = here::here("Output", "PD outcomes paper", "plots", "ors_dentist_adj.png"), width = 22, height = 20, units = "cm")

### not plotted ###
#plot_combined_heal_adj = cowplot::plot_grid(plot_pnism_pth_adj, plot_pd_pth_adj,
#                                         align = "hv",
#                                         labels = "AUTO", 
#                                         scale = 0.5,
#                                         ncol = 1)
#
#plot_combined_heal_adj
#
#ggsave(plot = plot_combined_heal_adj, filename = here::here("Output", "PD outcomes paper", "plots", #"ors_healer_adj.png"), width = 22, height = 20, units = "cm")
```