---
title: "Association between Parkinsonism/PD and incident dependency"
output: html_document
date: "2022-12-08"
---

### Open libraries

```{r}
library(cowplot)
library(broom)      # for tidy()
library(data.table) # for rbindlist()
library(descr)      # for crosstab(), descriptive statistics package
library(gridGraphics) # for grid.grab()
library(here)       # for easy file referencing by using the top-level directory of a file project
library(knitr)
library(meta)       # meta-analysis
library(tableone)
library(tidyverse)
```


What is the top-level of current project?
```{r}
here::here()
```

### Open 10/66 baseline dataset

Source codes
```{r}
source(here::here("Script", "Functions", "Data process", "func_open_and_process_data.R"))
source(here::here("Script", "Functions", "Data process", "func_compute_pd_variables.R"))
```

Set path for function input 
```{r}
path = here::here("Data", "raw data", "baseline survey", "prevalence_survey_data_1_3.dta")
```

Open dataset
```{r}
data = open_and_process_data(path, "dta") # this function opens a Stata dataset (dta) and converts Stata's labelled variables into factors
```

### Process dataset

Process Parkinsonism and PD variables
```{r}
data = compute_pd_variables(data)
```

Drop observations from China or India
```{r}
data = data %>% filter(centreid %in% c("Cuba", "DR", "Peru (urban)", "Peru (rural)", "Venezuela", "Mexico (urban)", "Mexico (rural)", "Puerto Rico"))

# drop unused factor levels
data$centreid = droplevels(data$centreid)
```

Subset relevant variables
```{r}
varnames = data %>% 
  select(houseid2, PARTICID, countryid, centreid, age, gender, rural, Nassets, PMARRY, CARENEED, illnocat, cdem1066, PEDUC, PTOLDDM, PSMOKE, PALCNOW, PALCPAST, PACTIVE, PMEATFRQ, PFISHFRQ, PVEGS, NEO14G, NEO6AU, NEO6AL, NEO6BU, NEO6BL, NEO4E, NEO4F, NOE1, NEO14E, PCVA, medserv, PPC, PHOSP, POTH, PPD, PDENT, PTH, PHOSAD, pnism, JorgePD, parkinsonism) %>% 
  names()

data = data %>% select_if(names(.) %in% varnames)
```

Recode `parkinsonism` variable

```{r}
data = data %>% 
  mutate(parkinsonism = if_else(parkinsonism == "Parkinsonian", 1, 0, NA_real_))

summary(as.factor(data$parkinsonism))
```

### Incident dependency

```{r}
# Subset participants who are NOT dependent at baseline
data2 = data %>% filter(!CARENEED=="needs care much of the time")

# Merge in follow-up status at incidence phase
path = here::here("Data", "raw data", "fu folder from Matthew", "incidence cohort (all survey outcomes)", "other countries", "status_outcome (survey cohort)_1_0.sav")
status_outcome = open_and_process_data(path, "sav")

# Merge in dependency data from incidence phase
path = here::here("Data", "raw data", "fu folder from Matthew", "incidence cohort (all survey outcomes)", "other countries", "full follow up_1_2.dta")
data_full_fu12 = open_and_process_data(path, "dta")

data_full_fu12 = data_full_fu12 %>% 
  select(centreid, HOUSEID, PARTICID, f_CARENEED) %>% 
  mutate(centreid_num = case_when(centreid == "Cuba" ~ 10,
                                  centreid == "DR" ~ 20,
                                  centreid == "Peru (urban)" ~ 30,
                                  centreid == "Peru (rural)" ~ 40,
                                  centreid == "Venezuela" ~ 50,
                                  centreid == "Mexico (urban)" ~ 60,
                                  centreid == "Mexico (rural)" ~ 70,
                                  centreid == "China (urban)" ~ 100,
                                  centreid == "China (rural)" ~ 110,
                                  centreid == "Puerto Rico" ~ 200)) %>% 
  mutate(HOUSEID = stringr::str_pad(HOUSEID, 4, pad="0")) %>% 
  mutate(houseid2 = as.numeric(paste0(centreid_num, HOUSEID))) %>% 
  select(-HOUSEID, -centreid, -centreid_num)

status_outcome = status_outcome %>% 
  mutate(centreid_num = case_when(centreid == "Cuba" ~ 10,
                                  centreid == "DR" ~ 20,
                                  centreid == "Peru (urban)" ~ 30,
                                  centreid == "Peru (rural)" ~ 40,
                                  centreid == "Venezuela" ~ 50,
                                  centreid == "Mexico (urban)" ~ 60,
                                  centreid == "Mexico (rural)" ~ 70,
                                  centreid == "China (urban)" ~ 100,
                                  centreid == "China (rural)" ~ 110,
                                  centreid == "Puerto Rico" ~ 200)) %>% 
  mutate(HOUSEID = stringr::str_pad(HOUSEID, 4, pad="0")) %>% 
  mutate(houseid2 = as.numeric(paste0(centreid_num, HOUSEID))) %>% 
  select(-HOUSEID, -centreid, -centreid_num)

data_full_fu12 = data_full_fu12 %>% 
  left_join(status_outcome, by = c("houseid2", "PARTICID")) 

#### Incidence phase data excludes participants who died, refused, were uncontactable or not recorded

# Merge dependency cohort to incidence data
data2 = data_full_fu12 %>% 
  left_join(data2, by = c("houseid2", "PARTICID")) %>% 
  filter(!is.na(f_CARENEED)) %>% 
  filter(!is.na(CARENEED)) %>% 
  mutate(dependency = if_else(f_CARENEED == "needs care much of the time", 1, 0))
```
# Association between Parkinsonism/PD and incident dependency

## Logistic regression: site-specific estimates

Create function to run logistic regression models

```{r}
func_logreg = function(data, outcome, exposure, adj, country){
  
  # Create an empty output df
  output = data.frame(
    outcome = NA,
    exposure = NA,
    study.site = NA,
    ors = NA,
    estimate = NA,
    std.error = NA
  )
  
  # List countries to iterate logistic regression through
  #countries = c("Cuba", "DR", "Peru (urban)", "Peru (rural)", "Venezuela", "Mexico (urban)", "Mexico (rural)", "Puerto Rico")
  countries = c("Cuba", "DR", "Peru", "Venezuela", "Mexico", "Puerto Rico")
  
  # Formula for the logistic regression
  formula = as.formula(paste0(outcome, " ~ ", exposure, adj))
  
  for (i in countries){
    
    model = glm(formula, family = binomial(link="logit"), data=data, subset=countryid==i) # logistic regression
  
    temp = tidy(model, conf.int = TRUE, conf.level = 0.95, exponentiate = TRUE) %>% # process regression output
      mutate(ors = paste0(format.pval(round(estimate,2),nsmall=2), " (", format.pval(round(conf.low,2),nsmall=2),"-", format.pval(round(conf.high,2),nsmall=2),")")) %>% 
      mutate(estimate = log(estimate)) %>% 
      select(exposure=term, ors, estimate, std.error)
    
    temp$outcome = outcome # label outcome
    temp$study.site = i #label study site
    
    temp = temp[temp$exposure==exposure, ] # select ORs for exposure of interest
    
    output = bind_rows(output, temp)
  
  }
  
  return(output)
  
}
```

Run models

```{r, message=FALSE, warning=FALSE}
ors_pnism_care_crude = func_logreg(data=data2, outcome="dependency", exposure="pnism", adj="")
ors_pd_care_crude = func_logreg(data=data2, outcome="dependency", exposure="JorgePD", adj="")
ors_selfpd_care_crude= func_logreg(data=data2, outcome="dependency", exposure="parkinsonism", adj="")

ors_pnism_care_adj = func_logreg(data=data2, outcome="dependency", exposure="pnism", adj=" + age + gender + PEDUC + illnocat")
ors_pd_care_adj = func_logreg(data=data2, outcome="dependency", exposure="JorgePD", adj=" + age + gender + PEDUC + illnocat")
ors_selfpd_care_adj = func_logreg(data=data2, outcome="dependency", exposure="parkinsonism", adj=" + age + gender + PEDUC + illnocat")
```

## Logistic regression: meta-analysis

Run random-effects model, assumes there are 2 sources of error: 1) sampling error and 2) variance from the fact that included study sites are not from a single, homogeneous population, thus there is distribution of true effect sizes. Thus, the random-effects model aims to model the mean of the distribution of true effects.

Create function to plot forest plot

```{r}
plot_forest_meta = function(results){
  
  mgen = meta::metagen(TE = estimate,                           # make sure log(OR) than OR only
                       seTE = std.error,
                       studlab = study.site,
                       sm = "OR",
                       fixed = TRUE,
                       random = FALSE,
                       method.tau = "DL",                       # DerSimonian-Laird estimator
                       hakn = TRUE,                             # Hartung-Knapp adjustment of SEs
                       prediction = FALSE,                       # the above line and this line allow more   uncertainty in the estimation of between-study heterogeneity and appropriate for use in random-effects   meta-analysis
                       data = results)
  
  meta::forest(mgen, 
             rightlabs = c("OR", "95% CI", "Weight"),
             print.tau2 = FALSE,
             leftcols = c("studlab"))
  plot = grid.grab() 
  
  return(plot)

}
```

### Parkinsonism and incident dependency (adjusted for age, sex, education, and illnocat)

```{r, fig.width = 10, fig.height = 6}
plot_pnism_care_adj = plot_forest_meta(ors_pnism_care_adj[-1, ])
```

### PD and incident dependency (adjusted for age, sex, education, and illnocat)

```{r, fig.width = 10, fig.height = 6}
plot_pd_care_adj = plot_forest_meta(ors_pd_care_adj[-1, ])
```

### Self-reported PD and incident dependency (adjusted for age, sex, education, and illnocat)

```{r, fig.width = 10, fig.height = 6}
plot_selfpd_care_adj = plot_forest_meta(ors_selfpd_care_adj[-1, ])
```

## Combine and save outputs

```{r}
plot_combined_care_adj = cowplot::plot_grid(plot_pnism_care_adj, plot_pd_care_adj,
                                         align = "hv",
                                         labels = "AUTO", 
                                         scale = 0.5,
                                         ncol = 1)

ggsave(plot = plot_combined_care_adj, filename = here::here("Output", "PD outcomes paper", "plots", "ors_IncidentDependency_adj.png"), width = 18, height = 15, units = "cm") # width = 22, height = 32 for 3 rows
```