---
title: "Association between Parkinsonism/PD and incident dependency (Cox PH)"
output: html_document
date: "2023-02-02"
---

### Open libraries

```{r}
library(cowplot)
library(broom)      # for tidy()
library(data.table) # for rbindlist()
library(descr)      # for crosstab(), descriptive statistics package
library(gridGraphics) # for grid.grab()
library(here)       # for easy file referencing by using the top-level directory of a file project
library(knitr)
library(meta)       # meta-analysis
library(survival)
library(tableone)
library(tidyverse)
```


What is the top-level of current project?
```{r}
here::here()
```

### Open 10/66 baseline dataset

Source codes
```{r}
source(here::here("Script", "Functions", "Data process", "func_open_and_process_data.R"))
source(here::here("Script", "Functions", "Data process", "func_compute_pd_variables.R"))
```

Set path for function input 
```{r}
path = here::here("Data", "raw data", "baseline survey", "prevalence_survey_data_1_3.dta")
```

Open dataset
```{r}
data = open_and_process_data(path, "dta") # this function opens a Stata dataset (dta) and converts Stata's labelled variables into factors
```

### Process dataset

Process Parkinsonism and PD variables
```{r}
data = compute_pd_variables(data)
```

Drop observations from China or India
```{r}
data = data %>% filter(centreid %in% c("Cuba", "DR", "Peru (urban)", "Peru (rural)", "Venezuela", "Mexico (urban)", "Mexico (rural)", "Puerto Rico"))

# drop unused factor levels
data$centreid = droplevels(data$centreid)
```

Subset relevant variables
```{r}
varnames = data %>% 
  select(houseid2, PARTICID, countryid, centreid, age, gender, rural, Nassets, PMARRY, CARENEED, illnocat, cdem1066, PEDUC, PTOLDDM, PSMOKE, PALCNOW, PALCPAST, PACTIVE, PMEATFRQ, PFISHFRQ, PVEGS, NEO14G, NEO6AU, NEO6AL, NEO6BU, NEO6BL, NEO4E, NEO4F, NOE1, NEO14E, PCVA, medserv, PPC, PHOSP, POTH, PPD, PDENT, PTH, PHOSAD, pnism, JorgePD, parkinsonism, PARK) %>% 
  names()

data = data %>% select_if(names(.) %in% varnames)
```

Recode `parkinsonism` variable

```{r}
data = data %>% 
  mutate(parkinsonism = if_else(parkinsonism == "Parkinsonian", 1, 0, NA_real_))

summary(as.factor(data$parkinsonism))
```
Create a PD variable that combines the algorithm-based dx (`JorgePD`) and self-reported dx (`PARK`)

```{r}
# Create a PD variable that combines the algorithm-based dx (`JorgePD`) and self-reported dx (`PARK`)
data = data %>% 
  mutate(JorgePD_or_selfPD = case_when(JorgePD==1 | PARK=="probable" | PARK=="certain" ~ 1, 
                                       JorgePD==0 | PARK=="no" ~ 0, 
                                       TRUE ~ NA_real_))

summary(as.factor(data$JorgePD_or_selfPD))
```

### Incident dependency and other follow-up info

Open relevant data

```{r}
# Open follow-up status at incidence phase
path = here::here("Data", "raw data", "fu folder from Matthew", "incidence cohort (all survey outcomes)", "other countries", "status_outcome (survey cohort)_1_0.sav")
status_outcome = open_and_process_data(path, "sav")

# Open follow-up data 
path = here::here("Data", "raw data", "fu folder from Matthew", "incidence cohort (all survey outcomes)", "other countries", "person_years1_1.sav")
fu_data = open_and_process_data(path, "sav")

# Open dependency data from incidence phase
path = here::here("Data", "raw data", "fu folder from Matthew", "incidence cohort (all survey outcomes)", "other countries", "full follow up_1_2.dta")
data_full_fu12 = open_and_process_data(path, "dta")
```

Subset participants who are NOT dependent at baseline

```{r}
# Subset participants who are NOT dependent at baseline
data2 = data %>% filter(!CARENEED=="needs care much of the time")
```

Select relevant variables from other datasets

```{r}
# Select dependecy at follow-up
data_full_fu12 = data_full_fu12 %>% 
  select(centreid, HOUSEID, PARTICID, f_CARENEED) %>% 
  mutate(centreid_num = case_when(centreid == "Cuba" ~ 10,
                                  centreid == "DR" ~ 20,
                                  centreid == "Peru (urban)" ~ 30,
                                  centreid == "Peru (rural)" ~ 40,
                                  centreid == "Venezuela" ~ 50,
                                  centreid == "Mexico (urban)" ~ 60,
                                  centreid == "Mexico (rural)" ~ 70,
                                  centreid == "China (urban)" ~ 100,
                                  centreid == "China (rural)" ~ 110,
                                  centreid == "Puerto Rico" ~ 200)) %>% 
  mutate(HOUSEID = stringr::str_pad(HOUSEID, 4, pad="0")) %>% 
  mutate(houseid2 = as.numeric(paste0(centreid_num, HOUSEID))) %>% 
  select(-HOUSEID, -centreid, -centreid_num)

# Select outcome status at follow-up
status_outcome = status_outcome %>% 
  mutate(centreid_num = case_when(centreid == "Cuba" ~ 10,
                                  centreid == "DR" ~ 20,
                                  centreid == "Peru (urban)" ~ 30,
                                  centreid == "Peru (rural)" ~ 40,
                                  centreid == "Venezuela" ~ 50,
                                  centreid == "Mexico (urban)" ~ 60,
                                  centreid == "Mexico (rural)" ~ 70,
                                  centreid == "China (urban)" ~ 100,
                                  centreid == "China (rural)" ~ 110,
                                  centreid == "Puerto Rico" ~ 200)) %>% 
  mutate(HOUSEID = stringr::str_pad(HOUSEID, 4, pad="0")) %>% 
  mutate(houseid2 = as.numeric(paste0(centreid_num, HOUSEID))) %>% 
  select(-HOUSEID, -centreid, -centreid_num)

# Select censor days 
fu_data = fu_data %>% 
  select(centreid, HOUSEID, PARTICID, censor_days, dead2) %>% 
  mutate(centreid_num = case_when(centreid == "Cuba" ~ 10,
                                  centreid == "DR" ~ 20,
                                  centreid == "Peru (urban)" ~ 30,
                                  centreid == "Peru (rural)" ~ 40,
                                  centreid == "Venezuela" ~ 50,
                                  centreid == "Mexico (urban)" ~ 60,
                                  centreid == "Mexico (rural)" ~ 70,
                                  centreid == "China (urban)" ~ 100,
                                  centreid == "China (rural)" ~ 110,
                                  centreid == "Puerto Rico" ~ 200)) %>% 
  mutate(HOUSEID = stringr::str_pad(HOUSEID, 4, pad="0")) %>% 
  mutate(houseid2 = as.numeric(paste0(centreid_num, HOUSEID))) %>% 
  select(-HOUSEID, -centreid, -centreid_num)
```
```{r}
# Check status outcome among the 12865 Latin American cohort
temp = data %>% 
  left_join(status_outcome, by = c("houseid2", "PARTICID"))

summary(temp$Statusfu)

# Check status outcome among the 11739 Latin American cohort who are NOT dependent at baseline
temp = data2 %>% 
  left_join(status_outcome, by = c("houseid2", "PARTICID"))

summary(temp$Statusfu)
```

Merge data into baseline data

```{r}
# Merge data
data_full_fu12 = data_full_fu12 %>% 
  left_join(status_outcome, by = c("houseid2", "PARTICID")) %>% 
  left_join(fu_data, by = c("houseid2", "PARTICID"))

#### Incidence phase data excludes participants who died, refused, were uncontactable or not recorded

# Merge dependency cohort to incidence data
data = data_full_fu12 %>% 
  left_join(data2, by = c("houseid2", "PARTICID")) %>% 
  filter(!is.na(f_CARENEED)) %>% 
  filter(!is.na(CARENEED)) %>% 
  mutate(dependency = if_else(f_CARENEED == "needs care much of the time", 1, 0))
```

# Association between Parkinsonism/PD and incident dependency

## Check PH assumption

```{r}
res.cox = survival::coxph(Surv(censor_days/2, dependency) ~ pnism, data = data)
test.ph = survival::cox.zph(res.cox)
test.ph

res.cox = survival::coxph(Surv(censor_days/2, dependency) ~ pnism + age + gender + illnocat + PEDUC, data = data)
test.ph = survival::cox.zph(res.cox)
test.ph

res.cox = survival::coxph(Surv(censor_days/2, dependency) ~ JorgePD, data = data)
test.ph = survival::cox.zph(res.cox)
test.ph

res.cox = survival::coxph(Surv(censor_days/2, dependency) ~ JorgePD + age + gender + illnocat + PEDUC, data = data)
test.ph = survival::cox.zph(res.cox)
test.ph

res.cox = survival::coxph(Surv(censor_days/2, dependency) ~ JorgePD_or_selfPD, data = data)
test.ph = survival::cox.zph(res.cox)
test.ph

res.cox = survival::coxph(Surv(censor_days/2, dependency) ~ JorgePD_or_selfPD + age + gender + illnocat + PEDUC, data = data)
test.ph = survival::cox.zph(res.cox)
test.ph
```
From the output above, the test is statistically significant for the `PEDUC` variable. Therefore, we can assume the proportional hazards is violated. One solution would be to conduct a stratified Cox PH - the covariate with nonproportional effects is included in the Cox model as stratification variable rather than a predictor.  However, the global test is only statistically significant for `JorgePD`, so simply adjust covariates.

## Cox Proportional hazards regression: site-specific estimates

Create function to run Cox PH regression models

```{r}
func_coxph = function(data, exposure, adj, country){
  
  # Create an empty output df
  output = data.frame(
    exposure = NA,
    study.site = NA,
    hrs = NA,
    estimate = NA,
    std.error = NA
  )
  
  # List countries to iterate Cox PH regression through
  #countries = c("Cuba", "DR", "Peru (urban)", "Peru (rural)", "Venezuela", "Mexico (urban)", "Mexico (rural)", "Puerto Rico") 
  countries = c("Cuba", "DR", "Peru", "Venezuela", "Mexico", "Puerto Rico") # using study sites results in small numbers, use country-level variable
  
  # Formula for the Cox PH regression
  outcome = "Surv(censor_days/2, dependency)"
  formula = as.formula(paste0(outcome, " ~ ", exposure, adj))
  
  for (i in countries){
    
    model = coxph(formula, data=data, subset=countries==i) # cox regression
  
    temp = tidy(model, conf.int = TRUE, conf.level = 0.95, exponentiate = TRUE) %>% # process regression output
      mutate(hrs = paste0(format.pval(round(estimate,2),nsmall=2), " (", format.pval(round(conf.low,2),nsmall=2),"-", format.pval(round(conf.high,2),nsmall=2),")")) %>% 
      mutate(estimate = log(estimate)) %>% 
      select(exposure=term, hrs, estimate, std.error)
    
    temp$study.site = i #label study site
    
    temp = temp[temp$exposure==exposure, ] # select ORs for exposure of interest
    
    output = bind_rows(output, temp)
  
  }
  
  return(output)
  
}
```

Run models

```{r, message=FALSE, warning=FALSE}
hrs_pnism_care_crude = func_coxph(data=data, exposure="pnism", adj="")
hrs_pd_care_crude = func_coxph(data=data, exposure="JorgePD", adj="")
hrs_pd2_care_crude= func_coxph(data=data, exposure="JorgePD_or_selfPD", adj="")

hrs_pnism_care_adj = func_coxph(data=data, exposure="pnism", adj=" + age + gender + illnocat + strata(PEDUC)")
hrs_pd_care_adj = func_coxph(data=data, exposure="JorgePD", adj=" + age + gender + illnocat + strata(PEDUC)")
hrs_pd2_care_adj = func_coxph(data=data, exposure="JorgePD_or_selfPD", adj=" + age + gender + illnocat + strata(PEDUC)")
```

## Cox PH regression: meta-analysis

Run random-effects model, assumes there are 2 sources of error: 1) sampling error and 2) variance from the fact that included study sites are not from a single, homogeneous population, thus there is distribution of true effect sizes. Thus, the random-effects model aims to model the mean of the distribution of true effects.

Create function to plot forest plot

```{r}
plot_forest_meta = function(results){
  
  mgen = meta::metagen(TE = estimate,                           # make sure log(OR) than OR only
                       seTE = std.error,
                       studlab = study.site,
                       sm = "HR",
                       fixed = TRUE,
                       random = FALSE,
                       method.tau = "DL",                       # DerSimonian-Laird estimator
                       hakn = TRUE,                             # Hartung-Knapp adjustment of SEs
                       prediction = FALSE,                       # the above line and this line allow more   uncertainty in the estimation of between-study heterogeneity and appropriate for use in random-effects   meta-analysis
                       data = results)
  
  meta::forest(mgen, 
             rightlabs = c("HR", "95% CI", "Weight"),
             print.tau2 = FALSE,
             leftcols = c("studlab"))
  
  plot = grid.grab() 
  
  return(plot)

}
```

### Parkinsonism and incident dependency (crude & adjusted for age, sex, education, and illnocat)

```{r, fig.width = 10, fig.height = 6}
plot_pnism_care_crude = plot_forest_meta(hrs_pnism_care_crude[-1, ])
plot_pnism_care_adj = plot_forest_meta(hrs_pnism_care_adj[-1, ])
```

### PD and incident dependency (crude & adjusted for age, sex, education, and illnocat)

```{r, fig.width = 10, fig.height = 6}
plot_pd_care_crude = plot_forest_meta(hrs_pd_care_crude[-1, ])
plot_pd_care_adj = plot_forest_meta(hrs_pd_care_adj[-1, ])
```

### JorgePD_or_selfPD and incident dependency (crude & adjusted for age, sex, education, and illnocat)

```{r, fig.width = 10, fig.height = 6}
plot_pd2_care_crude = plot_forest_meta(hrs_pd2_care_crude[-1, ])
plot_pd2_care_adj = plot_forest_meta(hrs_pd2_care_adj[-1, ])
```

## Combine and save outputs

```{r}
plot_combined_care_adj = cowplot::plot_grid(plot_pnism_care_adj, plot_pd2_care_adj,
                                         align = "hv",
                                         labels = "AUTO", 
                                         scale = 0.5,
                                         ncol = 1)

ggsave(plot = plot_combined_care_adj, filename = here::here("Output", "PD outcomes paper", "plots", "hrs_IncidentDependency_adj.png"), width = 18, height = 15, units = "cm") # height = 20 for 3 rows; height = 15 for 2 rows

plot_combined_care_crude = cowplot::plot_grid(plot_pnism_care_crude, plot_pd2_care_crude,
                                         align = "hv",
                                         labels = "AUTO", 
                                         scale = 0.5,
                                         ncol = 1)

ggsave(plot = plot_combined_care_crude, filename = here::here("Output", "PD outcomes paper", "plots", "hrs_IncidentDependency_crude.png"), width = 18, height = 15, units = "cm") # height = 20 for 3 rows; height = 15 for 2 rows
```

### Sensitivity analysis: Association between JorgePD and incident dependency

Save plot as rds

```{r}
saveRDS(plot_pd_care_adj, file = here::here("Output", "PD outcomes paper", "plots", "temp_plot_JorgePD_care.rds"))
```
